### 2014-11-17 Proposal.tex
First thesis proposal draft

\documentclass[twoside]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.5} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Naomi Pentrel $\bullet$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\bullet$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}

\usepackage{tocloft}

%\usepackage{csquotes}
%\MakeOuterQuote{"}

\hypersetup{
    bookmarks=true,
    unicode=false,
    pdftoolbar=true,
    pdfmenubar=true,
    pdffitwindow=false,
    pdfstartview={FitH},
    pdftitle={My title},
    pdfauthor={Author},
    pdfsubject={Subject},
    pdfcreator={Creator},
    pdfproducer={Producer},
    pdfkeywords={keyword1} {key2} {key3},
    pdfnewwindow=true,
    colorlinks=false,
    linkcolor=red,
    citecolor=green,
    filecolor=magenta,
    urlcolor=cyan
}

\usepackage{caption}
\usepackage{subcaption}
\usepackage[section]{placeins}
\usepackage{qtree}
\usepackage{gensymb}

\usepackage{setspace}

\usepackage{color}

%\doublespacing
% or:
%\onehalfspacing

%\renewcommand\cftchapafterpnum{\vskip10pt}
%\renewcommand\cftsecafterpnum{\vskip15pt}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}} % Article title

%----------------------------------------------------------------------------------------

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=0.7]{Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{Visualization of Theory Graphs of Semantically Annotated Documents in the Form of Spatial Presentations}
  \end{center}
  \vspace*{4mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel}
  \end{center}
  \vspace*{20mm}
  \begin{center}
    \large
    Bachelor Thesis Proposal in Computer Science
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}

      \hline
      Prof. Dr. Michael Kohlhase \\
      \\
    \end{tabular}
  \end{flushright}
  \vspace*{8mm}
  \begin{flushleft}
    \large
    Date of Submission: \today \\
    \rule{\textwidth}{1pt}
  \end{flushleft}
  \begin{center}
    \Large Jacobs University Bremen - School of Engineering and Science
  \end{center}

\newpage
\noindent
  With my signature, I certify that this thesis has been written by me
  using only the indicates resources and materials. Where I have
  presented data and results, the data and results are complete,
  genuine, and have been obtained by me unless otherwise acknowledged;
  where my results derive from computer programs, these computer
  programs have been written by me unless otherwise acknowledged. I
  further confirm that this thesis has not been submitted, either in
  part or as a whole, for any other academic degree at this or another
  institution.

  \vspace{20mm}

    \includegraphics[scale=0.2]{Signature}
 \hfill Bremen, \today

\newpage

\thispagestyle{fancy} % All pages have headers and footers

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

 \section*{Abstract}

  Consider this a separate document, although it is submitted together
  with the rest. The abstract aims at another audience than the rest
  of the proposal. It is directed at the final decision maker or
  generalist, who typically is not an expert at all in your field, but
  more a manager kind of person. Thus, don't go into any technical
  description in the abstract, but use it to motivate the work and to
  highlight the importance of your project.

  (target size: 15-20 lines)

  \newpage
  \tableofcontents

  \clearpage
  \pagenumbering{arabic}

  \section{Introduction}

  This, like the rest, addresses fellow experts from your field (but
  not from your particular topic of research). Here you should
  technically connect to the main concepts from that field and give an
  outline of your project, stating the research/engineering question
  that you want to get answered by your project.

  (target size: 1 page)
\newpage
  \section{Statement and Motivation of Research}

  This part should make clear which question, exactly, you are
  pursuing, and why your project is relevant/interesting. This is the
  place to cite relevant literature. Where does your project extend
  the state of the art? what weaknesses in known approaches to you
  hope to overcome? If you have carried out preliminary experiments,
  describe them here.

What is the idea?
Why is this important for the world?

What is Prezi?
How will this improve learning?
What's the best representation one could do

  (target size: 3-5 pages)
\newpage
  \section{Planned Investigation}

  This is the technical core of the proposal. Here you lay out your
  plans of how you want to answer your research question specify your
  design of experiments or simulations, point out difficulties that
  you expect to encounter, etc.

3. Planning
How will this be implemented?
Using which frameworks?

  (target size: 3-4 pages)
\newpage
  \section{Evaluation Criteria}

  This section discusses criteria which can be used to evaluate the
  research results and which can be used to related research results
  to the already known state-of-the-art.

  (target size: 1-2 page)
\newpage
  \section{Timeline}

\textbf{Milestones}
\begin{itemize}
\item \textbf{Until February 15th}: Complete preliminary development to create a presentation from an XML
\item \textbf{Until April 1st}: Complete development of organized presentations that are generated from ordered knowledge graphs.
\item \textbf{Until May 1st}: Testing and Performance Measurement.
\item \textbf{Until May 10th}: Complete development of organized presentations that are generated from ordered knowledge graphs.
\end{itemize}

\begin{figure}[h]
\begin{center}
\begin{ganttchart}[y unit title=0.4cm,
y unit chart=0.5cm,
vgrid,hgrid, 
title label anchor/.style={below=-1.6ex},
title left shift=.05,
title right shift=-.05,
title height=1,
bar/.style={fill=gray!50},
incomplete/.style={fill=white},
progress label text={},
bar height=0.7,
group right shift=0,
group top shift=.6,
group height=.3,
group peaks={}{}{.2}]{24}
%labels
\gantttitle{Proposed Timeline}{24} \\
\gantttitle{December}{4} 
\gantttitle{January}{4} 
\gantttitle{February}{4} 
\gantttitle{March}{4} 
\gantttitle{April}{4} 
\gantttitle{May}{4} \\
%tasks
\ganttbar{Preliminary development}{2}{10} \\
\ganttbar{Graph visualization}{11}{16} \\
\ganttbar{Testing \& Performance}{17}{20} \\
\ganttbar{Final Report submission}{21}{21.5}

%relations 
\ganttlink{elem0}{elem1} 
\ganttlink{elem1}{elem2} 
\ganttlink{elem2}{elem3} 
\end{ganttchart}
\end{center}
\caption{Gantt Chart}
\end{figure}

  \section{Conclusions}

  Summarize the main aspects of the proposal.

  (target size: 1/2 page)

\end{document}

### 2014-11-17 Proposal.tex
added Abstract draft

@@
 
-  Consider this a separate document, although it is submitted together
-  with the rest. The abstract aims at another audience than the rest
-  of the proposal. It is directed at the final decision maker or
-  generalist, who typically is not an expert at all in your field, but
-  more a manager kind of person. Thus, don't go into any technical
-  description in the abstract, but use it to motivate the work and to
-  highlight the importance of your project.
+Visualization of knowledge is important to foster learning.
+To optimize the representation of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context.
+This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics.
+This form of presenting the knowledge should make it easy to examine materials that form the basis for the topics the audience is interested in.\\
 
-  (target size: 15-20 lines)
+Consider the typical lecture one attends as a student.
+Towards the end of the lecture students might have difficulties remembering earlier topics.
+When introducing a new topic it would be ideal to have a simple way to find the knowledge dependencies and present students with a simple way to catch up.\\
+
+If this research is successful one could envision connecting all of Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class.
+As such it will foster learning and could transform how we interact with course material as a whole.
+It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\
 
@@
 
-  This, like the rest, addresses fellow experts from your field (but
-  not from your particular topic of research). Here you should
-  technically connect to the main concepts from that field and give an
-  outline of your project, stating the research/engineering question
-  that you want to get answered by your project.
+-addresses fellow experts from your field (but not from your particular topic of research). 
+- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.
 

### 2014-11-18 Proposal.tex
Updates to Introduction and general structure

@@
  \section*{Abstract}
-
 Visualization of knowledge is important to foster learning.
@@
 
-If this research is successful one could envision connecting all of Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class.
+The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.
+Using OMDoc, this research aims to visualize connecting some of what is written on Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class.
 As such it will foster learning and could transform how we interact with course material as a whole.
@@
   \section{Statement and Motivation of Research}
-
   This part should make clear which question, exactly, you are
@@
 
+(target size: 3-4 pages)
+
+\subsection{OMDoc}
+(half a page)
+\vspace*{8cm}
+\subsection{Spatial Narration}
+What is Prezi?
+(half a page)
+\vspace*{8cm}
+\subsection{Combining OMDoc and Spatial Narration}
 What is the idea?
+(half a page)
+\newpage
+\subsection{Positive Effects of the Combination of Spatial Narration and OMDoc}
 Why is this important for the world?
-
-What is Prezi?
 How will this improve learning?
-What's the best representation one could do
-
+(1 page)
+\newpage
+\subsection{Different Representations of Data}
+What's the best representation one could do?
+(1 page)
   (target size: 3-5 pages)
@@
 
-3. Planning
 How will this be implemented?
@@
 
-  (target size: 3-4 pages)
+\subsection{Forming Visualizations out of Knowledge Graphs which Convey Meaning}
+(1 page)
 \newpage
+
+\subsection{Ordered Knowledge Graphs}
+(1 page)
+\newpage
+
+\subsection{Meaningful Representation of Knowledge Graphs}
+(1 page)
+\newpage
+
 \section{Evaluation Criteria}
+
+????
 

### 2014-11-19 Proposal.tex
changes to abstract, adding ideas to intro, adding bibliography

@@
 \usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
-
+\usepackage{etoolbox}
+\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
 \usepackage{abstract} % Allows abstract customization
@@
 
-The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.
-Using OMDoc, this research aims to visualize connecting some of what is written on Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class.
+The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.\cite{OMDoc book} Using OMDoc, this research aims to visualize connecting some of what is written on Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class.
 As such it will foster learning and could transform how we interact with course material as a whole.
@@
 
+"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase}
+
+In this paper we want to go form merely displaying information to representing knowledge by displaying a network/context the information is in.
+In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
+context the information is in.\cite{Probst} \\
+
 -addresses fellow experts from your field (but not from your particular topic of research). 
 - Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.
-
   (target size: 1 page)
@@
 
+\newpage
+\section{References}
+\begin{thebibliography}{} % Bibliography - this is intentionally simple in this template
+\bibitem {Kohlhase}
+Kohlhase, Michael. "320441 CompLog Lecture Notes." (n.d.): n. pag. 17 Nov. 2014. Web. 19 Nov. 2014.
+\bibitem {OMDoc book}
+Kohlhase, Michael, and Alan Bundy. OMDoc - an Open Markup Format for Mathematical Documents. Berlin: SpringerLink, 2006. Print.
+\bibitem {Probst}
+Probst, Gilbert, Steffen Raub, and Kai Romhardt. \newblock Wissen Managen. \newblock Wiesbaden: S.n., 1997. Print.
+\end{thebibliography}
+
 \end{document}

### 2014-11-19 Proposal.tex
adding changes fromthe meeting

@@
 \usepackage{pgfgantt}
+\usepackage[show]{ed}
 \usepackage[sc]{mathpazo} % Use the Palatino font
@@
 - Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.
+
+Why is this important for the world?
+How will this improve learning?
+More effective education.
+
 (target size: 1 page)
+
+\ednote{Include in introduction Statement and Motivation of Research  } 
 \newpage 
-  \section{Statement and Motivation of Research}
+\section{Preliminaries}
   This part should make clear which question, exactly, you are
@@
 (target size: 3-4 pages)
+\ednote {explain primitives and apply to prezi.}
 
@@
 \vspace*{8cm}
-\subsection{Combining OMDoc and Spatial Narration}
-What is the idea?
-(half a page)
-\newpage
-\subsection{Positive Effects of the Combination of Spatial Narration and OMDoc}
-Why is this important for the world?
-How will this improve learning?
-(1 page)
-\newpage
 \subsection{Different Representations of Data}
@@
 (1 page)
-  (target size: 3-5 pages)
-\newpage
+
 \section{Planned Investigation}
@@
 (1 page)
+
+\ednote{evaluation criteria from lecture slides}
+\newpage
+
+\section{Work Plan}
+\subsection{WP1: Understand API of Prezi or similar software}
+
+\subsection{WP2: Combining OMDoc and Spatial Narration}
+
+What is the idea?
+(half a page)
+\newpage
+\subsection{WP3: Evaluation}
+1. Positive Effects of the Combination of Spatial Narration and OMDoc
+2. How fast does this work?
+-> qualitative analysis.
+
+(1 page)
+\newpage
+  (target size: 3-5 pages)
 \newpage
@@
 
-????
+\ednote{When do I feel successful?\\
+-running system (or I can tell why it didn't/couldn't work) \& \\
+-users can understand it and reconstruct the original graph. }
 
@@
 \end{itemize}
+
+\ednote {wp 4 - thesis writing}
 
@@
 %tasks
-\ganttbar{Preliminary development}{2}{10} \\
-\ganttbar{Graph visualization}{11}{16} \\
-\ganttbar{Testing \& Performance}{17}{20} \\
-\ganttbar{Final Report submission}{21}{21.5}
+\ganttbar{WP 1}{2}{10} \\
+\ganttbar{WP 2}{11}{16} \\
+\ganttbar{WP 3}{17}{20} \\
+\ganttbar{WP 4}{21}{21.5}
 
@@
 
+\ednote {
+-knowledge representation, semantic web
+}
+
 \end{document}

### 2014-11-23 Proposal.tex
add stuff about linguistics and impress.js

@@
 \title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}} % Article title
+
+%----------------------------------------------------------------------------------------
+% Macros
+%----------------------------------------------------------------------------------------
+\newcommand{\sys}{Knowledge Presentation System}
 
@@
 
+\sys
+
+\ednote{
+not towards a semantic representation of data but towards representing the network and context to not display information but represent knowledge http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
+\ednote{Knowledge Representation in the Social Semantic Web} 
 \ednote{Include in introduction Statement and Motivation of Research  }
+
+\ednote{link}
+% http://reader.eblib.com/(S(gkwt4h53aadjotp03mi25zsi))/Reader.aspx?p=655998&o=1706&u=tkyUhRRU8oBFV92xtGUdWNHfafo%3d&t=1416427415&h=AAEABAAD4041366D9CC8528AF618690B20349073&s=31025691&ut=5736&pg=1&r=img&c=-1&pat=n&cms=-1&sd=2
+
 \newpage 
@@
 \vspace*{8cm}
+\subsection{Status of Information within Discourse}
+
+In linguistics the concept of information packaging is know.
+Within this one discriminates between \textit{familiar} and \textit{old} information.
+Familiar information is shared by speaker and addressee whereas new information not.
+In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\
+
+[1] \textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}
+
+In this example in the first part of the sentence information pertaining to my sister and to a circus are introduced, i.e.
+\textit{discourse-new}.
+In the second part the underlined parts are considered \textit{discourse-old} since they have already been introduced.\cite{Cambridge}\\
+
+These concepts can be adapted to the situation of teaching Mathematics or Computer Science to students in a class.
+In general the information that the speaker is sharing with the addressees/students is \textit{discourse-new}\ednote{call course-new?} and depend on  information that is \textit{discourse-old}.
+I would like to introduce the term \textit{discourse-ancient} which covers the situation where the addressee has difficulties following the speaker since the \textit{discourse-new} information depends on \textit{discourse-old} information that might be 'too old', i.e.
+ancient, to be easily remembered.
+
+(half a page)
+\vspace*{8cm}
+
+\subsection{Context}
+
 \subsection{Spatial Narration}
@@
 \section{Work Plan}
-\subsection{WP1: Understand API of Prezi or similar software}
+\subsection{WP1: Understand API of Impress.js}
+
+Prezi is a software that has changed how people think about presentations.
+When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.
+Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi.
+Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress}
 
@@
 
-\ednote{When do I feel successful?\\
--running system (or I can tell why it didn't/couldn't work) \& \\
--users can understand it and reconstruct the original graph. }
+\ednote{When do I feel successful? when I have running system (or I can tell why it didn't/couldn't work) or when users can understand it and reconstruct the original graph. }
 
@@
 \begin{thebibliography}{} % Bibliography - this is intentionally simple in this template
+\bibitem {Cambridge}
+Huddleston, Rodney, Geoffrey K.
+Pullum, Laurie Bauer, Betty J.
+Birner, and Ted Briscoe.
+"Chapter 16 Information Packaging." The Cambridge Grammar of the English Language.
+Cambridge: Cambridge UP, 2002.
+N.
+pag.
+Print.
 \bibitem {Kohlhase}
@@
 Probst, Gilbert, Steffen Raub, and Kai Romhardt. \newblock Wissen Managen. \newblock Wiesbaden: S.n., 1997. Print.
+\bibitem {Impress}
+Szopka, Bartek. "Impress.js." Impress.js. Github, 28 Dec. 2011. Web. 23 Nov. 2014.
+
 \end{thebibliography}

### 2014-11-24 Proposal.tex
Introduction and several other additions

@@
 \usepackage[show]{ed}
+\setlength{\parindent}{0pt}
 \usepackage[sc]{mathpazo} % Use the Palatino font
@@
 \begin{flushright}
-    \includegraphics[scale=0.7]{Logo}
+    \includegraphics[scale=1.0]{Logo}
   \end{flushright}
@@
 Visualization of knowledge is important to foster learning.
-To optimize the representation of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context.
+To optimize the visualization of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context.
 This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics.
@@
 
-The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.\cite{OMDoc book} Using OMDoc, this research aims to visualize connecting some of what is written on Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class.
+The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.\cite{OMDoc book} Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories.
 As such it will foster learning and could transform how we interact with course material as a whole.
@@
 
-"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase}
+The Semantic Web approach aims to transform the World Wide Web (WWW) from a mere information space to an information web that is processable by machines.\cite{SemWeb} There exists an interesting similarity in other fields such as that of new presentation tools that aim to enable you to present information in a more interconnected way that provides context.
+Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\
 
-In this paper we want to go form merely displaying information to representing knowledge by displaying a network/context the information is in.
+These two developments have more in common than one would think.
+Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge.\cite{Weller} Here the processing of information to provide knowledge is lacking.
+Similarly I would argue that the existance of tools like Powerpoint have lead to virtually everyone doing presentations.
+As everyone who has witnessed many presentation knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\
+
+Semantic Web is aiming to change the former, whereas new, more visual presentation tools provide a solution to help provide presentations that are easier to process and thus will facilitate knowledge transfer.
+This research intends to bridge the gap and provide a tool for contextual visualization of information.
+It adapts some of the concepts of the semantic web on a smaller scale.
+
+In this paper we want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in.
 In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
-context the information is in.\cite{Probst} \\
+context the information is in.
 
--addresses fellow experts from your field (but not from your particular topic of research). 
-- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.
+\ednote{INSERT GRAPH that leads from info to knowledge
+\cite{Probst} \\}
 
-Why is this important for the world?
-How will this improve learning?
-More effective education.
+"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase} That said, it is imperative to facilitate knowledge transfer.
+Thus, we will examine how visually representing information and its context can make knowledge transfer easier.
+For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information.
+We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.
 
-(target size: 1 page)
+To exemplify this: Annie, a young student learning Spanish is watching her teacher give a presentation on how to form sentences.
+She wants to form the sentence 'I read books'.
+After struggling and looking up the word for reading she forms the sentence 'Yo leer libros'.
+For this Annie had to find the dependency on knowing the vocabulary words for 'I', 'read', and 'books'.
+However Annie made a mistake and did not know that the verb 'leer' needs to be conjugated appropriately.
+Her teacher tells her this.
+Now Annie has to try to find the information on how to conjugate verbs.
+This shows the dependencies of different pieces of information, i.e.
+the formulation of a sentence depends on knowledge of grammar and vocabulary.
+In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.
 
-\sys
+After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was looking at at the time.
+Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
 
-\ednote{
-not towards a semantic representation of data but towards representing the network and context to not display information but represent knowledge http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
-\ednote{Knowledge Representation in the Social Semantic Web} 
-\ednote{Include in introduction Statement and Motivation of Research  }
-
+\ednote{-addresses fellow experts from your field (but not from your particular topic of research). }
+\ednote{- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.}
+\ednote{Why is this important for the world? How will this improve learning? ->More effective education. }
+\ednote{(target size: 1 page)}
+\ednote{http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
 \ednote{link}
@@
 
-\newpage 
 \section{Preliminaries}
-  This part should make clear which question, exactly, you are
-  pursuing, and why your project is relevant/interesting. This is the
-  place to cite relevant literature. Where does your project extend
-  the state of the art? what weaknesses in known approaches to you
-  hope to overcome? If you have carried out preliminary experiments,
-  describe them here.
+\ednote{ This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting.
+This is the place to cite relevant literature.
+Where does your project extend the state of the art?
+what weaknesses in known approaches to you hope to overcome?
+If you have carried out preliminary experiments, describe them here.}
 
@@
 In linguistics the concept of information packaging is know.
-Within this one discriminates between \textit{familiar} and \textit{old} information.
+Within this, one discriminates between \textit{familiar} and \textit{old} information.
 Familiar information is shared by speaker and addressee whereas new information not.
@@
 
-[1] \textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}
+[1] \textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}\\
 
@@
 I would like to introduce the term \textit{discourse-ancient} which covers the situation where the addressee has difficulties following the speaker since the \textit{discourse-new} information depends on \textit{discourse-old} information that might be 'too old', i.e.
-ancient, to be easily remembered.
-
-(half a page)
-\vspace*{8cm}
+ancient, to be easily remembered.\\
 
 \subsection{Context}
+
+\ednote{prezi - cell example.}
 
@@
 
-Prezi is a software that has changed how people think about presentations.
+The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later: Prezi is a software that has changed how people think about presentations.
 When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.
 Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi.
-Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress}
+Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress}\ednote{Impressionist and jimpress}\\
+
+the development of of presentation tools like Prezi,  "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas"\cite{Prezi}
 
@@
 \newpage
-\subsection{WP3: Evaluation}
+
+\subsection{WP3: Implement OMDoc examples in Impress.js}
+\newpage
+
+\subsection{WP4: Evaluation}
 1. Positive Effects of the Combination of Spatial Narration and OMDoc
@@
 \begin{thebibliography}{} % Bibliography - this is intentionally simple in this template
+
+\bibitem {SemWeb}
+Berners-Lee, Tim. "Semantic Web Road Map." Semantic Web Roadmap. World Wide Web Consortium, Sept. 1998. Web. 23 Nov. 2014.
+\bibitem {Prezi}
+"Hi, We're Prezi." Prezi.com. N.p., n.d. Web. 23 Nov. 2014.
 \bibitem {Cambridge}
@@
 Szopka, Bartek. "Impress.js." Impress.js. Github, 28 Dec. 2011. Web. 23 Nov. 2014.
-
+\bibitem {Weller}
+Weller, Katrin. Knowledge Representation in the Social Semantic Web. New York: De Gruyter Saur, 2010. Print.
 \end{thebibliography}
 
-\ednote {
--knowledge representation, semantic web
-}
+\ednote{Research field: information systems}
 

### 2014-11-24 Proposal.tex
several additions

@@
 \section{Preliminaries}
+To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution.
+While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.
+
 \ednote{ This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting.
@@
 
-(target size: 3-4 pages)
+\ednote{(target size: 3-4 pages)}
 \ednote {explain primitives and apply to prezi.}
@@
 
+\subsection{Primitives}
+
 \subsection{Context}
@@
 
-\subsection{Spatial Narration}
-What is Prezi?
-(half a page)
-\vspace*{8cm}
+\subsection{Spatial Narrative}
+The development of of presentation tools like Impress.js and Prezi, "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas"\cite{Prezi}, has  changed how people think about presentations.
+When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.\\
+
+The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'".
+An example for this is the experience of a tour guide for a certain topic.\cite{Narrative}\\
+
+The benefits of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
+By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
+That is because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form.
+\ednote{find source}\\
+
+In this research we will use this knowledge to form an interconnected web of information that tells a visual story to facilitate the transfer of knowledge.
+
 \subsection{Different Representations of Data}
@@
 
-The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later: Prezi is a software that has changed how people think about presentations.
-When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.
+The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later.
 Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi.
-Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress}\ednote{Impressionist and jimpress}\\
-
-the development of of presentation tools like Prezi,  "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas"\cite{Prezi}
+Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress} \ednote{Impressionist and jimpress}\\
 
@@
 \subsection{WP4: Evaluation}
-1. Positive Effects of the Combination of Spatial Narration and OMDoc
-2. How fast does this work?
--> qualitative analysis.
 
-(1 page)
-\newpage
-  (target size: 3-5 pages)
+Perform qualitative analysis of the visualization produced by the implementet \sys.
+Determine whether the implemented \sys meats the goals that were outlined in the Evaluation Criteria.
+Measure the speed of the system.
+\ednote{SMART goals?}
 \newpage
@@
 
-  This section discusses criteria which can be used to evaluate the
-  research results and which can be used to related research results
-  to the already known state-of-the-art.
+The evaluation criteria for the research at hand are as follows. 
+\begin{enumerate}
+\item Does the \sys that was developed allow for the creation of a full presentation out of a given annotated document?
+\item  How fast does the \sys work? Can this be used in real time? Could a student request a presentation on a certain topic and could this be generated on the fly within seconds?
+\item Does a qualitative analysis yield the result that the developed system provide a better system for knowledge transfer?
+\item What are the possitive effects on the combination of Spatial Narrative and OMDoc?
+\item Are there negative side effects?
+\end{enumerate}
+\ednote{I am missing SMART goals... Can I use a scale from 0 - 10 for each point?}
 
-  (target size: 1-2 page)
+\ednote{(target size: 1-2 page)}
 \newpage
@@
 Kohlhase, Michael, and Alan Bundy. OMDoc - an Open Markup Format for Mathematical Documents. Berlin: SpringerLink, 2006. Print.
+\bibitem{Narrative}
+M{\o}ller-Jensen, Lasse.
+"Mobile GIS Strategies for Disseminating Thematic Tourist Information: Examples of Spatial Narratives." Diss.
+U of Copenhagen, n.d.
+Web.
+24 Nov.
+2014.
+\href{http://ifgi.uni-muenster.de/archives/tipugg/paper/tipugg2008_Lasse.pdf}{http://ifgi.uni-muenster.de/archives/tipugg/paper/tipugg2008\_Lasse.pdf}.
 \bibitem {Probst}

### 2014-11-24 Proposal.tex
updated work packages and evalutation criteria

@@
 For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information.
-We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.
+We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.\\
 
@@
 
-\subsection{WP2: Combining OMDoc and Spatial Narration}
+\subsection{WP2: Using OMDoc to create ordered information graphs}
+The idea is to use the General Computer Science Lecture notes as an experiment.
+The General Computer Science Lecture notes are an annotated set of documents.
+Using OMDoc, we will create an information graph out of the annotated set of documents.
+This information graph should be ordered based on dependencies of knowledge.\\
 
-What is the idea?
-(half a page)
-\newpage
+\subsection{WP3: Combining OMDoc and Spatial Narration}
+Once we have an ordered information graph we will visualize the information in different ways and analyze each way.
+The outcome of the analysis should be a model which we will then use to visualize the information in WP4.\\
 
 \subsection{WP3: Implement OMDoc examples in Impress.js}
-\newpage
+After the best model for spatial narration is found, we will implement a system that will take the ordered information graph and transform it into a spatial presentation using Impress.js.
 
 \subsection{WP4: Evaluation}
-
-Perform qualitative analysis of the visualization produced by the implementet \sys.
-Determine whether the implemented \sys meats the goals that were outlined in the Evaluation Criteria.
-Measure the speed of the system.
-\ednote{SMART goals?}
-\newpage
+Once we have results, a qualitative analysis of the visualization produced by the implemented \sys should be perfomed.
+In addition we will determine whether the implemented \sys meets the goals outlined in the Evaluation Criteria.
+Lastly we will measure the speed of the system.
 

### 2014-11-24 Proposal.tex
updated many small things

@@
 
-\subsection{WP3: Implement OMDoc examples in Impress.js}
+\subsection{WP4: Implement OMDoc examples in Impress.js}
 After the best model for spatial narration is found, we will implement a system that will take the ordered information graph and transform it into a spatial presentation using Impress.js.
 
-\subsection{WP4: Evaluation}
+\subsection{WP5: Evaluation}
 Once we have results, a qualitative analysis of the visualization produced by the implemented \sys should be perfomed.
@@
 
-\ednote{When do I feel successful? when I have running system (or I can tell why it didn't/couldn't work) or when users can understand it and reconstruct the original graph. }
+\ednote{should users be able to reconstruct the original graph after a presentation? }
 
@@
 \item Does a qualitative analysis yield the result that the developed system provide a better system for knowledge transfer?
-\item What are the possitive effects on the combination of Spatial Narrative and OMDoc?
+\item What are the positive effects on the combination of Spatial Narrative and OMDoc?
 \item Are there negative side effects?
@@
 \ednote{I am missing SMART goals... Can I use a scale from 0 - 10 for each point?}
+
+If the implemented \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
+If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers what is impossible.
+\\
+
+A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
 
@@
 \begin{itemize}
-\item \textbf{Until February 15th}: Complete preliminary development to create a presentation from an XML
-\item \textbf{Until April 1st}: Complete development of organized presentations that are generated from ordered knowledge graphs.
-\item \textbf{Until May 1st}: Testing and Performance Measurement.
-\item \textbf{Until May 10th}: Complete development of organized presentations that are generated from ordered knowledge graphs.
+\item \textbf{Until February 1st}: Understanding the API of Impress.js
+\item \textbf{Until March 1st}: Complete the creation of ordered information graphs using OMDoc
+\item \textbf{Until March 15th}: Find an ideal model for the visualization of the information graph
+\item \textbf{Until April 15th}: Implement/Automate the visualization of the information graph
+\item \textbf{Until May 10th}: Qualitative Analysis and evaluation of findings 
 \end{itemize}
@@
 %tasks
-\ganttbar{WP 1}{2}{10} \\
-\ganttbar{WP 2}{11}{16} \\
-\ganttbar{WP 3}{17}{20} \\
-\ganttbar{WP 4}{21}{21.5}
-
+\ganttbar{WP 1}{2}{8} \\
+\ganttbar{WP 2}{9}{12} \\
+\ganttbar{WP 3}{11}{14} \\
+\ganttbar{WP 4}{15}{18}\\
+\ganttbar{WP 5}{19}{21.5}
 %relations 
@@
 \ganttlink{elem2}{elem3} 
+\ganttlink{elem3}{elem4} 
 \end{ganttchart}

### 2014-11-28 Proposal.tex
after meeting
small change

@@
 \usepackage{hyperref} % For hyperlinks in the PDF
-
+\usepackage{xspace}
 \usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
@@
 \usepackage{titlesec} % Allows customization of titles
-\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
-\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
+%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
+%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
 \titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
@@
 %----------------------------------------------------------------------------------------
-\newcommand{\sys}{Knowledge Presentation System}
+\newcommand{\sys}{Knowledge Presentation System\xspace}
 
@@
 
-In this paper we want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in.
+In this proposed research, we want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in.
 In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
@@
 "Mobile GIS Strategies for Disseminating Thematic Tourist Information: Examples of Spatial Narratives." Diss.
-U of Copenhagen, n.d.
+University of Copenhagen, n.d.
 Web.

### 2014-11-28 Proposal.tex
switch to bibtex

@@
 \titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles
-
+\usepackage{cite}
 \usepackage{fancyhdr} % Headers and footers
@@
 
-The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.\cite{OMDoc book} Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories.
+The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
+Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories.
 As such it will foster learning and could transform how we interact with course material as a whole.
@@
 
-The Semantic Web approach aims to transform the World Wide Web (WWW) from a mere information space to an information web that is processable by machines.\cite{SemWeb} There exists an interesting similarity in other fields such as that of new presentation tools that aim to enable you to present information in a more interconnected way that provides context.
+The Semantic Web \cite{BernersLee:tsw98} approach aims to transform the World Wide Web (WWW) from a mere information space to an information web that is processable by machines.
+There exists an interesting similarity in other fields such as that of new presentation tools that aim to enable you to present information in a more interconnected way that provides context.
 Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\
@@
 These two developments have more in common than one would think.
-Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge.\cite{Weller} Here the processing of information to provide knowledge is lacking.
+Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge \cite{Weller:npentrel14}.
+Here the processing of information to provide knowledge is lacking.
 Similarly I would argue that the existance of tools like Powerpoint have lead to virtually everyone doing presentations.
@@
 
-\ednote{INSERT GRAPH that leads from info to knowledge
-\cite{Probst} \\}
+\ednote{INSERT GRAPH that leads from info to knowledge}
+\cite{ProbstRaubRomhardt}
 
-"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase} That said, it is imperative to facilitate knowledge transfer.
+"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
 Thus, we will examine how visually representing information and its context can make knowledge transfer easier.
@@
 
-In linguistics the concept of information packaging is know.
+In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is know.
 Within this, one discriminates between \textit{familiar} and \textit{old} information.
@@
 \textit{discourse-new}.
-In the second part the underlined parts are considered \textit{discourse-old} since they have already been introduced.\cite{Cambridge}\\
+In the second part the underlined parts are considered \textit{discourse-old} since they have already been introduced.\\
 
@@
 \subsection{Spatial Narrative}
-The development of of presentation tools like Impress.js and Prezi, "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas"\cite{Prezi}, has  changed how people think about presentations.
+The development of of presentation tools like Impress.js and Prezi, "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}, has  changed how people think about presentations.
 When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.\\
 
-The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'".
-An example for this is the experience of a tour guide for a certain topic.\cite{Narrative}\\
+The concept of Spatial Narrative \cite{SpatialNarratives:npentrel14} stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'".
+An example for this is the experience of a tour guide for a certain topic.\\
 
@@
 Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi.
-Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress} \ednote{Impressionist and jimpress}\\
+Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions.
+\ednote{Impressionist and jimpress}\\
 
@@
 
-\newpage
 \section{References}
-\begin{thebibliography}{} % Bibliography - this is intentionally simple in this template
-
-\bibitem {SemWeb}
-Berners-Lee, Tim. "Semantic Web Road Map." Semantic Web Roadmap. World Wide Web Consortium, Sept. 1998. Web. 23 Nov. 2014.
-\bibitem {Prezi}
-"Hi, We're Prezi." Prezi.com. N.p., n.d. Web. 23 Nov. 2014.
-\bibitem {Cambridge}
-Huddleston, Rodney, Geoffrey K.
-Pullum, Laurie Bauer, Betty J.
-Birner, and Ted Briscoe.
-"Chapter 16 Information Packaging." The Cambridge Grammar of the English Language.
-Cambridge: Cambridge UP, 2002.
-N.
-pag.
-Print.
-\bibitem {Kohlhase}
-Kohlhase, Michael. "320441 CompLog Lecture Notes." (n.d.): n. pag. 17 Nov. 2014. Web. 19 Nov. 2014.
-\bibitem {OMDoc book}
-Kohlhase, Michael, and Alan Bundy. OMDoc - an Open Markup Format for Mathematical Documents. Berlin: SpringerLink, 2006. Print.
-\bibitem{Narrative}
-M{\o}ller-Jensen, Lasse.
-"Mobile GIS Strategies for Disseminating Thematic Tourist Information: Examples of Spatial Narratives." Diss.
-University of Copenhagen, n.d.
-Web.
-24 Nov.
-2014.
-\href{http://ifgi.uni-muenster.de/archives/tipugg/paper/tipugg2008_Lasse.pdf}{http://ifgi.uni-muenster.de/archives/tipugg/paper/tipugg2008\_Lasse.pdf}.
-\bibitem {Probst}
-Probst, Gilbert, Steffen Raub, and Kai Romhardt. \newblock Wissen Managen. \newblock Wiesbaden: S.n., 1997. Print.
-\bibitem {Impress}
-Szopka, Bartek. "Impress.js." Impress.js. Github, 28 Dec. 2011. Web. 23 Nov. 2014.
-\bibitem {Weller}
-Weller, Katrin. Knowledge Representation in the Social Semantic Web. New York: De Gruyter Saur, 2010. Print.
-\end{thebibliography}
 
@@
 
+\bibliography{kwarc}{}
+\bibliographystyle{alpha}
 \end{document}

### 2014-11-28 Proposal.tex
implemented comments on the printed out proposal

@@
 
-The Semantic Web \cite{BernersLee:tsw98} approach aims to transform the World Wide Web (WWW) from a mere information space to an information web that is processable by machines.
-There exists an interesting similarity in other fields such as that of new presentation tools that aim to enable you to present information in a more interconnected way that provides context.
+The Semantic Web \cite{BernersLee:tsw98} approach aims to transform the World Wide Web (WWW) from a web of mere human readable information to an information web that is processable by machines.
+There is an interesting similarity in other fields such as that of new presentation tools that aim to enable the presentation of information in a more interconnected way that provides context.
 Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\
@@
 Here the processing of information to provide knowledge is lacking.
-Similarly I would argue that the existance of tools like Powerpoint have lead to virtually everyone doing presentations.
-As everyone who has witnessed many presentation knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\
+Similarly I would argue that the existence of tools like Powerpoint have lead to virtually everyone doing presentations.
+As everyone who has witnessed many presentations knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\
 
 Semantic Web is aiming to change the former, whereas new, more visual presentation tools provide a solution to help provide presentations that are easier to process and thus will facilitate knowledge transfer.
-This research intends to bridge the gap and provide a tool for contextual visualization of information.
+The work proposed here intends to bridge the gap and provide a tool for contextual visualization of information.
 It adapts some of the concepts of the semantic web on a smaller scale.
 
-In this proposed research, we want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in.
+We want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in.
 In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
@@
 
-In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is know.
+In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known.
 Within this, one discriminates between \textit{familiar} and \textit{old} information.
-Familiar information is shared by speaker and addressee whereas new information not.
+\textit{Familiar} information is shared by speaker and addressee, ie.
+common ground, whereas new information not.
 In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\
@@
 (1 page)
-
-\section{Planned Investigation}
-
-  This is the technical core of the proposal. Here you lay out your
-  plans of how you want to answer your research question specify your
-  design of experiments or simulations, point out difficulties that
-  you expect to encounter, etc.
-
-How will this be implemented?
-Using which frameworks?
-
-\subsection{Forming Visualizations out of Knowledge Graphs which Convey Meaning}
-(1 page)
-\newpage
-
-\subsection{Ordered Knowledge Graphs}
-(1 page)
-\newpage
-
-\subsection{Meaningful Representation of Knowledge Graphs}
-(1 page)
+Forming Visualizations out of Knowledge Graphs which Convey Meaning
+Meaningful Representation of Knowledge Graphs
 
@@
 \section{Work Plan}
+\ednote {Add some speculation HOW}
 \subsection{WP1: Understand API of Impress.js}
-
+\ednote {should Impress.js go into the introduction/preliminaries? - I decided agains this as I haven't examined Impress.js enough yet.}
 The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later.
@@
 \subsection{WP2: Using OMDoc to create ordered information graphs}
-The idea is to use the General Computer Science Lecture notes as an experiment.
+The idea is to use the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} as an experiment.
 The General Computer Science Lecture notes are an annotated set of documents.
@@
 \subsection{WP5: Evaluation}
-Once we have results, a qualitative analysis of the visualization produced by the implemented \sys should be perfomed.
+Once we have examples, we will undertake a qualitative analysis of the visualization produced by the implemented \sys .
 In addition we will determine whether the implemented \sys meets the goals outlined in the Evaluation Criteria.
@@
 
-The evaluation criteria for the research at hand are as follows. 
-\begin{enumerate}
-\item Does the \sys that was developed allow for the creation of a full presentation out of a given annotated document?
-\item  How fast does the \sys work? Can this be used in real time? Could a student request a presentation on a certain topic and could this be generated on the fly within seconds?
-\item Does a qualitative analysis yield the result that the developed system provide a better system for knowledge transfer?
-\item What are the positive effects on the combination of Spatial Narrative and OMDoc?
-\item Are there negative side effects?
-\end{enumerate}
+The evaluation criteria for the research at hand are on the one hand systematic and on the otherhand cognitive.
+Systematically we will be evaluating two main challenges: First we will evaluate whether the \sys that was developed allows for the creation of a full presentation from a given annotated document.
+Then we will evaluate the speed of the \sys .
+Special attention will be given to the question whether this could be used in real time such that a student could request a presentation on a certain topic and could this be generated on the fly within seconds.\\
+
+Cognitively we will be examining whether the developed system provides a better system for knowledge transfer.
+For this a qualitative analysis will be conducted.
+Based on that we will be able to understand the positive and possibly negative effects of the combination of Spatial Narrative and OMDoc.
+
 \ednote{I am missing SMART goals... Can I use a scale from 0 - 10 for each point?}
@@
 A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
+It is not the goal of this research that users should be able to reconstruct the original graph from the presentation.
 
@@
 
+\newpage
 \section{References}

### 2014-11-29 Proposal.tex
OMDoc part

@@
 
+\newenvironment{myfont}{\fontfamily{\sfdefault}\selectfont}{\par}
+
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\newcommand{\sys}{Knowledge Presentation System\xspace}
+\newcommand{\sys}{\textsc{Knowtation}\xspace}
 
@@
 The work proposed here intends to bridge the gap and provide a tool for contextual visualization of information.
-It adapts some of the concepts of the semantic web on a smaller scale.
+It adapts some of the concepts of the semantic web on a smaller scale.\\
 
@@
 In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
-context the information is in.
+context the information is in.\\
 
@@
 
-To exemplify this: Annie, a young student learning Spanish is watching her teacher give a presentation on how to form sentences.
-She wants to form the sentence 'I read books'.
-After struggling and looking up the word for reading she forms the sentence 'Yo leer libros'.
-For this Annie had to find the dependency on knowing the vocabulary words for 'I', 'read', and 'books'.
-However Annie made a mistake and did not know that the verb 'leer' needs to be conjugated appropriately.
-Her teacher tells her this.
-Now Annie has to try to find the information on how to conjugate verbs.
+To exemplify this: Annie, a young student learning Math is watching her teacher give a presentation on how to use the Pythagorean theorem.
+She is given a triangle with sides a = 3 cm and b = 4 cm.
+Now she wants to use the theorem to calculate the length of side c.
+Annie already know how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$.
+However Annie made a mistake and did not know what a right triangle is.
+Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle.
+Now Annie has to try to find out what a right triangle is.
 This shows the dependencies of different pieces of information, i.e.
-the formulation of a sentence depends on knowledge of grammar and vocabulary.
-In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.
+the Pythagorean theorem depends on knowledge of squares, lengths, area calculation, angles, and right angles.
+In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\
 
@@
 Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
+\\
 
@@
 % http://reader.eblib.com/(S(gkwt4h53aadjotp03mi25zsi))/Reader.aspx?p=655998&o=1706&u=tkyUhRRU8oBFV92xtGUdWNHfafo%3d&t=1416427415&h=AAEABAAD4041366D9CC8528AF618690B20349073&s=31025691&ut=5736&pg=1&r=img&c=-1&pat=n&cms=-1&sd=2
-
+\ednote{use Knowledge Presentation System}
+\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn.
+question: how does the spatial narrative work - should we use the inherent semantic closeness
+}
 \section{Preliminaries}
 To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution.
-While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.
+While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
 
-\ednote{ This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting.
+\ednote{This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting.
 This is the place to cite relevant literature.
@@
 \subsection{OMDoc}
-(half a page)
-\vspace*{8cm}
+OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
+As such it is a semi-formal domain ontology.
+An ontology provides the framework for creating a semantic structure.
+It formally describes concepts within a specified area.
+A semi-formal ontology \cite{Sheth:npentrel14} is an ontology where formality of semantics is not a given.
+The semi-formal ontology can consist of partial or incomplete knowledge.
+\\
+
+If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways.
+This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts.
+The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations.
+This elevates the net of separate pieces of information that are stored individually to a semantic representation and one step further to knowledge.\\
+
+In \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers".
+The content layers are the mathematical objects, i.e.
+the statements or theories.
+Narrative layers refer to the order the mathematical objects from content layers are presented.
+In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently.
+Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
+
 \subsection{Status of Information within Discourse}
-
+\ednote{intersection of knowledge of student and teacher aka shared knowledge base (also called “content commons”)}
 In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known.
@@
 ancient, to be easily remembered.\\
-
+\ednote {- reference old example from introduction -> and add onto it showing discourse-ancient.}
 \subsection{Primitives}
@@
 \ednote{evaluation criteria from lecture slides}
+\ednote{add how to work packages. -> my first approach will be...}
 \newpage
@@
 \subsection{WP1: Understand API of Impress.js}
-\ednote {should Impress.js go into the introduction/preliminaries? - I decided agains this as I haven't examined Impress.js enough yet.}
-The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later.
+\ednote {should Impress.js go into the introduction/preliminaries? - I decided against this as I haven't examined Impress.js enough yet.}
+The first step to implementing a \sys \ednote{Is the font format ok?} is to understand the tool we want to represent the knowledge in later.
 Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi.
@@
 
-\ednote{should users be able to reconstruct the original graph after a presentation? }
+\ednote {- work out concepts not a binding contract.}
+\ednote{ 1. - 2. system goals -> kinda measurable}
+\ednote{ 3.-5. cognitive goals -> exploring space of information systems}
+
+\ednote{ make 2nd eval criteria last}
 

### 2014-11-29 Proposal.tex
primitives

@@
 \ednote {- reference old example from introduction -> and add onto it showing discourse-ancient.}
+
 \subsection{Primitives}
+
+Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
+Primitives are the different elements of representation.
+In terms of evaluation it is important to have intuitive primitive elements.
+
+For Impress.js, the primitive elements are text, images, frame-like structures, and the visual relation between the different frame-like structures.
+\ednote {not sure whether I understand this correctly}
 

### 2014-11-29 Proposal.tex
context

@@
 In terms of evaluation it is important to have intuitive primitive elements.
+\\
 
@@
 
-\ednote{prezi - cell example.}
+Context can be easily explained with the example of Annie learning the Pythagorean theorem.
+The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e.
+calculating squares, lengths, area calculation, angles, and right angles.
+This is the context that the Pythagorean theorem needs.\\
+
+Within this regard one should also consider context-sensitive and context-opaque\ednote{cite} information.
 

### 2014-11-29 Proposal.tex
update to abstract and intro

@@
     \huge
-    \textbf{Visualization of Theory Graphs of Semantically Annotated Documents in the Form of Spatial Presentations}
+    \textbf{The Combination of Spatial Narrative and Semantic Closeness to derive Visualizations of Theory Graphs}
   \end{center}
@@
 Visualization of knowledge is important to foster learning.
-To optimize the visualization of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context.
-This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics.
-This form of presenting the knowledge should make it easy to examine materials that form the basis for the topics the audience is interested in.\\
+To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context.
+The proposed research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics.
+This form of presenting knowledge should enable users to examine materials they may have forgotten which form the basis for the understanding of the topics the audience is interested in.\\
 
@@
 Towards the end of the lecture students might have difficulties remembering earlier topics.
-When introducing a new topic it would be ideal to have a simple way to find the knowledge dependencies and present students with a simple way to catch up.\\
+When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with a simple way to catch up.\\
 
 The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories.
+Using OMDoc, this research aims to visualize the connections of Mathematical knowledge in a way that allows students to learn the concepts the current topic depends on should they need to refresh their memories.
 As such it will foster learning and could transform how we interact with course material as a whole.
-It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\
+This research has many other real world applications, namely, anywhere where knowledge is supposed to be transferred.\\
 
@@
 
-The Semantic Web \cite{BernersLee:tsw98} approach aims to transform the World Wide Web (WWW) from a web of mere human readable information to an information web that is processable by machines.
-There is an interesting similarity in other fields such as that of new presentation tools that aim to enable the presentation of information in a more interconnected way that provides context.
-Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\
+The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
+There are an interesting similar developments in other fields such as that of new presentation tools.
+These aim to enable the presentation of information in a more interconnected way that provides context.
+Both developments strive to connect pieces of information and through providing context to elevate pure information to knowledge.\\
 
-These two developments have more in common than one would think.
-Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge \cite{Weller:npentrel14}.
+The concept behind these two developments is quite similar.
+Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content.
+Whereas this lead to a lot of information on the web, it provided comparatively little knowledge.
 Here the processing of information to provide knowledge is lacking.
-Similarly I would argue that the existence of tools like Powerpoint have lead to virtually everyone doing presentations.
-As everyone who has witnessed many presentations knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\
+Similarly the existence of tools like Powerpoint have lead to virtually everyone doing presentations in this format.
+As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but are often badly delivered and lack structure and context.
+\\
 
-Semantic Web is aiming to change the former, whereas new, more visual presentation tools provide a solution to help provide presentations that are easier to process and thus will facilitate knowledge transfer.
-The work proposed here intends to bridge the gap and provide a tool for contextual visualization of information.
+In essence, both issues stem from information being generated without enough context or structure.
+This makes the information hard to process by humans and/or machines.
+The Semantic Web hopes to change the former, whereas new, more visual presentation tools using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.
+The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information.
 It adapts some of the concepts of the semantic web on a smaller scale.\\
 
-We want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in.
-In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
-context the information is in.\\
-
-\ednote{INSERT GRAPH that leads from info to knowledge}
-\cite{ProbstRaubRomhardt}
+\begin{center}
+\includegraphics[scale=0.5]{model}
+\end{center}
 
 "Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
-Thus, we will examine how visually representing information and its context can make knowledge transfer easier.
-For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information.
-We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.\\
+The above graph is based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}.
+It shows the path from mere data to knowledge through adding context such that we gain information and then through adding networking to get knowledge.\\
+\newpage
+We want to go from merely displaying information to visualizing information by displaying the network/context a piece of information is in.
+In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
+the context the information is in.
+Specifically we want to examine whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\
 
-To exemplify this: Annie, a young student learning Math is watching her teacher give a presentation on how to use the Pythagorean theorem.
+To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks).
+For this we will be using the OMDoc (Open Mathematical Documents) format which will provide us with an annotated set of documents.
+This will give us information about the semantic closeness of different pieces of information.
+From there on we will visualize the dependencies of the information contained in these documents.
+Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative in the form of an API such as Impress.js to allow for us to show the current piece of information of interest within the network of dependent information.\\
+
+To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem.
 She is given a triangle with sides a = 3 cm and b = 4 cm.
 Now she wants to use the theorem to calculate the length of side c.
-Annie already know how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$.
+Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$.
 However Annie made a mistake and did not know what a right triangle is.
@@
 
-After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was looking at at the time.
+After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
 Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
@@
 
-\ednote{-addresses fellow experts from your field (but not from your particular topic of research). }
-\ednote{- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.}
-\ednote{Why is this important for the world? How will this improve learning? ->More effective education. }
-\ednote{(target size: 1 page)}
-\ednote{http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
-\ednote{link}
-% http://reader.eblib.com/(S(gkwt4h53aadjotp03mi25zsi))/Reader.aspx?p=655998&o=1706&u=tkyUhRRU8oBFV92xtGUdWNHfafo%3d&t=1416427415&h=AAEABAAD4041366D9CC8528AF618690B20349073&s=31025691&ut=5736&pg=1&r=img&c=-1&pat=n&cms=-1&sd=2
-\ednote{use Knowledge Presentation System}
-\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn.
-question: how does the spatial narrative work - should we use the inherent semantic closeness
-}
 \section{Preliminaries}
@@
 \ednote {explain primitives and apply to prezi.}
+
+\subsection{Terminology}
+Information 
+Knowledge
+Context.
 
@@
 \section{Evaluation Criteria}
-
+\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn.
+question: how does the spatial narrative work - should we use the inherent semantic closeness
+}
 \ednote {- work out concepts not a binding contract.}

### 2014-11-29 Proposal.tex
updating preliminaries part 1

@@
 \usepackage{etoolbox}
+\usepackage{eurosym}
 \patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
@@
 Using OMDoc, this research aims to visualize the connections of Mathematical knowledge in a way that allows students to learn the concepts the current topic depends on should they need to refresh their memories.
-As such it will foster learning and could transform how we interact with course material as a whole.
+It will examine if and how spatial narrative and semantic closeness can be combined to foster learning.
+Thus it could transform how we interact with course material and learning as a whole.
 This research has many other real world applications, namely, anywhere where knowledge is supposed to be transferred.\\
@@
 
+\newpage
 \section{Preliminaries}
-To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution.
-While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
+To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution.
+While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
 
 \ednote{This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting.
-This is the place to cite relevant literature.
 Where does your project extend the state of the art?
-what weaknesses in known approaches to you hope to overcome?
-If you have carried out preliminary experiments, describe them here.}
-
-\ednote{(target size: 3-4 pages)}
-\ednote {explain primitives and apply to prezi.}
+what weaknesses in known approaches to you hope to overcome?}
 
 \subsection{Terminology}
-Information 
-Knowledge
-Context.
+Before we delve into the actual subject matter, we need to ensure that the terminology used is understood as intended. In the following we will use the terms information, knowledge, and context.\\
+
+The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
+Looking back at the figure from section 1, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
+For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
+Of special importance for us is the association.
+We will take this as meaning that the knowledge is made up out of several pieces of information that are connected.
+In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used.\\
+
+Merriam-Webster \cite{Webster:npentrel14} defines \textbf{context} as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
+A Context can be easily explained with the example of Annie learning the Pythagorean theorem.
+The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e.
+calculating squares, lengths, area calculation, angles, and right angles.
+This is the context that the Pythagorean theorem needs.
+We will be using the terms context and network almost interchangeably and depend on the reader to have the right intuition about these terms.\\
 
@@
 In \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers".
-The content layers are the mathematical objects, i.e.
+Here, the content layers are the mathematical objects, i.e.
 the statements or theories.
 Narrative layers refer to the order the mathematical objects from content layers are presented.
-In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently.
+Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects.
+In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness.
 Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
@@
 
-\subsection{Context}
-
-Context can be easily explained with the example of Annie learning the Pythagorean theorem.
-The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e.
-calculating squares, lengths, area calculation, angles, and right angles.
-This is the context that the Pythagorean theorem needs.\\
-
-Within this regard one should also consider context-sensitive and context-opaque\ednote{cite} information.
+\ednote {explain primitives and apply to prezi.}
 

### 2014-11-29 Proposal.tex
updating preliminaries part 2

@@
 
-\begin{center}
-\includegraphics[scale=0.5]{model}
-\end{center}
+\begin{figure}[H]
+        \centering
+                \fbox{\includegraphics[width=0.8\textwidth]{model}}
+                \caption{From Data to Knowledge}
+                \label{fig:dataknow}
+\end{figure}
 
 "Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
-The above graph is based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}.
+Figure \ref{fig:dataknow} is based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}.
 It shows the path from mere data to knowledge through adding context such that we gain information and then through adding networking to get knowledge.\\
-\newpage
+
 We want to go from merely displaying information to visualizing information by displaying the network/context a piece of information is in.
@@
 \section{Preliminaries}
-To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution.
+To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
 While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
-
-\ednote{This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting.
-Where does your project extend the state of the art?
-what weaknesses in known approaches to you hope to overcome?}
 
@@
 
-\subsection{Status of Information within Discourse}
-\ednote{intersection of knowledge of student and teacher aka shared knowledge base (also called “content commons”)}
+\subsection{Status of Information within the (Dis)Course}
 In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known.
@@
 \textit{Familiar} information is shared by speaker and addressee, ie.
-common ground, whereas new information not.
-In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\
+it is in the intersection of knowledge of student and teacher.
+New information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
+In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
 
-[1] \textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}\\
+\begin{center}
+\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}\\
+\end{center}
 
-In this example in the first part of the sentence information pertaining to my sister and to a circus are introduced, i.e.
+In this example in the first part of the sentence, information pertaining to my sister and to a circus are introduced, i.e.
 \textit{discourse-new}.
-In the second part the underlined parts are considered \textit{discourse-old} since they have already been introduced.\\
+In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.\\
 
 These concepts can be adapted to the situation of teaching Mathematics or Computer Science to students in a class.
-In general the information that the speaker is sharing with the addressees/students is \textit{discourse-new}\ednote{call course-new?} and depend on  information that is \textit{discourse-old}.
-I would like to introduce the term \textit{discourse-ancient} which covers the situation where the addressee has difficulties following the speaker since the \textit{discourse-new} information depends on \textit{discourse-old} information that might be 'too old', i.e.
-ancient, to be easily remembered.\\
-\ednote {- reference old example from introduction -> and add onto it showing discourse-ancient.}
+In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}.
+Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
+We will additionally introduce a third modus for information called \textit{course-ancient}.
+This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e.
+\textit{course-ancient}.\\
+
+Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
+The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
+The information about squares which Annie still remembers is \textit{course-old}.
+Through the semantic closeness that OMDoc provides us we will be able to determine the status of information within the (dis)course.
+\\
 
@@
 
-For Impress.js, the primitive elements are text, images, frame-like structures, and the visual relation between the different frame-like structures.
-\ednote {not sure whether I understand this correctly}
+For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
+The exact layout of the frames and the best visualization of the relation between the frames is to be determined.
+Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+\ednote {not sure whether I understand this correctly - does this need more explanation?}
 
-\ednote {explain primitives and apply to prezi.}
+\subsection{Different Representations of Information}
+
+Information can be (re)presented in different ways: text, visuals, images, etc.
+Actually everything that is in the world around us conveys information to us.
+A sign of a women on a door conveys to most of us that this is a bathroom for women.
+The information graphs that OMDoc provides us with could also be simply visualized as that - a tree of information.
+But this would not be very engaging and it would be hard for a human to process.
+Similarly traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
+\\
+
+In the proposed research we will focus less on text, tree-like structures, or metaphors like the sign of a woman on a door.
+We will rather focus on the spatial narrative and placing content that inherently belongs together visually close together since this can convey the meaning that these objects belong together.\\
+
+\begin{figure}[H]
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \fbox{\includegraphics[width=\textwidth]{size-of-objects}}
+                \caption{Importance of Objects}
+                \label{fig:imp_objects}
+        \end{subfigure}%
+        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \fbox{\includegraphics[width=\textwidth]{relation}}
+                \caption{Relation of Objects}
+                \label{fig:rel_objects}
+        \end{subfigure}
+        \caption{Conveying Visual Meaning}\label{fig:Objects}
+\end{figure}
+
+The figures above clarify what we mean by 'meaningful representations'.
+Figure \ref{fig:imp_objects} shows how size conveys importance.
+When asked, people generally say that the circle on the left is most important, the ones on the right are less important.
+Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different.
+When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
+
+These perceptions can be used to convey meaning visually.
+For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information.
+From there on it depends how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics.
+Similarly we will employ visual relations as in \ref{fig:rel_objects} to show related content.
+Thus we will provide Annie with a meaningful representation of the information taken from the information graph.
+In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\
+
+\ednote{ These are things I derive from what I have been teaching my APS seminars and have probably been told by multile people during my training as a prezi ambassador.
+Do I need to cite my teaching material?
+Not sure...}
 
 \subsection{Spatial Narrative}
-The development of of presentation tools like Impress.js and Prezi, "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}, has  changed how people think about presentations.
-When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.\\
 
-The concept of Spatial Narrative \cite{SpatialNarratives:npentrel14} stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'".
-An example for this is the experience of a tour guide for a certain topic.\\
+Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}.
+When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.
+The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.\\
+
+The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'" \cite{SpatialNarratives:npentrel14}.
+Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\
 
@@
 By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
-That is because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form.
-\ednote{find source}\\
+That is because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \ednote{Storytelling:npentrel14}.\\
 
-In this research we will use this knowledge to form an interconnected web of information that tells a visual story to facilitate the transfer of knowledge.
-
-\subsection{Different Representations of Data}
-What's the best representation one could do?
-(1 page)
-Forming Visualizations out of Knowledge Graphs which Convey Meaning
-Meaningful Representation of Knowledge Graphs
-
-\ednote{evaluation criteria from lecture slides}
-\ednote{add how to work packages. -> my first approach will be...}
-\newpage
+In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected.
+It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\
 
 \section{Work Plan}
+\ednote{add how to work packages. -> my first approach will be...}
 \ednote {Add some speculation HOW}
@@
 \section{Evaluation Criteria}
+\ednote{Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness}
 \ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn.

### 2014-11-30 Proposal.tex
work packages and evaluation update

@@
  \section*{Abstract}
+ \label{sec:abstract}
 Visualization of knowledge is important to foster learning.
@@
   \section{Introduction}
+  \label{sec:introduction}
 
@@
 \section{Preliminaries}
+\label{sec:preliminaries}
+
 To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
@@
 \subsection{Terminology}
+\label{sec:terminology}
+
 Before we delve into the actual subject matter, we need to ensure that the terminology used is understood as intended. In the following we will use the terms information, knowledge, and context.\\
@@
 \subsection{OMDoc}
+\label{sec:OMDoc}
+
 OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
@@
 \subsection{Status of Information within the (Dis)Course}
+\label{sec:infostatus}
+
 In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known.
@@
 \subsection{Primitives}
+\label{sec:primitives}
 
@@
 \subsection{Different Representations of Information}
+\label{sec:inforep}
 
@@
 
-\ednote{ These are things I derive from what I have been teaching my APS seminars and have probably been told by multile people during my training as a prezi ambassador.
+\ednote{ These are things I derive from what I have been in teaching my APS seminars and have probably been told by multile people during my training as a prezi ambassador.
 Do I need to cite my teaching material?
@@
 \subsection{Spatial Narrative}
+\label{sec:spatialnarrative}
 
@@
 \section{Work Plan}
-\ednote{add how to work packages. -> my first approach will be...}
-\ednote {Add some speculation HOW}
+\label{sec:workplan}
+
 \subsection{WP1: Understand API of Impress.js}
-\ednote {should Impress.js go into the introduction/preliminaries? - I decided against this as I haven't examined Impress.js enough yet.}
-The first step to implementing a \sys \ednote{Is the font format ok?} is to understand the tool we want to represent the knowledge in later.
-Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi.
-Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions.
-\ednote{Impressionist and jimpress}\\
+\label{sec:wp1}
+
+\ednote {should Impress.js go into the introduction/preliminaries? - I decided against this as I haven't examined Impress.js enough yet and this will take several days to do.}
+The first step to implementing \sys \ednote{Is the font format ok?} is to understand the tool we want to represent the knowledge in later.
+Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without using the editor, this research will employ another tool that is inspired by the idea behind Prezi.
+Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions.\\
+
+Impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
+Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation.
+In this step we will define several models of how data is presented within a frame.
+Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}).
+Last but not least we need to create several models of how the relations between the different frames can be portrayed within Impress.js.\\
+
+After finishing this part we should have several different presentation styles and one should be chosen with which we will continue our work.\\
+
+\ednote{look at Impressionist and jimpress when writing actual thesis}\\
 
 \subsection{WP2: Using OMDoc to create ordered information graphs}
+\label{sec:wp2}
+
 The idea is to use the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} as an experiment.
 The General Computer Science Lecture notes are an annotated set of documents.
-Using OMDoc, we will create an information graph out of the annotated set of documents.
-This information graph should be ordered based on dependencies of knowledge.\\
+Using OMDoc, we will create an XML information graph out of the annotated set of documents.\\
+
+The information graph we receive from OMDoc should be topologically sorted based on dependencies of knowledge.
+This will allow us to assign values representing the status of information within the course as as in section \ref{sec:infostatus}.
+It will also allow us to create values for the relative semantic closeness of information which will be needed for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
+Knowing the dependencies and the status of the information will allow us to choose which information to show the user in the close surroundings of the current information we are showing.\\
+
+Each piece of information needs to also have an importance level assigned to it as well (see section \ref{sec:inforep}).
+This ought to be determined by knowing how often the concept is used and how important it is for the student to grasp it.\\
 
 \subsection{WP3: Combining OMDoc and Spatial Narration}
-Once we have an ordered information graph we will visualize the information in different ways and analyze each way.
-The outcome of the analysis should be a model which we will then use to visualize the information in WP4.\\
+\label{sec:wp3}
+
+Once we have an ordered information graph with all the additional attribute values mentioned in section \ref{sec:wp2}, we will create the knowledge presentation system \sys.
+\sys will visualize the information from the graph.
+The outcome of this part should be a general \sys presentation model, that implements the models according to the models chosen in section \ref{sec:wp1}.
+We will then use \sys to visualize the information in WP4.\\
 
 \subsection{WP4: Implement OMDoc examples in Impress.js}
-After the best model for spatial narration is found, we will implement a system that will take the ordered information graph and transform it into a spatial presentation using Impress.js.
+\label{sec:wp4}
+
+\sys will take the ordered information graph of the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} with all the additional attributes we generated in \ref{sec:wp2} and transform it into a spatial presentation using Impress.js.
+This will be done by parsing the created XML and creating the markup that Impress.js is using to create the chosen presentation models from section \ref{sec:wp1}.
+After this work package, we should have one (or more) presentations of the topics covered in the General Computer Science Lecture notes.\\
 
 \subsection{WP5: Evaluation}
-Once we have examples, we will undertake a qualitative analysis of the visualization produced by the implemented \sys .
-In addition we will determine whether the implemented \sys meets the goals outlined in the Evaluation Criteria.
-Lastly we will measure the speed of the system.
+\label{sec:wp5}
+
+Once we have examples, we will undertake a qualitative analysis of the visualization produced by the implemented knowledge presentation system \sys .
+To achieve this, we will use the newly created examples from \ref{sec:wp4} and the general General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base}.
+We will have two groups: a control group that is shown the lecture notes and a test group that is shown the new, interactive Impress.js presentations.
+Afterwards both groups have to answer a set of questions.
+In addition, we will determine whether the implemented \sys meets the goals outlined in the Evaluation Criteria (see section \ref{sec:evalcriteria}).\\
 
 \section{Evaluation Criteria}
-\ednote{Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness}
-\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn.
-question: how does the spatial narrative work - should we use the inherent semantic closeness
-}
-\ednote {- work out concepts not a binding contract.}
-\ednote{ 1. - 2. system goals -> kinda measurable}
-\ednote{ 3.-5. cognitive goals -> exploring space of information systems}
+\label{sec:evalcriteria}
 
-\ednote{ make 2nd eval criteria last}
+The evaluation criteria for the research at hand are on the one hand systematic and on the other hand cognitive.
+Systematically, we will be evaluating two main challenges: First we will evaluate whether the knowledge presentation system \sys that was developed allows for the creation of a full presentation from a given annotated document.
+Then we will evaluate the speed of \sys.
+Special attention will be given to the question whether this could be used in real time such that a student could request a presentation on a certain topic and whether this could be generated on the fly within seconds.\\
 
-The evaluation criteria for the research at hand are on the one hand systematic and on the otherhand cognitive.
-Systematically we will be evaluating two main challenges: First we will evaluate whether the \sys that was developed allows for the creation of a full presentation from a given annotated document.
-Then we will evaluate the speed of the \sys .
-Special attention will be given to the question whether this could be used in real time such that a student could request a presentation on a certain topic and could this be generated on the fly within seconds.\\
+Cognitively, we will be exploring the space of information systems.
+Therefore we will be examining whether the developed system provides a better system for knowledge transfer.
+For this a qualitative analysis will be conducted as outlined in section \ref{sec:wp5}.
+Based on that we will be able to understand the positive and possibly negative effects of the combination of Spatial Narrative and OMDoc within \sys .\\
 
-Cognitively we will be examining whether the developed system provides a better system for knowledge transfer.
-For this a qualitative analysis will be conducted.
-Based on that we will be able to understand the positive and possibly negative effects of the combination of Spatial Narrative and OMDoc.
+Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improfe knowledge transfer.
 
-\ednote{I am missing SMART goals... Can I use a scale from 0 - 10 for each point?}
-
-If the implemented \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
-If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers what is impossible.
-\\
+If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
+If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers what is impossible.\\
 
 A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
-It is not the goal of this research that users should be able to reconstruct the original graph from the presentation.
+It is not the goal of this research that users should be able to reconstruct the original graph from the presentation.\\
 
-\ednote{(target size: 1-2 page)}
-\newpage
 \section{Timeline}
+\label{sec:timeline}
 
@@
 \end{itemize}
-
-\ednote {wp 4 - thesis writing}
-
 \begin{figure}[h]
@@
 
-\ednote{Research field: information systems}
-
 \bibliography{kwarc}{}

### 2014-11-30 Proposal.tex
cleaning up folder structure
yayay only conclusion left

@@
 \usepackage{minted}
+\usepackage{nameref}
 \usemintedstyle{autumn}
@@
 \begin{flushright}
-    \includegraphics[scale=1.0]{Logo}
+    \includegraphics[scale=1.0]{assets/Logo}
   \end{flushright}
@@
 
-    \includegraphics[scale=0.2]{Signature}
+    \includegraphics[scale=0.2]{assets/Signature}
  \hfill Bremen, \today
@@
         \centering
-                \fbox{\includegraphics[width=0.8\textwidth]{model}}
+                \fbox{\includegraphics[width=0.8\textwidth]{assets/model}}
                 \caption{From Data to Knowledge}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{size-of-objects}}
+                \fbox{\includegraphics[width=\textwidth]{assets/size-of-objects}}
                 \caption{Importance of Objects}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{relation}}
+                \fbox{\includegraphics[width=\textwidth]{assets/relation}}
                 \caption{Relation of Objects}
@@
 By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
-That is because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \ednote{Storytelling:npentrel14}.\\
+That is because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \cite{Storytelling:npentrel14}.\\
 
@@
 
-\subsection{WP1: Understand API of Impress.js}
+\subsection{WP1: Understanding API of Impress.js}
 \label{sec:wp1}
@@
 
-\subsection{WP2: Using OMDoc to create ordered information graphs}
+\subsection{WP2: Creation of Ordered Information Graphs using OMDoc}
 \label{sec:wp2}
@@
 
-\subsection{WP3: Combining OMDoc and Spatial Narration}
+\subsection{WP3: Combination OMDoc and Spatial Narration}
 \label{sec:wp3}
@@
 
-\subsection{WP4: Implement OMDoc examples in Impress.js}
+\subsection{WP4: Implementation of OMDoc Examples in Impress.js}
 \label{sec:wp4}
@@
 
-\subsection{WP5: Evaluation}
+\subsection{WP5: Qualitative Analysis and Evaluation of Findings}
 \label{sec:wp5}
@@
 \begin{itemize}
-\item \textbf{Until February 1st}: Understanding the API of Impress.js
-\item \textbf{Until March 1st}: Complete the creation of ordered information graphs using OMDoc
-\item \textbf{Until March 15th}: Find an ideal model for the visualization of the information graph
-\item \textbf{Until April 15th}: Implement/Automate the visualization of the information graph
-\item \textbf{Until May 10th}: Qualitative Analysis and evaluation of findings 
+\item \textbf{Until February 1st}: \nameref{sec:wp1}
+\item \textbf{Until March 1st}: \nameref{sec:wp2}
+\item \textbf{Until March 15th}: \nameref{sec:wp3}
+\item \textbf{Until April 15th}:\nameref{sec:wp4}
+\item \textbf{Until May 10th}: \nameref{sec:wp5}
 \end{itemize}
@@
 %tasks
-\ganttbar{WP 1}{2}{8} \\
-\ganttbar{WP 2}{9}{12} \\
-\ganttbar{WP 3}{11}{14} \\
-\ganttbar{WP 4}{15}{18}\\
-\ganttbar{WP 5}{19}{21.5}
+\ganttbar{\ref{sec:wp1} WP1}{2}{8} \\
+\ganttbar{\ref{sec:wp2} WP2}{9}{12} \\
+\ganttbar{\ref{sec:wp3} WP3}{11}{14} \\
+\ganttbar{\ref{sec:wp4} WP4}{15}{18}\\
+\ganttbar{\ref{sec:wp5} WP5}{19}{21.5}
 %relations 

### 2014-11-30 Proposal.tex
somewhat final draft - ok some more notes from meike and some more research maybe...

@@
 
+It is a stretch goal for \sys to create or change these presentations on the fly as needed by the audience.
+The specific use case would be when Annie asks her teacher about right angles.
+The teacher would then just have to click on right angles and \sys would create a short guided tour through the topic of right angles before returning to the subject of the Pythagorean theorem.\\
+
 \subsection{WP5: Qualitative Analysis and Evaluation of Findings}
@@
 A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
+Another stretch goal is for \sys to create or change presentations on the fly as outlined in \ref{sec:wp4}.
 It is not the goal of this research that users should be able to reconstruct the original graph from the presentation.\\
@@
 
-\textbf{Milestones}
-\begin{itemize}
-\item \textbf{Until February 1st}: \nameref{sec:wp1}
-\item \textbf{Until March 1st}: \nameref{sec:wp2}
-\item \textbf{Until March 15th}: \nameref{sec:wp3}
-\item \textbf{Until April 15th}:\nameref{sec:wp4}
-\item \textbf{Until May 10th}: \nameref{sec:wp5}
-\end{itemize}
 \begin{figure}[h]
@@
 
-  \section{Conclusions}
+\textbf{Milestones}
+\begin{itemize}
+\item \textbf{Until February 1st}: \nameref{sec:wp1}
+\item \textbf{Until March 1st}: \nameref{sec:wp2}
+\item \textbf{Until March 15th}: \nameref{sec:wp3}
+\item \textbf{Until April 15th}:\nameref{sec:wp4}
+\item \textbf{Until May 10th}: \nameref{sec:wp5}
+\end{itemize}
 
-  Summarize the main aspects of the proposal.
+  \section{Conclusion}
+  \label{sec:conclusion}
 
-  (target size: 1/2 page)
+The proposed research will evaluate if and how spatial narrative can be combined with semantic closeness to form visual presentations that will facilitate knowledge transfer.
+The knowledge presentation systen \sys that we will implement will allow us to automatically create these visual presentations from the OMDoc format.
+Through using semantic closeness the presentations can be created with meaningful visual connections between information.
+Similarly to how the Semantic Web tries to add relations between different resources for machines, \sys will add meaningful relations between course content.\\
+
+Going back to our contrived example, \sys will provide Annie's teacher with a tool that allows her to use her normal lecture material in a more interactive way.
+Thus when the teacher realizes that Annie needs to revise previous material, the teacher can easily go to that material and provide Annie with a good learning experience.
+This facilitates knowledge transfer and allows for a more engaging and interactive education.\\
+
+But not only will \sys make courses more engaging, interactive, and easier to follow.
+It will also lead to better knowledge absorption because students learn the concepts and in addition how they relate to one another.
+This allows for revision of material that is fast and will allow students to learn better on their own.
+\\
+
+In essence, this proposed research will be beneficial for education and knowledge transfer.
+It aims to make the creation of engaging and interactive presentations simple and fast for current users of OMDoc.
+Should this research prove successful it could be adapted for other areas.
+In the future creating a meaningful, interactive presentation might be just a matter of uploading a document.
 

### 2014-11-30 Proposal.tex
Final Draft 1

@@
         \centering
-                \fbox{\includegraphics[width=0.8\textwidth]{assets/model}}
+                \fbox{\includegraphics[width=0.8\textwidth]{assets/model2}}
                 \caption{From Data to Knowledge}
@@
 \textit{discourse-new}.
-In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.\\
+In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
+These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}.
+The accessibility depends on the relative \textit{newness}, i.e.
+recency of mention, of this information.\\
 

### 2014-12-04 Proposal.tex
Meike's comments and comments from meeting on Monday

@@
 \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.5} % Line spacing - Palatino needs more space between lines
+\linespread{1.3} % Line spacing - Palatino needs more space between lines
 \usepackage{microtype} % Slightly tweak font spacing for aesthetics
 \usepackage{minted}
+\usepackage[section]{placeins}
 \usepackage{nameref}
@@
     colorlinks=false,
-    linkcolor=red,
-    citecolor=green,
-    filecolor=magenta,
-    urlcolor=cyan
+    %linkcolor=red,
+    %citecolor=green,
+    %filecolor=magenta,
+    %urlcolor=cyan
+    pdfborder={0 0 0},
 }
@@
   With my signature, I certify that this thesis has been written by me
-  using only the indicates resources and materials. Where I have
+  using only the indicated resources and materials. Where I have
   presented data and results, the data and results are complete,
@@
 The proposed research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics.
-This form of presenting knowledge should enable users to examine materials they may have forgotten which form the basis for the understanding of the topics the audience is interested in.\\
+This form of presenting knowledge should enable users to examine materials which they may have forgotten which form the basis for the understanding of the topics the audience is interested in.\\
 
-Consider the typical lecture one attends as a student.
-Towards the end of the lecture students might have difficulties remembering earlier topics.
-When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with a simple way to catch up.\\
+Taking the typical lectures as an example, it is often the case that especially towards the end of the lecture students might have difficulties remembering earlier topics.
+When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with an easy way to catch up.\\
 
 The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, this research aims to visualize the connections of Mathematical knowledge in a way that allows students to learn the concepts the current topic depends on should they need to refresh their memories.
+Using OMDoc, this research aims at visualizing the connections of different pieces of Mathematical concepts in a way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
 It will examine if and how spatial narrative and semantic closeness can be combined to foster learning.
-Thus it could transform how we interact with course material and learning as a whole.
-This research has many other real world applications, namely, anywhere where knowledge is supposed to be transferred.\\
+If this approach proves successful it will transform how we interact with course material and learning processes in general.
+Ultimately, this research may be applicable to almost all areas in which knowledge is supposed to be transferred.\\
 
@@
 The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
-There are an interesting similar developments in other fields such as that of new presentation tools.
+There are interesting similar developments in other fields such as that of new presentation tools.
 These aim to enable the presentation of information in a more interconnected way that provides context.
-Both developments strive to connect pieces of information and through providing context to elevate pure information to knowledge.\\
+Both developments strive to connect pieces of information through providing context to not just provide information but rather knowledge.\\
 
@@
 Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content.
-Whereas this lead to a lot of information on the web, it provided comparatively little knowledge.
+While this led to a lot of information on the web, it provided comparatively little knowledge.
 Here the processing of information to provide knowledge is lacking.
-Similarly the existence of tools like Powerpoint have lead to virtually everyone doing presentations in this format.
-As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but are often badly delivered and lack structure and context.
-\\
+Similarly the existence of tools like Powerpoint have lead to virtually everyone creating presentations in this format.
+As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but often lack structure and context.\\
 
@@
 
-"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
+One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
 Figure \ref{fig:dataknow} is based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}.
-It shows the path from mere data to knowledge through adding context such that we gain information and then through adding networking to get knowledge.\\
+It shows the path from mere data to knowledge, through adding context, such that we gain information.
+From information, we can obtain knowledge through adding networking.\\
 
-We want to go from merely displaying information to visualizing information by displaying the network/context a piece of information is in.
-In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e.
-the context the information is in.
+We want to go from merely displaying information to visualizing information by displaying the network/context a piece of information is part of.
+In this we will not try to semantically represent the meaning of the information that is shown but rather to show the network, i.e.
+the context the information is a part of.
 Specifically we want to examine whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\
@@
 This will give us information about the semantic closeness of different pieces of information.
-From there on we will visualize the dependencies of the information contained in these documents.
-Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative in the form of an API such as Impress.js to allow for us to show the current piece of information of interest within the network of dependent information.\\
+Taking this as a starting point, we will visualize the dependencies of the information contained in these documents.
+Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative in the form of an API such as Impress.js in order to show the current piece of information of interest within the network of dependent information.\\
 
@@
 
-After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
-Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
+After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
+There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
 \\
@@
 
-To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
+To understand the problem of information that lacks context, this part of the proposal will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
 While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
@@
 
-Before we delve into the actual subject matter, we need to ensure that the terminology used is understood as intended. In the following we will use the terms information, knowledge, and context.\\
+Before we delve into the actual subject, we need to ensure that the terminology used is understood as intended. In the following we will use the terms information, knowledge, and context.\\
 
@@
 
-\subsection{Primitives}
-\label{sec:primitives}
-
-Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
-Primitives are the different elements of representation.
-In terms of evaluation it is important to have intuitive primitive elements.
-\\
-
-For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
-The exact layout of the frames and the best visualization of the relation between the frames is to be determined.
-Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
-\ednote {not sure whether I understand this correctly - does this need more explanation?}
-
 \subsection{Different Representations of Information}
@@
 Figure \ref{fig:imp_objects} shows how size conveys importance.
-When asked, people generally say that the circle on the left is most important, the ones on the right are less important.
+When asked, people generally say that the circle on the right is most important, the ones on the left are less important.
 Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different.
@@
 Do I need to cite my teaching material?
-Not sure...}
+Not sure...
+-> it is well known that.}
+
+\subsection{Primitives}
+\label{sec:primitives}
+
+Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
+Primitives are the different elements of representation.
+In terms of evaluation it is important to have intuitive primitive elements.
+\\
+
+For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
+The exact layout of the frames and the best visualization of the relation between the frames is to be determined.
+Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+\ednote {not sure whether I understand this correctly - does this need more explanation?}
+\ednote {visual and graph language have different primitives and it's interesting how it is mapped to one another}
 
@@
 
+\subsection{Related Works}
+\label{sec:relatedworks}
+
+When searching for related works there is little to be found.
+There has been work done to make teaching more effective by providing students with materials from the lecture after the lectures.
+To make this more effective systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
+It has been found that allowing students to review all class material has a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}, hence these systems are a good approach.
+However, while this approach also aims at improving the learning experience, it does not in any way link content or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\
+
+In
+
 \section{Work Plan}
@@
 \ednote {should Impress.js go into the introduction/preliminaries? - I decided against this as I haven't examined Impress.js enough yet and this will take several days to do.}
-The first step to implementing \sys \ednote{Is the font format ok?} is to understand the tool we want to represent the knowledge in later.
+The first step to implementing \sys is to understand the tool we want to represent the knowledge in later.
 Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without using the editor, this research will employ another tool that is inspired by the idea behind Prezi.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \begin{center}
@@
 It will also lead to better knowledge absorption because students learn the concepts and in addition how they relate to one another.
-This allows for revision of material that is fast and will allow students to learn better on their own.
+This allows faster revision of material and facilitates studying without a teacher present.
 \\

### 2014-12-04 Proposal.tex
All comments from Meike done

@@
 One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
-Figure \ref{fig:dataknow} is based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}.
-It shows the path from mere data to knowledge, through adding context, such that we gain information.
+Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information.
 From information, we can obtain knowledge through adding networking.\\
@@
 Taking this as a starting point, we will visualize the dependencies of the information contained in these documents.
-Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative in the form of an API such as Impress.js in order to show the current piece of information of interest within the network of dependent information.\\
+Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative with the help of a presentation framework such as Impress.js in order to show the current piece of information of interest within the network of dependent information.\\
 
@@
 
-Before we delve into the actual subject, we need to ensure that the terminology used is understood as intended. In the following we will use the terms information, knowledge, and context.\\
+In this section we will introduce some basic terminology which will be needed to discuss the actual subject matter in the following part.
+We will define the terms information, knowledge, and context.\\
 
 The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
-Looking back at the figure from section 1, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
+Recalling figure \ref{fig:dataknow} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
 For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
-Of special importance for us is the association.
-We will take this as meaning that the knowledge is made up out of several pieces of information that are connected.
+\textbf{Association} is of special importance for the current project.
+We will define this as knowledge that is made up out of several pieces of information that are connected.
 In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used.\\
 
-Merriam-Webster \cite{Webster:npentrel14} defines \textbf{context} as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
+According to the Merriam-Webster dictionary \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
 A Context can be easily explained with the example of Annie learning the Pythagorean theorem.
@@
 
-In \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers".
-Here, the content layers are the mathematical objects, i.e.
+In \textit{A mathematical approach to ontology authoring and
+documentation} \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers".
+In our case, the content layers are the mathematical objects, i.e.
 the statements or theories.
@@
 
-In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is known.
-Within this, one discriminates between \textit{familiar} and \textit{old} information.
-\textit{Familiar} information is shared by speaker and addressee, ie.
+In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
+Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information.
+\textit{Familiar/ old} information is shared by speaker and addressee, i.e.
 it is in the intersection of knowledge of student and teacher.
-New information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
+\textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
 In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
@@
 A sign of a women on a door conveys to most of us that this is a bathroom for women.
-The information graphs that OMDoc provides us with could also be simply visualized as that - a tree of information.
+The information graphs that OMDoc provides us with could also be simply visualized as a tree of information.
 But this would not be very engaging and it would be hard for a human to process.
@@
 
-In the proposed research we will focus less on text, tree-like structures, or metaphors like the sign of a woman on a door.
+In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics like the sign of a woman on a door.
 We will rather focus on the spatial narrative and placing content that inherently belongs together visually close together since this can convey the meaning that these objects belong together.\\
@@
 
-The figures above clarify what we mean by 'meaningful representations'.
+The figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'.
 Figure \ref{fig:imp_objects} shows how size conveys importance.
-When asked, people generally say that the circle on the right is most important, the ones on the left are less important.
+It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size.
 Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different.
@@
 In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\
-
-\ednote{ These are things I derive from what I have been in teaching my APS seminars and have probably been told by multile people during my training as a prezi ambassador.
-Do I need to cite my teaching material?
-Not sure...
--> it is well known that.}
 
@@
 
-In
+In \ednote{continue}
 
@@
 
-\subsection{WP1: Understanding API of Impress.js}
+\subsection{WP1: Understanding the API of Impress.js}
 \label{sec:wp1}
 
-\ednote {should Impress.js go into the introduction/preliminaries? - I decided against this as I haven't examined Impress.js enough yet and this will take several days to do.}
 The first step to implementing \sys is to understand the tool we want to represent the knowledge in later.
-Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without using the editor, this research will employ another tool that is inspired by the idea behind Prezi.
+Since Prezi at the current time does not have an Application Programming Interface (API) that would allow for the generation of a whole presentation without using the editor, this research will employ another tool that is inspired by the idea behind Prezi.
 Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions.\\
@@
 
-After finishing this part we should have several different presentation styles and one should be chosen with which we will continue our work.\\
+After finishing this part we should have several different presentation styles from which one can be chosen to continue the main research question.\\
 
@@
 
-Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improfe knowledge transfer.
+Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.
 
 If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
-If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers what is impossible.\\
+If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers which other parameters need to be kept in mind in order to succeed in future.
 

### 2014-12-04 Proposal.tex
layout changes according to meeting notes

@@
-\documentclass[twoside]{article}
+\documentclass[twoside, 12pt]{article}
 \usepackage{amsmath}
@@
 \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.3} % Line spacing - Palatino needs more space between lines
+\linespread{1.2} % Line spacing - Palatino needs more space between lines
 \usepackage{microtype} % Slightly tweak font spacing for aesthetics
@@
 %\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
-\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
-\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles
+\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
+\titleformat{\subsection}[block]{\large\scshape}{\thesubsection.}{1em}{} % Change the look of the section titles
 \usepackage{cite}
@@
 
-\newpage
 \section{Preliminaries}

### 2014-12-04 Proposal.tex
related work and starting with the example

@@
 
-To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem.
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \vspace{-20pt}
+  \begin{center}
+                \fbox{\includegraphics[width=0.4\textwidth]{assets/Annie1}}
+\end{center}
+  \vspace{-20pt}
+  \caption{Slide about the Pythagorean Theorem}
+                \label{fig:Annie-presentation-teacher}
+  \vspace{-10pt}
+\end{wrapfigure}
+
+To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
 She is given a triangle with sides a = 3 cm and b = 4 cm.
@@
 In this section we will introduce some basic terminology which will be needed to discuss the actual subject matter in the following part.
-We will define the terms information, knowledge, and context.\\
+We will conceptualize what we mean by the terms information, knowledge, and context.\\
 
@@
 In \textit{A mathematical approach to ontology authoring and
-documentation} \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers".
+documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers".
 In our case, the content layers are the mathematical objects, i.e.
@@
 When searching for related works there is little to be found.
-There has been work done to make teaching more effective by providing students with materials from the lecture after the lectures.
-To make this more effective systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
-It has been found that allowing students to review all class material has a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}, hence these systems are a good approach.
-However, while this approach also aims at improving the learning experience, it does not in any way link content or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\
+Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}.
+For this systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
+Some of these systems use temporal information \cite{DBLP:dblp_journals/isci/ChungS97} to show multiple resources in sync as they appeared in the lecture.
+However, while this approach also aims at improving the learning experience, it does not in any way link content semantically based on dependencies or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\
 
-In \ednote{continue}
+Another piece of research has focused on the automatic generation of mind maps from text {Direct automatic generation of mind maps from text with M 2 Gen}.
+The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects.
+While this is close to what the proposed research intends in showing the relation between pieces of information, it does it on a word level.
+For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map.
+We, on the other hand, will focus on exactly that, i.e.
+dependencies and the creation of interactive presentations.\\
 

### 2014-12-05 Proposal.tex
many changes regarding example

@@
 \noindent
-  With my signature, I certify that this thesis has been written by me
+  With my signature, I certify that this thesis proposal has been written by me
   using only the indicated resources and materials. Where I have
@@
 To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context.
-The proposed research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics.
-This form of presenting knowledge should enable users to examine materials which they may have forgotten which form the basis for the understanding of the topics the audience is interested in.\\
+The proposed research aims at taking an existing annotated corpus and presenting its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
+This form of presenting knowledge should enable users to interactively examine materials that are related to the topics the audience is interested in.\\
 
-Taking the typical lectures as an example, it is often the case that especially towards the end of the lecture students might have difficulties remembering earlier topics.
+Taking the typical lectures as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics.
 When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with an easy way to catch up.\\
@@
 The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, this research aims at visualizing the connections of different pieces of Mathematical concepts in a way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
+Using OMDoc, this research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
 It will examine if and how spatial narrative and semantic closeness can be combined to foster learning.
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-  \vspace{-20pt}
-  \begin{center}
-                \fbox{\includegraphics[width=0.4\textwidth]{assets/Annie1}}
-\end{center}
-  \vspace{-20pt}
-  \caption{Slide about the Pythagorean Theorem}
-                \label{fig:Annie-presentation-teacher}
-  \vspace{-10pt}
-\end{wrapfigure}
-
 To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
@@
 Now Annie has to try to find out what a right triangle is.
-This shows the dependencies of different pieces of information, i.e.
-the Pythagorean theorem depends on knowledge of squares, lengths, area calculation, angles, and right angles.
+This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e.
+the Pythagorean theorem depends on knowledge of squares,triangles, lengths, area calculation, and right angles.
 In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\
+
+\begin{figure}[H]
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
+			   \caption{Simple, explanatory slide}
+                \label{fig:Annie-presentation-teacher}
+        \end{subfigure}%
+        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.45\textwidth}
+                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
+		  \caption{Information dependencies}
+                \label{fig:Annie-presentation-information}
+        \end{subfigure}
+        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
+\end{figure}
 
@@
 The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
-Recalling figure \ref{fig:dataknow} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
+Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$} (see \ref{fig:Annie-presentation-teacher}).
 For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
@@
 We will define this as knowledge that is made up out of several pieces of information that are connected.
-In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used.\\
+In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \ref{fig:Annie-presentation-information}).\\
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.45\textwidth]{assets/Annie3}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Information in context}
+  \label{fig:Annie-context}
+\vspace{-10pt}
+\end{wrapfigure}
 
 According to the Merriam-Webster dictionary \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
-A Context can be easily explained with the example of Annie learning the Pythagorean theorem.
+Context can be easily explained with the example of Annie learning the Pythagorean theorem.
 The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e.
-calculating squares, lengths, area calculation, angles, and right angles.
+calculating squares, area calculation, triangles, and right angles.
 This is the context that the Pythagorean theorem needs.
@@
 
+\begin{wrapfigure}{l}{0.5\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.45\textwidth]{assets/Annie4xml}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Information in context}
+  \label{fig:Annie-context}
+\vspace{-10pt}
+\end{wrapfigure}
+
 In \textit{A mathematical approach to ontology authoring and
@@
 Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
+
+\ednote{on top of the info about when it appears within the course.}
 
@@
 \textit{course-ancient}.\\
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.45\textwidth]{assets/Annie4ancient2}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Course-ancient information}
+  \label{fig:Annie-context}
+\vspace{-10pt}
+\end{wrapfigure}
 
@@
 
-\subsection{Related Works}
+\subsection{Related Work}
 \label{sec:relatedworks}
@@
 
-Another piece of research has focused on the automatic generation of mind maps from text {Direct automatic generation of mind maps from text with M 2 Gen}.
+Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}.
 The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects.
-While this is close to what the proposed research intends in showing the relation between pieces of information, it does it on a word level.
+While the proposed research also intends to show the relation between pieces of information, it does it on a different level.
 For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map.

### 2014-12-05 Proposal.tex
happy with abstract and intro

@@
 Taking the typical lectures as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics.
-When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with an easy way to catch up.\\
+When a new topic is introduced it would be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\
 
 The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, this research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
+Using OMDoc, the proposed research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
 It will examine if and how spatial narrative and semantic closeness can be combined to foster learning.
 If this approach proves successful it will transform how we interact with course material and learning processes in general.
-Ultimately, this research may be applicable to almost all areas in which knowledge is supposed to be transferred.\\
+Ultimately, this research may be applicable to almost all areas in which knowledge needs to be transferred.\\
 
@@
 These aim to enable the presentation of information in a more interconnected way that provides context.
-Both developments strive to connect pieces of information through providing context to not just provide information but rather knowledge.\\
+Both developments strive to connect pieces of information through providing context, to not just provide information, but rather knowledge.\\
 
@@
 This makes the information hard to process by humans and/or machines.
-The Semantic Web hopes to change the former, whereas new, more visual presentation tools using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.
+The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.
 The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information.
@@
 
-To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
+\begin{figure}[H]
+        \centering
+        \begin{subfigure}[b]{0.47\textwidth}
+                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
+			   \caption{Simple, explanatory slide}
+                \label{fig:Annie-presentation-teacher}
+        \end{subfigure}%
+        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.47\textwidth}
+                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
+		  \caption{Information dependencies}
+                \label{fig:Annie-presentation-information}
+        \end{subfigure}
+        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
+\end{figure}
+
+To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
 She is given a triangle with sides a = 3 cm and b = 4 cm.
@@
 In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\
-
-\begin{figure}[H]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
-			   \caption{Simple, explanatory slide}
-                \label{fig:Annie-presentation-teacher}
-        \end{subfigure}%
-        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.45\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
-		  \caption{Information dependencies}
-                \label{fig:Annie-presentation-information}
-        \end{subfigure}
-        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
-\end{figure}
 

### 2014-12-05 Proposal.tex
happy with 2.1

@@
 The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
-Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$} (see \ref{fig:Annie-presentation-teacher}).
-For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
-\textbf{Association} is of special importance for the current project.
-We will define this as knowledge that is made up out of several pieces of information that are connected.
-In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \ref{fig:Annie-presentation-information}).\\
+Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
+For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
+This \textbf{association} is of special importance for the current project.
+We will define it as knowledge that is made up out of several pieces of information that are connected.
+In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see figure \ref{fig:Annie-presentation-information}).\\
 
@@
 
-According to the Merriam-Webster dictionary \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
+According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
 Context can be easily explained with the example of Annie learning the Pythagorean theorem.
-The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e.
+The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on.
+Without this context, Annie cannot understand the theorem.
+Figure \ref{fig:Annie-context} shows the context by showing the dependencies of the theorem, i.e.
 calculating squares, area calculation, triangles, and right angles.
-This is the context that the Pythagorean theorem needs.
+It semiotically represents relatedness of concepts by linking the different concepts with lines, thus creating associations between the different pieces of information.
 We will be using the terms context and network almost interchangeably and depend on the reader to have the right intuition about these terms.\\
@@
 \vspace{-20pt}
-  \caption{Information in context}
-  \label{fig:Annie-context}
+  \caption{Information in ???}
+  \label{fig:Annie-Omdoc}
 \vspace{-10pt}
@@
   \caption{Course-ancient information}
-  \label{fig:Annie-context}
+  \label{fig:Annie-ancient}
 \vspace{-10pt}

### 2014-12-05 Proposal.tex
happy with 2.2

@@
 
-\begin{wrapfigure}{l}{0.5\textwidth}
+\begin{wrapfigure}{l}{0.6\textwidth}
 \vspace{-26pt}
@@
   \fbox{
-    \includegraphics[width=0.45\textwidth]{assets/Annie4xml}
+    \includegraphics[width=0.55\textwidth]{assets/Annie4xml3}
     }
@@
 \vspace{-20pt}
-  \caption{Information in ???}
-  \label{fig:Annie-Omdoc}
+  \caption{Narrative Layers and semantic closeness}
+  \label{fig:Annie-semantic-closeness}
 \vspace{-10pt}
@@
 Narrative layers refer to the order the mathematical objects from content layers are presented.
+In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them.
 Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects.
+These levels of semantic closeness are represented through the different sizes of the frames of the related information.
 In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness.
 Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
-
-\ednote{on top of the info about when it appears within the course.}
 
@@
   \fbox{
-    \includegraphics[width=0.45\textwidth]{assets/Annie4ancient2}
+    \includegraphics[width=0.45\textwidth]{assets/Annie4xml3ancient}
     }

### 2014-12-05 Proposal.tex
happy with 2.3

@@
 
-In this example in the first part of the sentence, information pertaining to my sister and to a circus are introduced, i.e.
-\textit{discourse-new}.
+In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced.
 In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
@@
 
-These concepts can be adapted to the situation of teaching Mathematics or Computer Science to students in a class.
+These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
 In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}.
@@
 The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
+This is marked orange in \ref{fig:Annie-ancient}.
 The information about squares which Annie still remembers is \textit{course-old}.

### 2014-12-05 Proposal.tex
happy up to 4.4

@@
 The information graphs that OMDoc provides us with could also be simply visualized as a tree of information.
-But this would not be very engaging and it would be hard for a human to process.
-Similarly traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
+But this would not be very engaging and it would be hard for a person to process.
+Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
 \\
 
-In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics like the sign of a woman on a door.
+In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door.
 We will rather focus on the spatial narrative and placing content that inherently belongs together visually close together since this can convey the meaning that these objects belong together.\\
@@
 When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
+\newpage
+\begin{wrapfigure}{l}{0.5\textwidth}
+\vspace{-10pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.45\textwidth]{assets/Annie4size}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Relative size and relations}
+  \label{fig:Annie-relsize}
+\vspace{-10pt}
+\end{wrapfigure}
 
@@
 For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information.
-From there on it depends how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics.
-Similarly we will employ visual relations as in \ref{fig:rel_objects} to show related content.
+Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics.
+Similarly we will employ visual relations as in figure \ref{fig:rel_objects} to show related content.
+Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts.
+Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger.
 Thus we will provide Annie with a meaningful representation of the information taken from the information graph.

### 2014-12-05 Proposal.tex
more comments from meike

@@
 
-Taking the typical lectures as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics.
+Taking the typical lecture as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics.
 When a new topic is introduced it would be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\
@@
 Here the processing of information to provide knowledge is lacking.
-Similarly the existence of tools like Powerpoint have lead to virtually everyone creating presentations in this format.
+Similarly, the existence of tools like Powerpoint have lead to virtually everyone creating presentations in this format.
 As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but often lack structure and context.\\
@@
 
-We want to go from merely displaying information to visualizing information by displaying the network/context a piece of information is part of.
+We want to go from merely displaying information to visualizing information by displaying the network/context of which a piece of information is part of.
 In this we will not try to semantically represent the meaning of the information that is shown but rather to show the network, i.e.
@@
 
-To understand the problem of information that lacks context, this part of the proposal will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
+To understand the problem of information that lacks context, this part of the proposal will provide the necessary background information.
+It will allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
 While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
@@
 In this section we will introduce some basic terminology which will be needed to discuss the actual subject matter in the following part.
-We will conceptualize what we mean by the terms information, knowledge, and context.\\
+We will conceptualize what we mean by the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\
 
-The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
+The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
 Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
-For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
-This \textbf{association} is of special importance for the current project.
+For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
+This \textit{association} is of special importance for the current project.
 We will define it as knowledge that is made up out of several pieces of information that are connected.
@@
 
-According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
+According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
 Context can be easily explained with the example of Annie learning the Pythagorean theorem.
-The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on.
-Without this context, Annie cannot understand the theorem.
-Figure \ref{fig:Annie-context} shows the context by showing the dependencies of the theorem, i.e.
+The \textit{information} about the calculation of the length of the third side of the triangle is only helpful for Annie within the \textit{context} of the pieces of \textit{information} this depends on.
+Without this \textit{context}, Annie cannot understand the theorem.
+Figure \ref{fig:Annie-context} illustrates the context by showing the dependencies of the theorem, i.e.
 calculating squares, area calculation, triangles, and right angles.
-It semiotically represents relatedness of concepts by linking the different concepts with lines, thus creating associations between the different pieces of information.
-We will be using the terms context and network almost interchangeably and depend on the reader to have the right intuition about these terms.\\
+It semiotically represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}.
+We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\
 
@@
 The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
-This is marked orange in \ref{fig:Annie-ancient}.
+This is marked orange in figure \ref{fig:Annie-ancient}.
 The information about squares which Annie still remembers is \textit{course-old}.
@@
 In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door.
-We will rather focus on the spatial narrative and placing content that inherently belongs together visually close together since this can convey the meaning that these objects belong together.\\
+We will rather focus on the spatial narrative and placing content that is inherently related visually close together since this can convey the meaning that these objects belong together.\\
 
@@
 
-The figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'.
+Figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'.
 Figure \ref{fig:imp_objects} shows how size conveys importance.
@@
 
+The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
 Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}.
-When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.
-The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.\\
+When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.\\
 

### 2014-12-05 Proposal.tex
more work

@@
 These aim to enable the presentation of information in a more interconnected way that provides context.
-Both developments strive to connect pieces of information through providing context, to not just provide information, but rather knowledge.\\
+Both developments strive to connect pieces of information through adding context, to not just provide information, but rather knowledge.\\
 
@@
 Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information.
-From information, we can obtain knowledge through adding networking.\\
+From information, we can then obtain knowledge through adding networking.\\
 
@@
 This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e.
-the Pythagorean theorem depends on knowledge of squares,triangles, lengths, area calculation, and right angles.
+the Pythagorean theorem depends on knowledge of squares, triangles, lengths, area calculation, and right angles.
 In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\
@@
   \fbox{
-    \includegraphics[width=0.55\textwidth]{assets/Annie4xml3}
+    \includegraphics[width=0.58\textwidth]{assets/Annie4xml3}
     }
@@
 These levels of semantic closeness are represented through the different sizes of the frames of the related information.
-In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness.
+In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness of content.
 Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
@@
 The information about squares which Annie still remembers is \textit{course-old}.
-Through the semantic closeness that OMDoc provides us we will be able to determine the status of information within the (dis)course.
+Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
 \\
@@
 In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door.
-We will rather focus on the spatial narrative and placing content that is inherently related visually close together since this can convey the meaning that these objects belong together.\\
+We will rather focus on spatial narrative and placing content, that is inherently related, visually close together since this conveys the meaning that these objects belong together.\\
 
@@
 
-Figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'.
+Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations.
 Figure \ref{fig:imp_objects} shows how size conveys importance.
@@
 Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics.
-Similarly we will employ visual relations as in figure \ref{fig:rel_objects} to show related content.
+Similarly, we will employ visual relations as in figure \ref{fig:rel_objects} to show related content.
 Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts.
@@
 Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
-\ednote {not sure whether I understand this correctly - does this need more explanation?}
-\ednote {visual and graph language have different primitives and it's interesting how it is mapped to one another}
+\\
+
+Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another.
+When we consider tree-like graphs, there are two structural primitives, namely the nodes/ concepts and the relations between nodes.
+Additionally we can add semantic primitives like attributes to the concepts and to the relations.
+These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
 

### 2014-12-05 Proposal.tex
almost done :D

@@
 When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
-\newpage
-\begin{wrapfigure}{l}{0.5\textwidth}
-\vspace{-10pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.45\textwidth]{assets/Annie4size}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Relative size and relations} 
-  \label{fig:Annie-relsize}
-\vspace{-10pt}
-\end{wrapfigure}
 
@@
 
+\begin{figure}[H]
+        \centering
+		    \fbox{\includegraphics[width=0.65\textwidth]{assets/Annie4size}}
+  \caption{Relative size and relations} 
+  \label{fig:Annie-relsize}
+\end{figure}
+
 \subsection{Primitives}
@@
 
+Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another.
+When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes.
+Additionally we can add semantic primitives like attributes to the concepts and to the relations.
+In normal graphs a relation between two nodes is often quite simple there is one node that is the subject, one node that acts as an object, and the relation that acts like a predicate.
+Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles.
+These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
+
 For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
+The frames can be mapped directly to the nodes/concepts that graphs use.
+Text and images are taken for granted within the frames.
+Similarly, the visual relation between different frames is very much like the relations between nodes.
+However, the relations can be much more expressive within Impress.js.\\
+
+Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information.
+Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
+As such the temporal associations show the path that a normal lecture would take.
+The dependencies that are visualized around each frame allow for the interactiveness.\\
+
 The exact layout of the frames and the best visualization of the relation between the frames is to be determined.
-Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+Ideally the added expressiveness should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
 \\
-
-Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another.
-When we consider tree-like graphs, there are two structural primitives, namely the nodes/ concepts and the relations between nodes.
-Additionally we can add semantic primitives like attributes to the concepts and to the relations.
-These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
 
@@
 Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}).
-Last but not least we need to create several models of how the relations between the different frames can be portrayed within Impress.js.\\
+Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within Impress.js.\\
 
 After finishing this part we should have several different presentation styles from which one can be chosen to continue the main research question.\\
-
-\ednote{look at Impressionist and jimpress when writing actual thesis}\\
 
@@
 
-The information graph we receive from OMDoc should be topologically sorted based on dependencies of knowledge.
-This will allow us to assign values representing the status of information within the course as as in section \ref{sec:infostatus}.
+The information graph OMDoc provides us with should be topologically sorted based on dependencies of knowledge.
+This will allow us to assign values representing the status of information within the course as outlined in section \ref{sec:infostatus}.
 It will also allow us to create values for the relative semantic closeness of information which will be needed for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
@@
 
-Each piece of information needs to also have an importance level assigned to it as well (see section \ref{sec:inforep}).
-This ought to be determined by knowing how often the concept is used and how important it is for the student to grasp it.\\
+Each piece of information needs to also have an importance level assigned to it (see section \ref{sec:inforep}).
+This ought to be determined by counting how often the concept is used and how important it is for the student to grasp it.\\
 
-\subsection{WP3: Combination OMDoc and Spatial Narration}
+\subsection{WP3: Combination of OMDoc and Spatial Narration}
 \label{sec:wp3}
@@
 Once we have an ordered information graph with all the additional attribute values mentioned in section \ref{sec:wp2}, we will create the knowledge presentation system \sys.
-\sys will visualize the information from the graph.
+\sys will visualize the information from the graph including all the attributes we added.
 The outcome of this part should be a general \sys presentation model, that implements the models according to the models chosen in section \ref{sec:wp1}.
-We will then use \sys to visualize the information in WP4.\\
+We will then use \sys to visualize information in WP4.\\
 
@@
 \sys will take the ordered information graph of the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} with all the additional attributes we generated in \ref{sec:wp2} and transform it into a spatial presentation using Impress.js.
-This will be done by parsing the created XML and creating the markup that Impress.js is using to create the chosen presentation models from section \ref{sec:wp1}.
+This will be done by parsing the generated XML and creating the markup that Impress.js is using to create the chosen presentation models from section \ref{sec:wp1}.
 After this work package, we should have one (or more) presentations of the topics covered in the General Computer Science Lecture notes.\\
@@
 
-The evaluation criteria for the research at hand are on the one hand systematic and on the other hand cognitive.
+The evaluation criteria for the research at hand are, on the one hand, systematic and, on the other hand, cognitive.
 Systematically, we will be evaluating two main challenges: First we will evaluate whether the knowledge presentation system \sys that was developed allows for the creation of a full presentation from a given annotated document.
@@
 
-Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.
+Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.\\
 
 If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
-If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers which other parameters need to be kept in mind in order to succeed in future.
+If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers which other parameters need to be kept in mind in order to succeed in future.\\
 
@@
 Another stretch goal is for \sys to create or change presentations on the fly as outlined in \ref{sec:wp4}.
-It is not the goal of this research that users should be able to reconstruct the original graph from the presentation.\\
+It is not the goal of this research that users should be able to reconstruct the original information graph from the presentation.\\
 
@@
 
-But not only will \sys make courses more engaging, interactive, and easier to follow.
-It will also lead to better knowledge absorption because students learn the concepts and in addition how they relate to one another.
-This allows faster revision of material and facilitates studying without a teacher present.
-\\
+But not only will \sys make courses more engaging, interactive, and easier to follow, it will also lead to better knowledge absorption because students learn the concepts and in addition intuitively understand how they relate to one another.
+This allows faster revision of material and facilitates studying without a teacher present.\\
 
@@
 Should this research prove successful it could be adapted for other areas.
-In the future creating a meaningful, interactive presentation might be just a matter of uploading a document.
+In the future creating a meaningful, interactive presentation might be just a matter of uploading an annotated document.
 

### 2014-12-05 Proposal.tex
somewhat final version?

@@
 \usepackage{pgfgantt}
-\usepackage[show]{ed}
+%\usepackage[show]{ed}
 \setlength{\parindent}{0pt}
@@
 
-\begin{wrapfigure}{l}{0.6\textwidth}
+\begin{wrapfigure}{l}{0.5\textwidth}
 \vspace{-26pt}
@@
   \fbox{
-    \includegraphics[width=0.58\textwidth]{assets/Annie4xml3}
+    \includegraphics[width=0.48\textwidth]{assets/Annie4xml3}
     }
@@
         \centering
-		    \fbox{\includegraphics[width=0.65\textwidth]{assets/Annie4size}}
+		    \fbox{\includegraphics[width=0.6\textwidth]{assets/Annie4size}}
   \caption{Relative size and relations} 
@@
 In terms of evaluation it is important to have intuitive primitive elements.
-\\
+The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}.
+The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\
 
-Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another.
+Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the other.
 When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes.
-Additionally we can add semantic primitives like attributes to the concepts and to the relations.
-In normal graphs a relation between two nodes is often quite simple there is one node that is the subject, one node that acts as an object, and the relation that acts like a predicate.
-Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles.
+Additionally we can add semantic primitives like attributes to the concepts and to the relations to show what kind of a relation it is.
+In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts like a predicate.
+Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}).
 These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
@@
 As such the temporal associations show the path that a normal lecture would take.
-The dependencies that are visualized around each frame allow for the interactiveness.\\
+The dependencies that are visualized around each frame allow for interactiveness.\\
 
-The exact layout of the frames and the best visualization of the relation between the frames is to be determined.
-Ideally the added expressiveness should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+The exact layout of the frames and the best visualization of the relation between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
+Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
 \\
@@
 
+\begin{wrapfigure}{l}{0.4\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.35\textwidth]{assets/Annie3spatial}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Guided spatial tour}
+  \label{fig:Annie-guided}
+\vspace{-10pt}
+\end{wrapfigure}
+
 In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
-For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected.
+For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:Annie-guided}).
 It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\
@@
 It is not the goal of this research that users should be able to reconstruct the original information graph from the presentation.\\
-
+\newpage
 \section{Timeline}

### 2014-12-06 Proposal.tex
submitted version

@@
 
-Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the other.
+Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter.
 When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes.
-Additionally we can add semantic primitives like attributes to the concepts and to the relations to show what kind of a relation it is.
-In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts like a predicate.
-Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}).
+Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is.
+In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate.
+Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}).
 These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
@@
 
-The exact layout of the frames and the best visualization of the relation between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
-Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
+Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
 \\

### 2015-04-30 Thesis.tex
adding thesiss

--- 2014-12-05 Proposal.tex
@@
     \huge
-    \textbf{The Combination of Spatial Narrative and Semantic Closeness to derive Visualizations of Theory Graphs}
+    \textbf{The Combination of Spatial Narrative and Semantic Closeness to Derive Visualizations of Theory Graphs}
   \end{center}
@@
     \large
-    Bachelor Thesis Proposal in Computer Science
+    Bachelor Thesis in Computer Science
   \end{center}
@@
 \noindent
-  With my signature, I certify that this thesis proposal has been written by me
+  With my signature, I certify that this thesis has been written by me
   using only the indicated resources and materials. Where I have
@@
 To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context.
-The proposed research aims at taking an existing annotated corpus and presenting its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
-This form of presenting knowledge should enable users to interactively examine materials that are related to the topics the audience is interested in.\\
+The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
+This form of presenting knowledge enable susers to interactively examine materials that are related to the topics the audience is interested in.\\
 
@@
 The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, the proposed research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
-It will examine if and how spatial narrative and semantic closeness can be combined to foster learning.
-If this approach proves successful it will transform how we interact with course material and learning processes in general.
-Ultimately, this research may be applicable to almost all areas in which knowledge needs to be transferred.\\
+Using OMDoc, this research presents different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
+Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning while discussing several different schema that are ditaktisch wertvoll\ednote{check translation}.This approach to presenting learning materials changes how we interact with course material which will allow students to learn better.
+Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.\\
 
@@
 
-The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
+%The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
 There are interesting similar developments in other fields such as that of new presentation tools.
@@
 
-The concept behind these two developments is quite similar.
+%The concept behind these two developments is quite similar.
 Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content.
@@
 
-In essence, both issues stem from information being generated without enough context or structure.
+%In essence, both issues stem from information being generated without enough context or structure.
 This makes the information hard to process by humans and/or machines.
@@
 
-One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
+%One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
 Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information.
@@
 
-We want to go from merely displaying information to visualizing information by displaying the network/context of which a piece of information is part of.
+%We want to go from merely displaying information to visualizing information by displaying the network/context of which a piece of information is part of.
 In this we will not try to semantically represent the meaning of the information that is shown but rather to show the network, i.e.
@@
 
-To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks).
+%To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks).
 For this we will be using the OMDoc (Open Mathematical Documents) format which will provide us with an annotated set of documents.
@@
 
-To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
+%To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
 She is given a triangle with sides a = 3 cm and b = 4 cm.
@@
 
-After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
+%After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
 There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
@@
 
-To understand the problem of information that lacks context, this part of the proposal will provide the necessary background information.
-It will allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution to allow Annie's teacher to transfer knowledge more effectively.
-While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\
+As we have pointed out in the \ref{sec:introduction}, presenting information in an efficient way is essential in order for any learning to occur.
+In the following we will examine some prerequisite knowledge.
+By engaging with our example presentation we will show how Annie's teacher can transfer knowledge more effectively.\\
 
@@
 
-In this section we will introduce some basic terminology which will be needed to discuss the actual subject matter in the following part.
-We will conceptualize what we mean by the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\
+Before discussing the buzzword knowledge transfer further, we will first engage in the conceptualization of the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\
 
-The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
+%The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
 Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.45\textwidth]{assets/Annie3}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Information in context}
-  \label{fig:Annie-context}
-\vspace{-10pt}
-\end{wrapfigure}
+\ednote{In current presentations there is only one context. By adding more levels of context we can allow viewers to understand the subject on a deeper level.}
 
-According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
+%According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
 Context can be easily explained with the example of Annie learning the Pythagorean theorem.
@@
 We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\
-
+\newpage
 \subsection{OMDoc}
@@
 
-OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
+%OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
 As such it is a semi-formal domain ontology.
@@
 
-If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways.
+%If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways.
 This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts.
@@
 
-\begin{wrapfigure}{l}{0.6\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.58\textwidth]{assets/Annie4xml3}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Narrative Layers and semantic closeness}
-  \label{fig:Annie-semantic-closeness}
-\vspace{-10pt}
-\end{wrapfigure}
-
-In \textit{A mathematical approach to ontology authoring and
-documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers".
+%In \textit{A mathematical approach to ontology authoring and documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers".
 In our case, the content layers are the mathematical objects, i.e.
@@
 Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
-
+\newpage
 \subsection{Status of Information within the (Dis)Course}
@@
 
-In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
+%In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
 Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information.
@@
 
-In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced.
+%In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced.
 In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
@@
 
-These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
+%These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
 In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}.
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.45\textwidth]{assets/Annie4xml3ancient}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Course-ancient information}
-  \label{fig:Annie-ancient}
-\vspace{-10pt}
-\end{wrapfigure}
-
-Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
+%Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
 The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
@@
 \\
-
+\newpage
 \subsection{Different Representations of Information}
@@
 
-Information can be (re)presented in different ways: text, visuals, images, etc.
+%Information can be (re)presented in different ways: text, visuals, images, etc.
 Actually everything that is in the world around us conveys information to us.
@@
 
-In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door.
+%In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door.
 We will rather focus on spatial narrative and placing content, that is inherently related, visually close together since this conveys the meaning that these objects belong together.\\
@@
 
-Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations.
+%Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations.
 Figure \ref{fig:imp_objects} shows how size conveys importance.
@@
 
-These perceptions can be used to convey meaning visually.
+%These perceptions can be used to convey meaning visually.
 For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information.
@@
 
-Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
+%Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
 Primitives are the different elements of representation.
 In terms of evaluation it is important to have intuitive primitive elements.
-\\
+The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}.
+The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\
 
-Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another.
+%Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter.
 When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes.
-Additionally we can add semantic primitives like attributes to the concepts and to the relations.
-In normal graphs a relation between two nodes is often quite simple there is one node that is the subject, one node that acts as an object, and the relation that acts like a predicate.
-Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles.
+Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is.
+In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate.
+Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}).
 These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
 
-For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
+%For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
 The frames can be mapped directly to the nodes/concepts that graphs use.
@@
 
-Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information.
+%Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information.
 Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
 As such the temporal associations show the path that a normal lecture would take.
-The dependencies that are visualized around each frame allow for the interactiveness.\\
+The dependencies that are visualized around each frame allow for interactiveness.\\
 
-The exact layout of the frames and the best visualization of the relation between the frames is to be determined.
-Ideally the added expressiveness should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
+Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
 \\
-
+\newpage
 \subsection{Spatial Narrative}
@@
 
-The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
+%The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
 Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}.
@@
 
-The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'" \cite{SpatialNarratives:npentrel14}.
+%The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'" \cite{SpatialNarratives:npentrel14}.
 Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\
 
-The benefits of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
+%The benefits of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
 By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
@@
 
-In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
-For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected.
+%In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:Annie-guided}).
 It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\
+\newpage
+\subsection{Impress.js}
+
+The jQuery plugin Impress.js was created by bartez.
+It works jointly with HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
+The presentation data is entered in the html file; each slide in its own div with data-x, data-y, and data-z attributes to change the position of the slide.
+The data-x and data-y axis change the position of the element according to the normal x- and y-axes.
+The data-z attribute changes the closeness of the elements along the z axis.\\
+\\
+\definecolor{bg}{rgb}{0.95,0.95,0.95}
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+<div class="step" data-x="1000" data-y="0">
+  Slide Content
+</div>
+\end{minted}
+
+Apart from these basic attributes, Impress.js offers the data-scale attribute to scale content, making slides appear bigger or smaller, and the data-rotate attribute which rotates slides in 3 dimensions using data-rotate-x, data-rotate-y, and data-rotate-z.\ednote{show robotics slide of 3d rotations - this allows the dependency timeline to go into the third dimension!!}\\
+
+In the following code snippets, a few other basic functionalities we will be using are explained.\ednote{cite http://www.andismith.com/blog/2012/01/impress-with-impress/} 
+The opacity attribute allows us to discriminate between active and inactive slides which will later on allow us to hide content so as to not throw too much information at a user.
+Adding an overview can be accomplished with the last past of the CSS snippet and the html snippet below that.\\
+\\
+
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+.step {
+  opacity: 0.2;
+}
+
+.step.active {
+  opacity: 1;
+}
+
+.step-overview .step {
+  opacity: 1;
+  cursor: pointer;
+}
+
+\end{minted}
+
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+<div id="overview" class="step" data-x="600" data-y="300" data-scale="2"></div>
+\end{minted}
+
+\ednote{check no cite} %http://www.1stwebdesigner.com/creating-stunning-visualizations-with-impress-js/#/slide1}
+
+%http://www.andismith.com/blog/2012/01/impress-with-impress/
+
+Linking to a slide
+%For example, a slide with an ID of "statistics" will be accessible by appending "#/statistics" to the end of the URL.
+
+presenter notes:
+%https://github.com/twenty-seven/im_present
+
+progress bar:
+%https://github.com/m42e/impress.js-progress
+
+Read the book
+Rakhitha Nimesh Ratnayake
+Building Impressive Presentations with impress.js
 
@@
 
-When searching for related works there is little to be found.
+%When searching for related works there is little to be found.
 Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}.
@@
 
-Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}.
+%Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}.
 The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects.

### 2015-05-03 Thesis.tex
Thesis grows

@@
 \fancyfoot{} % Blank out the default footer
-\fancyhead[C]{Naomi Pentrel $\bullet$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\bullet$ \today} % Custom header text
+\fancyhead[C]{Naomi Pentrel $\cdot$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\cdot$ \today} % Custom header text
 \fancyfoot[RO,LE]{\thepage} % Custom footer text
@@
 %----------------------------------------------------------------------------------------
-\newcommand{\sys}{\textsc{Knowtation}\xspace}
+\newcommand{\sys}{\textsc{RPresentation}\xspace}
 
@@
 \noindent
-  With my signature, I certify that this thesis has been written by me
-  using only the indicated resources and materials. Where I have
-  presented data and results, the data and results are complete,
-  genuine, and have been obtained by me unless otherwise acknowledged;
-  where my results derive from computer programs, these computer
-  programs have been written by me unless otherwise acknowledged. I
-  further confirm that this thesis has not been submitted, either in
-  part or as a whole, for any other academic degree at this or another
-  institution.
+With my signature, I certify that this thesis has been written by me using only the indicated resources and materials.
+Where I have presented data and results, the data and results are complete, genuine, and have been obtained by me unless otherwise acknowledged; where my results derive from computer programs, these computer programs have been written by me unless otherwise acknowledged.
+I further confirm that this thesis has not been submitted, either in part or as a whole, for any other academic degree at this or another institution.
 
@@
 Visualization of knowledge is important to foster learning.
-To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context.
+To optimize the visualization of information and its interdependencies, we focus on identifying ways to present information without loosing context.
 The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
-This form of presenting knowledge enable susers to interactively examine materials that are related to the topics the audience is interested in.\\
+This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.\\
 
@@
 The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, this research presents different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
-Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning while discussing several different schema that are ditaktisch wertvoll\ednote{check translation}.This approach to presenting learning materials changes how we interact with course material which will allow students to learn better.
+Using OMDoc, the implemented system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
+Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning while discussing several different presentation schemata that are valuable for learning.
+This approach to presenting learning materials changes how we interact with course material which will allow students to learn better.
 Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.\\
@@
 
-  \section{Introduction}
+\section{Introduction \& Motivation}
 \label{sec:introduction}
 
-%The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
-There are interesting similar developments in other fields such as that of new presentation tools.
-These aim to enable the presentation of information in a more interconnected way that provides context.
-Both developments strive to connect pieces of information through adding context, to not just provide information, but rather knowledge.\\
+Normally we only have one path for a narration.
+That is true for books, movies, Facebook timelines, and also presentations.
+For three out of those four this has not changed in decades.
+With the advancement of technology, we are, however, able to change the way presentations and their narratives work.
+In essence we should be able to make it possible to link content that logically belongs together, in other words, content that is semantically close.
+Through that it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined path, but rather along the path that will allow the audience to make the most out of the presentation.\\
 
-%The concept behind these two developments is quite similar.
+This idea of linking content is not new.
+When Tim Berners-Lee laid out his Semantic Web Roadmap \cite{BernersLee:tsw98}, its intention was to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
+Both strive to connect pieces of information through adding context and thus to not just provide information, but rather knowledge.
+Within presentations, the intention is to present information in a more interconnected way that provides context and thus facilitates understanding and learning.
+\\
+
+As pointed out in \ednote{Do I need to cite my proposal?}, the concept behind the semantic web and changing presentations is quite similar.
 Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content.
@@
 
-%In essence, both issues stem from information being generated without enough context or structure.
+In essence, both issues stem from information being generated without enough context or structure.
 This makes the information hard to process by humans and/or machines.
-The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.
+The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.\\
+
 The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information.
-It adapts some of the concepts of the semantic web on a smaller scale.\\
+It adapts some of the concepts of the semantic web on a smaller scale and connects information logically.
+The end product should be a system that creates presentations which allow users to choose their own narrative path where users can seamlessly look at related topics and brush up on half-forgotten topics.\\
 
@@
 
-%One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
+One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
 Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information.
@@
 
-%We want to go from merely displaying information to visualizing information by displaying the network/context of which a piece of information is part of.
-In this we will not try to semantically represent the meaning of the information that is shown but rather to show the network, i.e.
-the context the information is a part of.
-Specifically we want to examine whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\
+We want to go from merely displaying information to allowing users to interact with information and choosing a learning path that suits them individually.
+The concept of information existing in networks and relatedness of information will be used to display not just the prescribed presentation path but also allow the user to deviate from the path to go back to topics that form the preliminary knowledge base for the current topic.
+Specifically this research examines whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\
 
-%To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks).
-For this we will be using the OMDoc (Open Mathematical Documents) format which will provide us with an annotated set of documents.
-This will give us information about the semantic closeness of different pieces of information.
+To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks).
+For this we will be using the OMDoc (Open Mathematical Documents) format which, given an annotated set of documents, will provide us with the necessary HTML-representation of the information.
+This will also allow us to extract information about the semantic closeness of different pieces of information.
 Taking this as a starting point, we will visualize the dependencies of the information contained in these documents.
-Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative with the help of a presentation framework such as Impress.js in order to show the current piece of information of interest within the network of dependent information.\\
+We will visualize the dependencies in a simple but effective approach with basic elements of spatial narrative using the presentation framework Impress.js.
+The final product will allow for an interactive way of viewing a presentation.\\
 
-\begin{figure}[H]
-        \centering
-        \begin{subfigure}[b]{0.47\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
-			   \caption{Simple, explanatory slide}
-                \label{fig:Annie-presentation-teacher}
-        \end{subfigure}%
-        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.47\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
-		  \caption{Information dependencies}
-                \label{fig:Annie-presentation-information}
-        \end{subfigure}
-        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
-\end{figure}
-
-%To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}).
+\ednote{readd slide images}
+To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure %\ref{fig:Annie-presentation-teacher}
+).
 She is given a triangle with sides a = 3 cm and b = 4 cm.
@@
 Now Annie has to try to find out what a right triangle is.
-This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e.
+This shows the dependencies of different pieces of information (see figure %\ref{fig:Annie-presentation-information}
+), i.e.
 the Pythagorean theorem depends on knowledge of squares, triangles, lengths, area calculation, and right angles.
@@
 
-%After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
+After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
 There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
 \\
+
+\section{Research Questions}
+
+As we have pointed out in \autoref{sec:introduction}, presenting information in an effective way is essential to foster learning. This research will answer the following basic questions:
+
+\begin{itemize}
+\item How can we combine spatial narrative and semantic closeness of information to improve the presentation of information?
+\item Which ways of visualizing information dependencies are there?
+\end{itemize}
+
+\section{Related Work}
+\label{sec:relatedworks}
+
+When searching for related work there is little to be found.
+Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}.
+For this systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
+Some of these systems use temporal information \cite{DBLP:dblp_journals/isci/ChungS97} to show multiple resources in sync as they appeared in the lecture.
+However, while this approach also aims at improving the learning experience, it does not in any way link content semantically based on dependencies or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\
+
+Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}.
+The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects.
+While the research at hand also intends to show the relation between pieces of information, it does it on a different level.
+For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map.
+We, on the other hand, will focus on exactly that, i.e.
+dependencies and the creation of interactive presentations.\\
 
@@
 
-As we have pointed out in the \ref{sec:introduction}, presenting information in an efficient way is essential in order for any learning to occur.
-In the following we will examine some prerequisite knowledge.
-By engaging with our example presentation we will show how Annie's teacher can transfer knowledge more effectively.\\
+In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how Annie's teacher can transfer knowledge more effectively.\\
 
@@
 
-%The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
-Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
+The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
+Recalling figure %\ref{fig:PythagoreanTheorem}
+\ednote{readd figures}
+ and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
 For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
@@
 We will define it as knowledge that is made up out of several pieces of information that are connected.
-In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see figure \ref{fig:Annie-presentation-information}).\\
+In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see figure %\ref{fig:Annie-presentation-information}
+ ).\\
 
-\ednote{In current presentations there is only one context. By adding more levels of context we can allow viewers to understand the subject on a deeper level.}
-
-%According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
+According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
 Context can be easily explained with the example of Annie learning the Pythagorean theorem.
@@
 We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\
-\newpage
+
 \subsection{OMDoc}
@@
 
-%OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
+OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
 As such it is a semi-formal domain ontology.
@@
 
-%If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways.
+If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways.
 This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts.
@@
 Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
-\newpage
+
 \subsection{Status of Information within the (Dis)Course}
@@
 
-%In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
+In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
 Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information.
@@
 
-%In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced.
+In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced.
 In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
@@
 
-%These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
+These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
 In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}.
@@
 
-%Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
+Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
 The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
@@
 Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
-\\
-\newpage
+\ednote{check example and later on refer to this with the different levels.} \\
+
 \subsection{Different Representations of Information}
 \label{sec:inforep}
-
+\ednote{Needs a lot of changing. Maybe it won't fit anymore at all.}
 %Information can be (re)presented in different ways: text, visuals, images, etc.
@@
 
-\begin{figure}[H]
-        \centering
-        \begin{subfigure}[b]{0.3\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{assets/size-of-objects}}
-                \caption{Importance of Objects}
-                \label{fig:imp_objects}
-        \end{subfigure}%
-        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.3\textwidth}
-                \fbox{\includegraphics[width=\textwidth]{assets/relation}}
-                \caption{Relation of Objects}
-                \label{fig:rel_objects}
-        \end{subfigure}
-        \caption{Conveying Visual Meaning}\label{fig:Objects}
-\end{figure}
+%\begin{figure}[H]
+%        \centering
+%        \begin{subfigure}[b]{0.3\textwidth}
+%                \fbox{\includegraphics[width=\textwidth]{assets/size-of-objects}}
+%                \caption{Importance of Objects}
+%                \label{fig:imp_objects}
+%        \end{subfigure}%
+%        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+%          %(or a blank line to force the subfigure onto a new line)
+%        \begin{subfigure}[b]{0.3\textwidth}
+%                \fbox{\includegraphics[width=\textwidth]{assets/relation}}
+%                \caption{Relation of Objects}
+%                \label{fig:rel_objects}
+%        \end{subfigure}
+%        \caption{Conveying Visual Meaning}\label{fig:Objects}
+%\end{figure}
 
@@
 In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\
-
-\begin{figure}[H]
-        \centering
-		    \fbox{\includegraphics[width=0.6\textwidth]{assets/Annie4size}}
-  \caption{Relative size and relations} 
-  \label{fig:Annie-relsize}
-\end{figure}
 
@@
 \\
-\newpage
+
 \subsection{Spatial Narrative}
@@
 It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\
-\newpage
+
 \subsection{Impress.js}
+\label{sec:Impressjs}
 
-The jQuery plugin Impress.js was created by bartez.
-It works jointly with HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
+\ednote{here or rather in 5.3?}
+
+For the implementation of \sys, we chose to use Impress.js, as applications like Prezi do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
+The open-source presentation framework \textbf{Impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's.
+It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
 The presentation data is entered in the html file; each slide in its own div with data-x, data-y, and data-z attributes to change the position of the slide.
@@
 
-Apart from these basic attributes, Impress.js offers the data-scale attribute to scale content, making slides appear bigger or smaller, and the data-rotate attribute which rotates slides in 3 dimensions using data-rotate-x, data-rotate-y, and data-rotate-z.\ednote{show robotics slide of 3d rotations - this allows the dependency timeline to go into the third dimension!!}\\
+\begin{wrapfigure}{r}{0.3\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.28 \textwidth]{assets/rotate}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Rotations}
+  \label{fig:Rotate}
+\vspace{-10pt}
+\end{wrapfigure}
+
+Apart from these basic attributes, Impress.js offers the data-scale attribute to scale content, making slides appear bigger or smaller, and the data-rotate attribute which rotates slides in 3 dimensions using data-rotate-x, data-rotate-y, and data-rotate-z.
+As shown in \autoref{fig:Rotate} this allows the dependency graph to go into the third dimension.\\
 
@@
 Adding an overview can be accomplished with the last past of the CSS snippet and the html snippet below that.\\
-\\
 
 \begin{minted}[linenos=true, bgcolor=bg]{C}
-.step {
-  opacity: 0.2;
-}
+.step { opacity: 0.2; }
+.step.active { opacity: 1; }
+.step-overview .step { opacity: 1; cursor: pointer; }
+\end{minted}
+\vspace*{2mm}\\
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+<div id="overview" class="step" data-x="8000" data-y="1000" data-scale="10">
+</div>
+\end{minted}
+\\
+To link back to a slide, slides are accessible via IDs. The slide with the ID "conclusion" will thus be accessible by appending "\#/conclusion" to the end of the URL.
 
-.step.active {
-  opacity: 1;
-}
+\ednote{check link} %http://www.1stwebdesigner.com/creating-stunning-visualizations-with-impress-js/#/slide1}
+%http://www.andismith.com/blog/2012/01/impress-with-impress/
 
-.step-overview .step {
-  opacity: 1;
-  cursor: pointer;
-}
+%progress bar:
+%https://github.com/m42e/impress.js-progress
 
+%Read the book
+%Rakhitha Nimesh Ratnayake
+%Building Impressive Presentations with impress.js
+
+\section{Towards a More Effective Presentation Format}
+\label{sec:TowardsAMoreEffectivePresentationFormat}
+
+\subsection{Creation of Ordered Information Graphs using OMDoc}
+\label{sec:wp2}
+
+With the OMDoc framework and its tools it is possible to write down a paper in stex.
+From this paper we can then, in theory, seamlessly create slides both in pdf format as well as in xhtml format.
+Using a test paper that is supposed to explain the pythagorean theorem and related topics, we can thus create an XML information graph out of the annotated set of documents.\\
+
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+theory path/to/file?theory_name
+Includes path/to/file path/to/dependent/file?theory_name
 \end{minted}
 
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-<div id="overview" class="step" data-x="600" data-y="300" data-scale="2"></div>
-\end{minted}
+The system itself outputs information about dependencies of topics as shown above.
+Using the \sys \ednote{should I cite my github?} tool we created for this research project, it is possible to get the order of the slides as well as dependencies.
+The order of information in certain topics will be referred to as levels.
+If we look at the pythagorean theorem and then realize we lack knowledge the concept of squares we could then read about that topic by going to that resource.
+From there on we are on a different \textit{level} which we can follow and dig deeper into until we understand squares.\\
+\ednote{draw the whole graph and add here}
+\ednote{add somewhere: By adding more levels of context we can allow viewers to understand the subject on a deeper level.}
 
-\ednote{check no cite} %http://www.1stwebdesigner.com/creating-stunning-visualizations-with-impress-js/#/slide1}
+%narrative and mroe info
 
-%http://www.andismith.com/blog/2012/01/impress-with-impress/
+% for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
+Knowing the dependencies and the status of the information will allow us to choose which information to show the user in the close surroundings of the current information we are showing.\\
 
-Linking to a slide
-%For example, a slide with an ID of "statistics" will be accessible by appending "#/statistics" to the end of the URL.
+\subsubsection{Narrative Paths}
+\subsubsection{Levels}
 
-presenter notes:
-%https://github.com/twenty-seven/im_present
-
-progress bar:
-%https://github.com/m42e/impress.js-progress
-
-Read the book
-Rakhitha Nimesh Ratnayake
-Building Impressive Presentations with impress.js
-
-\subsection{Related Work}
-\label{sec:relatedworks}
-
-%When searching for related works there is little to be found.
-Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}.
-For this systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
-Some of these systems use temporal information \cite{DBLP:dblp_journals/isci/ChungS97} to show multiple resources in sync as they appeared in the lecture.
-However, while this approach also aims at improving the learning experience, it does not in any way link content semantically based on dependencies or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\
-
-%Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}.
-The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects.
-While the proposed research also intends to show the relation between pieces of information, it does it on a different level.
-For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map.
-We, on the other hand, will focus on exactly that, i.e.
-dependencies and the creation of interactive presentations.\\
-
-\section{Work Plan}
-\label{sec:workplan}
-
-\subsection{WP1: Understanding the API of Impress.js}
+\subsection{Using Impress.js to Combine OMDoc and Spatial Narration}
 \label{sec:wp1}
 
-The first step to implementing \sys is to understand the tool we want to represent the knowledge in later.
-Since Prezi at the current time does not have an Application Programming Interface (API) that would allow for the generation of a whole presentation without using the editor, this research will employ another tool that is inspired by the idea behind Prezi.
-Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions.\\
+With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file.
+Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}.
+The primary narrative that the presenter wants to follow is formed by a horizontal stream of slides.
+\ednote{add picture of this}\\
 
-Impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
+This horizontal stream of slides is achieved by giving the slides incremental data-x values in the attributes.
+If a slide has dependencies then these will be added as slides below the slide itself.
+This, in turn, is achieved by keeping the data-x value but increasing the data-y value.
+Thus users can now simply press down and explore all the dependent information.\\
+
+If they, while browsing through these different levels, realize that they need to refresh their memory or learn more about any of the dependent information they can enter that level.
+The presentation will then continue on that level and give all the slides from that topic in the correct order.
+Once the user has gone through this short excursion, he or she can return to the initial slide and resume the normal narrative path.
+These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
+Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\
+
+%Impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
 Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation.
@@
 
-After finishing this part we should have several different presentation styles from which one can be chosen to continue the main research question.\\
-
-\subsection{WP2: Creation of Ordered Information Graphs using OMDoc}
-\label{sec:wp2}
-
-The idea is to use the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} as an experiment.
-The General Computer Science Lecture notes are an annotated set of documents.
-Using OMDoc, we will create an XML information graph out of the annotated set of documents.\\
-
-The information graph OMDoc provides us with should be topologically sorted based on dependencies of knowledge.
-This will allow us to assign values representing the status of information within the course as outlined in section \ref{sec:infostatus}.
-It will also allow us to create values for the relative semantic closeness of information which will be needed for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
-Knowing the dependencies and the status of the information will allow us to choose which information to show the user in the close surroundings of the current information we are showing.\\
-
-Each piece of information needs to also have an importance level assigned to it (see section \ref{sec:inforep}).
-This ought to be determined by counting how often the concept is used and how important it is for the student to grasp it.\\
-
-\subsection{WP3: Combination of OMDoc and Spatial Narration}
-\label{sec:wp3}
-
-Once we have an ordered information graph with all the additional attribute values mentioned in section \ref{sec:wp2}, we will create the knowledge presentation system \sys.
+%Once we have an ordered information graph with all the additional attribute values mentioned in section \ref{sec:wp2}, we will create the knowledge presentation system \sys.
 \sys will visualize the information from the graph including all the attributes we added.
@@
 
-\subsection{WP4: Implementation of OMDoc Examples in Impress.js}
+\subsection{Implementation of \sys}
 \label{sec:wp4}
+\ednote{Do I need this or is it okay if I explain it on the go as I do so far?}
 
-\sys will take the ordered information graph of the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} with all the additional attributes we generated in \ref{sec:wp2} and transform it into a spatial presentation using Impress.js.
+%\sys will take the ordered information graph of the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} with all the additional attributes we generated in \ref{sec:wp2} and transform it into a spatial presentation using Impress.js.
 This will be done by parsing the generated XML and creating the markup that Impress.js is using to create the chosen presentation models from section \ref{sec:wp1}.
@@
 
-It is a stretch goal for \sys to create or change these presentations on the fly as needed by the audience.
+%It is a stretch goal for \sys to create or change these presentations on the fly as needed by the audience.
 The specific use case would be when Annie asks her teacher about right angles.
@@
 
-\subsection{WP5: Qualitative Analysis and Evaluation of Findings}
-\label{sec:wp5}
+\section{Evaluation}
+\label{sec:evalcriteria}
 
-Once we have examples, we will undertake a qualitative analysis of the visualization produced by the implemented knowledge presentation system \sys .
+\subsection{General Evaluation}
+
+\subsection{Shortcomings and Problems with the System}
+
+%Once we have examples, we will undertake a qualitative analysis of the visualization produced by the implemented knowledge presentation system \sys .
 To achieve this, we will use the newly created examples from \ref{sec:wp4} and the general General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base}.
@@
 
-\section{Evaluation Criteria}
-\label{sec:evalcriteria}
-
-The evaluation criteria for the research at hand are, on the one hand, systematic and, on the other hand, cognitive.
+%The evaluation criteria for the research at hand are, on the one hand, systematic and, on the other hand, cognitive.
 Systematically, we will be evaluating two main challenges: First we will evaluate whether the knowledge presentation system \sys that was developed allows for the creation of a full presentation from a given annotated document.
@@
 
-Cognitively, we will be exploring the space of information systems.
+%Cognitively, we will be exploring the space of information systems.
 Therefore we will be examining whether the developed system provides a better system for knowledge transfer.
@@
 
-Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.\\
+%Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.\\
 
-If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
+%If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
 If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers which other parameters need to be kept in mind in order to succeed in future.\\
 
-A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
+%A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
 Another stretch goal is for \sys to create or change presentations on the fly as outlined in \ref{sec:wp4}.
 It is not the goal of this research that users should be able to reconstruct the original information graph from the presentation.\\
-\newpage
-\section{Timeline}
-\label{sec:timeline}
 
-\begin{figure}[H]
-\begin{center}
-\begin{ganttchart}[y unit title=0.4cm,
-y unit chart=0.5cm,
-vgrid,hgrid, 
-title label anchor/.style={below=-1.6ex},
-title left shift=.05,
-title right shift=-.05,
-title height=1,
-bar/.style={fill=gray!50},
-incomplete/.style={fill=white},
-progress label text={},
-bar height=0.7,
-group right shift=0,
-group top shift=.6,
-group height=.3,
-group peaks={}{}{.2}]{24}
-%labels
-\gantttitle{Proposed Timeline}{24} \\
-\gantttitle{December}{4} 
-\gantttitle{January}{4} 
-\gantttitle{February}{4} 
-\gantttitle{March}{4} 
-\gantttitle{April}{4} 
-\gantttitle{May}{4} \\
-%tasks
-\ganttbar{\ref{sec:wp1} WP1}{2}{8} \\
-\ganttbar{\ref{sec:wp2} WP2}{9}{12} \\
-\ganttbar{\ref{sec:wp3} WP3}{11}{14} \\
-\ganttbar{\ref{sec:wp4} WP4}{15}{18}\\
-\ganttbar{\ref{sec:wp5} WP5}{19}{21.5}
-%relations 
-\ganttlink{elem0}{elem1} 
-\ganttlink{elem1}{elem2} 
-\ganttlink{elem2}{elem3} 
-\ganttlink{elem3}{elem4} 
-\end{ganttchart}
-\end{center}
-\caption{Gantt Chart}
-\end{figure}
+\section{Further Developments}
 
-\textbf{Milestones}
-\begin{itemize}
-\item \textbf{Until February 1st}: \nameref{sec:wp1}
-\item \textbf{Until March 1st}: \nameref{sec:wp2}
-\item \textbf{Until March 15th}: \nameref{sec:wp3}
-\item \textbf{Until April 15th}:\nameref{sec:wp4}
-\item \textbf{Until May 10th}: \nameref{sec:wp5}
-\end{itemize}
+\ednote{e.g. need to test this via qualitative analysis}
 
@@
 
-The proposed research will evaluate if and how spatial narrative can be combined with semantic closeness to form visual presentations that will facilitate knowledge transfer.
+%The proposed research will evaluate if and how spatial narrative can be combined with semantic closeness to form visual presentations that will facilitate knowledge transfer.
 The knowledge presentation systen \sys that we will implement will allow us to automatically create these visual presentations from the OMDoc format.
@@
 
-Going back to our contrived example, \sys will provide Annie's teacher with a tool that allows her to use her normal lecture material in a more interactive way.
+%Going back to our contrived example, \sys will provide Annie's teacher with a tool that allows her to use her normal lecture material in a more interactive way.
 Thus when the teacher realizes that Annie needs to revise previous material, the teacher can easily go to that material and provide Annie with a good learning experience.
@@
 
-But not only will \sys make courses more engaging, interactive, and easier to follow, it will also lead to better knowledge absorption because students learn the concepts and in addition intuitively understand how they relate to one another.
+%But not only will \sys make courses more engaging, interactive, and easier to follow, it will also lead to better knowledge absorption because students learn the concepts and in addition intuitively understand how they relate to one another.
 This allows faster revision of material and facilitates studying without a teacher present.\\
 
-In essence, this proposed research will be beneficial for education and knowledge transfer.
+%In essence, this proposed research will be beneficial for education and knowledge transfer.
 It aims to make the creation of engaging and interactive presentations simple and fast for current users of OMDoc.

### 2015-05-07 Thesis.tex
LOADS of changes

@@
 \usepackage{wrapfig}
+\usepackage[]{natbib}
+\usepackage{tocloft}
 
-\usepackage{tocloft}
+\def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
+\def\sTeX{\stex}
 
@@
 \label{sec:introduction}
+\ednote{shorten}
 
 Normally we only have one path for a narration.
-That is true for books, movies, Facebook timelines, and also presentations.
+That is true for books, movies, Facebook timelines, and also slide-based presentations.
 For three out of those four this has not changed in decades.
@@
 
-As pointed out in \ednote{Do I need to cite my proposal?}, the concept behind the semantic web and changing presentations is quite similar.
+\ednote{how relevant?}
+The concept behind the semantic web and changing presentations is quite similar.
 Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content.
@@
 
-One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.
+One can define knowledge as "the information necessary to support intelligent reasoning" \cite{Kohlhase:Complog:base}.
+That said, it is imperative to facilitate knowledge transfer.
 Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information.
@@
 
-\section{Research Questions}
+%\section{Research Questions}
 
-As we have pointed out in \autoref{sec:introduction}, presenting information in an effective way is essential to foster learning. This research will answer the following basic questions:
+%As we have pointed out in \autoref{sec:introduction}, presenting information in an effective way is essential to foster learning. This research will answer the following basic questions:
 
-\begin{itemize}
-\item How can we combine spatial narrative and semantic closeness of information to improve the presentation of information?
-\item Which ways of visualizing information dependencies are there?
-\end{itemize}
+%\begin{itemize}
+%\item How can we combine spatial narrative and semantic closeness of information to improve the presentation of information?
+%\item Which ways of visualizing information dependencies are there?
+%\end{itemize}
 
@@
 dependencies and the creation of interactive presentations.\\
+
+There has also been research focusing on guided tours in mathematics \cite{SieBen:acgap00}.
+This creates guided tours on topics depending on the background of the user.
+While following the same ideal to improve knowledge transfer, it differs from this work in the fact that its presentation format is completely different.
+While Siekmann et al., focused on one topic and displaying it differently to users with different backgrounds, this research will show the topics of a whole course while allowing to see dependencies and while allowing to diverge from the prescribed presentation path.\\
+
+Adding on to the research about guided tours in mathematics, there has also been research on semantic document navigation \cite{Koh:NavigationInMathDocs2012}.
+It demonstrates the need for assistance in form of navigation support for the reading of mathematical documents by creating a system that allows for semantic navigation in Excel spreadsheets.
+This research underlines the importance of a system that allows users to navigate information according to dependencies.\\
 
@@
 
-%The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
+The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
 Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}.
@@
 
-%The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'" \cite{SpatialNarratives:npentrel14}.
+The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'" \cite{SpatialNarratives:npentrel14}.
 Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\
 
-%The benefits of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
+The benefits of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
 By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
@@
 
-%In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
 For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:Annie-guided}).
@@
 
-\ednote{here or rather in 5.3?}
-
-For the implementation of \sys, we chose to use Impress.js, as applications like Prezi do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
+For the implementation of \sys, we chose to use Impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
 The open-source presentation framework \textbf{Impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's.
 It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
-The presentation data is entered in the html file; each slide in its own div with data-x, data-y, and data-z attributes to change the position of the slide.
-The data-x and data-y axis change the position of the element according to the normal x- and y-axes.
-The data-z attribute changes the closeness of the elements along the z axis.\\
-\\
-\definecolor{bg}{rgb}{0.95,0.95,0.95}
+The presentation data is entered in the html file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide.
+The \texttt{data-x} and \texttt{data-y} axis change the position of the element according to the normal x- and y-axes.
+The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
+\definecolor{bg}{rgb}{0.90,0.90,0.90}
+
+\begin{wrapfigure}{r}{\textwidth}
+\vspace{-26pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
+\vspace{-5pt}
+  \caption{Code Snippet to Create a Slide}
+  \label{fig:SSlide}
+  \vspace{12pt}
+\end{wrapfigure}
 
@@
 \vspace{-20pt}
-  \caption{Rotations}
+  \caption{Rotations \cite{Rotations:npentrel14}}
   \label{fig:Rotate}
@@
 
-Apart from these basic attributes, Impress.js offers the data-scale attribute to scale content, making slides appear bigger or smaller, and the data-rotate attribute which rotates slides in 3 dimensions using data-rotate-x, data-rotate-y, and data-rotate-z.
+Apart from these basic attributes, Impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}.
 As shown in \autoref{fig:Rotate} this allows the dependency graph to go into the third dimension.\\
 
-In the following code snippets, a few other basic functionalities we will be using are explained.\ednote{cite http://www.andismith.com/blog/2012/01/impress-with-impress/} 
+In the following code snippets, a few other basic functionalities we will be using are explained \cite{andismith:npentrel15}.
 The opacity attribute allows us to discriminate between active and inactive slides which will later on allow us to hide content so as to not throw too much information at a user.
@@
 
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-26pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
-\vspace*{2mm}\\
+\vspace{-5pt}
+  \caption{Code Snippet to Show and Hide Content}
+  \label{fig:SSlide}
+  \vspace{30pt}
+\end{wrapfigure}
+
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-26pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
-\\
-To link back to a slide, slides are accessible via IDs. The slide with the ID "conclusion" will thus be accessible by appending "\#/conclusion" to the end of the URL.
+\vspace{-7pt}
+  \caption{Code Snippet for an Overview}
+  \label{fig:SSlide}
+  \vspace{12pt}
+\end{wrapfigure}
 
-\ednote{check link} %http://www.1stwebdesigner.com/creating-stunning-visualizations-with-impress-js/#/slide1}
-%http://www.andismith.com/blog/2012/01/impress-with-impress/
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
 
-%progress bar:
-%https://github.com/m42e/impress.js-progress
-
-%Read the book
-%Rakhitha Nimesh Ratnayake
-%Building Impressive Presentations with impress.js
+To link back to a slide, slides are accessible via IDs. The slide with the ID \texttt{conclusion} will thus be accessible by appending \texttt{\#/conclusion} to the end of the URL.
 
@@
 
+Building on the preliminaries, we will now commence the journey towards building a more effective presentation format.
+To begin with the creation of a tool, RPresentation \cite{npentrel:npentrel15}, for building these presentations automatically will be discussed.
+In the next section, we will then examine how this makes presentations more effective.
+
 \subsection{Creation of Ordered Information Graphs using OMDoc}
@@
 
-With the OMDoc framework and its tools it is possible to write down a paper in stex.
-From this paper we can then, in theory, seamlessly create slides both in pdf format as well as in xhtml format.
-Using a test paper that is supposed to explain the pythagorean theorem and related topics, we can thus create an XML information graph out of the annotated set of documents.\\
+With the OMDoc framework and its tools it is possible to write down course notes or other documents in \stex.
+From this document we can then, in theory, seamlessly create slides both in PDF format as well as in XHTML format.
+Using a test document that is supposed to explain the pythagorean theorem and related topics, we can thus create an XML information graph out of the annotated documment.\\
 
+\begin{wrapfigure}{r}{\textwidth}
+\vspace{-26pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
+\vspace{-5pt}
+  \caption{Code Snippet of Relational Data}
+  \label{fig:SSlide}
+  \vspace{12pt}
+\end{wrapfigure}
+
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+\ednote{explain further}
 
 The system itself outputs information about dependencies of topics as shown above.
-Using the \sys \ednote{should I cite my github?} tool we created for this research project, it is possible to get the order of the slides as well as dependencies.
+Using the \sys tool I created for this research project, it is possible to get the order of the slides as well as dependencies.
 The order of information in certain topics will be referred to as levels.
@@
 \ednote{add somewhere: By adding more levels of context we can allow viewers to understand the subject on a deeper level.}
+
+\ednote {explain ids of slides}
 
@@
 
-\subsection{Using Impress.js to Combine OMDoc and Spatial Narration}
+\subsection{Creating Relational Presentations}
 \label{sec:wp1}
@@
 
-This horizontal stream of slides is achieved by giving the slides incremental data-x values in the attributes.
+This horizontal stream of slides is achieved by giving the slides incremental \texttt{data-x} values in the attributes.
 If a slide has dependencies then these will be added as slides below the slide itself.
-This, in turn, is achieved by keeping the data-x value but increasing the data-y value.
+This, in turn, is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value.
 Thus users can now simply press down and explore all the dependent information.\\
@@
 
-\subsection{Implementation of \sys}
+\subsection{Technical Details}
 \label{sec:wp4}
-\ednote{Do I need this or is it okay if I explain it on the go as I do so far?}
 
-%\sys will take the ordered information graph of the General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base} with all the additional attributes we generated in \ref{sec:wp2} and transform it into a spatial presentation using Impress.js.
-This will be done by parsing the generated XML and creating the markup that Impress.js is using to create the chosen presentation models from section \ref{sec:wp1}.
-After this work package, we should have one (or more) presentations of the topics covered in the General Computer Science Lecture notes.\\
+To implement \sys we rely on the Local MathHub Tool (lmh) which creates our input data.
+As input data we take, the \sTeX files of the document, the information about dependencies, and the XHTML of the slides.
+We use this information in several steps in our system \sys:
 
-%It is a stretch goal for \sys to create or change these presentations on the fly as needed by the audience.
-The specific use case would be when Annie asks her teacher about right angles.
-The teacher would then just have to click on right angles and \sys would create a short guided tour through the topic of right angles before returning to the subject of the Pythagorean theorem.\\
+\begin{enumerate}
+\item Get user input for the location and name of the folder
+\item Parsing \sTeX to retrieve the order of information
+\item Extracting relational information from \ednote{ref}
+\item Extracting necessary HTML parts
+\item Creation of presentation
+\end{enumerate}
+
+For the implementation of  \sys Java was used. It would have been possible to choose other programming languages, however, using Java, we end up with platform-independent code.\\
+
+In the last step, where the presentation is created, we use self-created boilerplate code, in which only some coordinates and the HTML for the slide is added.
+For the presentation Impress.JS was chosen such that the HTML code, automatically generated by lmh, can be reused.
+An important additional reason for the choice of Impress.JS is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and and \autoref{sec:Impressjs}.\\
+
+Due to the choice of Impress.JS \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
+Impress.JS works in all modern browsers that support CSS 3D transforms.
 
@@
 
+Even though an evaluation is not fully possible given the limited time frame, the next subsections will attempt to evaluate the created system and the created presentations as well as their shortcomings.
+Afterwards we will briefly look at future work and possible extensions to our system.
+
 \subsection{General Evaluation}
 
-\subsection{Shortcomings and Problems with the System}
-
-%Once we have examples, we will undertake a qualitative analysis of the visualization produced by the implemented knowledge presentation system \sys .
-To achieve this, we will use the newly created examples from \ref{sec:wp4} and the general General Computer Science Lecture notes \cite{Kohlhase:GenCSI:base}.
-We will have two groups: a control group that is shown the lecture notes and a test group that is shown the new, interactive Impress.js presentations.
-Afterwards both groups have to answer a set of questions.
-In addition, we will determine whether the implemented \sys meets the goals outlined in the Evaluation Criteria (see section \ref{sec:evalcriteria}).\\
-
-%The evaluation criteria for the research at hand are, on the one hand, systematic and, on the other hand, cognitive.
-Systematically, we will be evaluating two main challenges: First we will evaluate whether the knowledge presentation system \sys that was developed allows for the creation of a full presentation from a given annotated document.
-Then we will evaluate the speed of \sys.
-Special attention will be given to the question whether this could be used in real time such that a student could request a presentation on a certain topic and whether this could be generated on the fly within seconds.\\
+The evaluation conducted in the following part is on the one hand, systematic and, on the other hand, cognitive.
+Systematically, the knowledge presentation system \sys that was developed allows for the creation of a full relational presentation from a given annotated document which fulfills the goal of this project.
+It does so in a very timely manner.
 
@@
 
+\subsection{Shortcomings and Problems with the System}
+
+For browsers that cannot display the created presentations fallback styles could be added to make the content accessible.
+
+\ednote{lmh not working :(}
+
 %If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
@@
 
-%A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations.
-Another stretch goal is for \sys to create or change presentations on the fly as outlined in \ref{sec:wp4}.
-It is not the goal of this research that users should be able to reconstruct the original information graph from the presentation.\\
+\ednote{ImpressJS had to be changed}
 
-\section{Further Developments}
+\section{Future Work and Possible Extensions}
 
-\ednote{e.g. need to test this via qualitative analysis}
+This section lists some ideas on future work regarding this topic and the created system \sys.
+Before embarking on improvements of the system, a qualitative and quantitative analysis of the produced visual presentations should be conducted to confirm that this system helps users.
+For the quantitative analysis it would be ideal to take a course that has already been taught using a more traditional approach to presentations which can then function as a control group.
+After teaching the whole course using the newly created presentation, the data of how the students in this test group performed can be compared with the gathered data from how students used to perform in the course.
+For a qualitative analysis, students who have been subject to the use of and who have actively used the new presentation could be interviewed.\\
+
+Apart from an analysis to evaluate the effectiveness of the created presentations, the whole system could be made more user friendly for both the creator and the users of the presentations.
+By improving the creation user interface and allowing for users to choose their own designs, it becomes more easy to use and more attractive for users.
+Adding an editor would make this much more user friendly for creators as well.
+To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\
+
+In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make important information bigger than less important information using the \texttt{data-scale} attribute.
+This would further add more semantic meaning to the slides.
+Additionally, one could think about adding a progress bar by using the work of Matthias Bilger \cite{bilger:npentrel15} to motivate users to continue.\\
+
+Overall it is even thinkable to create a different version of this system that could be made available to common users outside this research domain.
+The idea would be to allow users to add slides in an editor and to allow them to add dependencies themselves.
+Possibly the system could even suggest dependencies.
+As an example, I could very well envision a biology presentation that explains Photosynthesis and allows the attentive student to catch up on processes that transform ADP to ATP.\\
 

### 2015-05-07 Thesis.tex
primitives changed

@@
 Taking this as a starting point, we will visualize the dependencies of the information contained in these documents.
-We will visualize the dependencies in a simple but effective approach with basic elements of spatial narrative using the presentation framework Impress.js.
+We will visualize the dependencies in a simple but effective approach with basic elements of spatial narrative using the presentation framework impress.js.
 The final product will allow for an interactive way of viewing a presentation.\\
@@
 
-%Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
+Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
 Primitives are the different elements of representation.
@@
 
-%Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter.
+Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter.
 When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes.
@@
 
-%For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures.
-The frames can be mapped directly to the nodes/concepts that graphs use.
-Text and images are taken for granted within the frames.
-Similarly, the visual relation between different frames is very much like the relations between nodes.
-However, the relations can be much more expressive within Impress.js.\\
+For impress.js, the primitive elements are text, images, slides, and the visual relation between the different frame-like structures.
+The slides can be mapped directly to the nodes/concepts that graphs use.
+Text and images are taken for granted within the slides.
+Similarly, the visual relation between different slides is very much like the relations between nodes.
+However, the relations can be much more expressive within impress.js.\\
 
-%Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information.
-Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
+These relations or connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
 As such the temporal associations show the path that a normal lecture would take.
-The dependencies that are visualized around each frame allow for interactiveness.\\
-
-%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
-Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
-\\
+The dependencies that are visualized around each frame allow for additional interactiveness.\\
 
@@
 
-The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
+The development of presentation tools like impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
 Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}.
@@
 
-\subsection{Impress.js}
+\subsection{impress.js}
 \label{sec:Impressjs}
 
-For the implementation of \sys, we chose to use Impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
-The open-source presentation framework \textbf{Impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's.
+For the implementation of \sys, we chose to use impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
+The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's.
 It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
@@
 
-Apart from these basic attributes, Impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}.
+Apart from these basic attributes, impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}.
 As shown in \autoref{fig:Rotate} this allows the dependency graph to go into the third dimension.\\
@@
 
-%Impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
+%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
 Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation.
@@
 Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}).
-Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within Impress.js.\\
+Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within impress.js.\\
 
@@
 We will then use \sys to visualize information in WP4.\\
+
+% Layout
+%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
+Ideally the added expressiveness that impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+\\
 
@@
 In the last step, where the presentation is created, we use self-created boilerplate code, in which only some coordinates and the HTML for the slide is added.
-For the presentation Impress.JS was chosen such that the HTML code, automatically generated by lmh, can be reused.
-An important additional reason for the choice of Impress.JS is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and and \autoref{sec:Impressjs}.\\
+For the presentation impress.js was chosen such that the HTML code, automatically generated by lmh, can be reused.
+An important additional reason for the choice of impress.js is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and and \autoref{sec:Impressjs}.\\
 
-Due to the choice of Impress.JS \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
-Impress.JS works in all modern browsers that support CSS 3D transforms.
+Due to the choice of impress.js \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
+mpress.js works in all modern browsers that support CSS 3D transforms.
 
@@
 
-In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make important information bigger than less important information using the \texttt{data-scale} attribute.
+In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make use of relative size to additionally convey importance using impress.js' \texttt{data-scale} attribute.
 This would further add more semantic meaning to the slides.

### 2015-05-08 Thesis.tex
Rewriting main part

@@
 \usepackage{minted}
+\usepackage{enumitem}
 \usepackage[section]{placeins}
@@
 
-%In \textit{A mathematical approach to ontology authoring and documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers".
-In our case, the content layers are the mathematical objects, i.e.
-the statements or theories.
-Narrative layers refer to the order the mathematical objects from content layers are presented.
-In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them.
-Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects.
-These levels of semantic closeness are represented through the different sizes of the frames of the related information.
-In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness of content.
-Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\
-
 \subsection{Status of Information within the (Dis)Course}
@@
 Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
-\ednote{check example and later on refer to this with the different levels.} \\
-
-\subsection{Different Representations of Information}
-\label{sec:inforep}
-\ednote{Needs a lot of changing. Maybe it won't fit anymore at all.}
-%Information can be (re)presented in different ways: text, visuals, images, etc.
-Actually everything that is in the world around us conveys information to us.
-A sign of a women on a door conveys to most of us that this is a bathroom for women.
-The information graphs that OMDoc provides us with could also be simply visualized as a tree of information.
-But this would not be very engaging and it would be hard for a person to process.
-Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
-\\
-
-%In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door.
-We will rather focus on spatial narrative and placing content, that is inherently related, visually close together since this conveys the meaning that these objects belong together.\\
-
-%\begin{figure}[H]
-%        \centering
-%        \begin{subfigure}[b]{0.3\textwidth}
-%                \fbox{\includegraphics[width=\textwidth]{assets/size-of-objects}}
-%                \caption{Importance of Objects}
-%                \label{fig:imp_objects}
-%        \end{subfigure}%
-%        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-%          %(or a blank line to force the subfigure onto a new line)
-%        \begin{subfigure}[b]{0.3\textwidth}
-%                \fbox{\includegraphics[width=\textwidth]{assets/relation}}
-%                \caption{Relation of Objects}
-%                \label{fig:rel_objects}
-%        \end{subfigure}
-%        \caption{Conveying Visual Meaning}\label{fig:Objects}
-%\end{figure}
-
-%Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations.
-Figure \ref{fig:imp_objects} shows how size conveys importance.
-It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size.
-Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different.
-When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
-
-%These perceptions can be used to convey meaning visually.
-For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information.
-Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics.
-Similarly, we will employ visual relations as in figure \ref{fig:rel_objects} to show related content.
-Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts.
-Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger.
-Thus we will provide Annie with a meaningful representation of the information taken from the information graph.
-In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\
+\ednote{later on refer to this with the different levels.} \\
 
@@
 Building on the preliminaries, we will now commence the journey towards building a more effective presentation format.
-To begin with the creation of a tool, RPresentation \cite{npentrel:npentrel15}, for building these presentations automatically will be discussed.
-In the next section, we will then examine how this makes presentations more effective.
-
-\subsection{Creation of Ordered Information Graphs using OMDoc}
-\label{sec:wp2}
+To create these presentations automatically, the tool RPresentation \cite{npentrel:npentrel15} was created.\\
 
@@
 From this document we can then, in theory, seamlessly create slides both in PDF format as well as in XHTML format.
-Using a test document that is supposed to explain the pythagorean theorem and related topics, we can thus create an XML information graph out of the annotated documment.\\
+Using a test document that is supposed to explain the pythagorean theorem and related topics, the \sys tool can retrieve the the order of the slides as well as dependencies.
+This combined creates an information graph which we us to create a relational presentation out of the annotated document.\\
+
+\ednote{should this be longer?}
+
+\subsection{Narrative Paths}
+\label{sec:narrativePaths}
+
+The information graphs that OMDoc provides us with could also be simply visualized as a tree of information.
+But this would not be very engaging and it would be hard for a person to process.
+Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
+Therefore we will focus on using spatial narrative to make presentations more engaging and enhance knowledge transfer.\\
+
+One opportunity to employ spatial narrative is to place content which is inherently related visually close together since this conveys the meaning that these objects belong together.
+In \textit{A mathematical approach to ontology authoring and documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers".
+In our case, the content layers are the mathematical objects, i.e.
+the statements or theories.
+Narrative layers refer to the order the mathematical objects from content layers are presented.\\
+
+In our system \sys, we parse the \stex files to retrieve the traditional narrative the writer intended to use.
+This is the first narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation.
+To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}.
+This code creates \ednote{insert image of just the primary narrative path from example}.
+\\
+
+\begin{wrapfigure}{r}{\textwidth}
+\vspace{-26pt}
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+<div class="step" data-x="1250" data-y="0"> ... </div>
+<div class="step" data-x="2500" data-y="0"> ... </div>
+<div class="step" data-x="3750" data-y="0"> ... </div>
+<div class="step" data-x="5000" data-y="0"> ... </div>
+\end{minted}
+\vspace{-5pt}
+  \caption{Code Snippet for a Narrative Path}
+  \label{fig:narrativePathCode}
+  \vspace{12pt}
+\end{wrapfigure}
+
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+The primary narrative path is the traditional path a presenter normally uses when preparing a PowerPoint presentation.
+This path happens to also contain temporal information.
+This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\
+
+This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic.
+In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
+\ednote{use Annie example} In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
+These occur on different levels as explained in the next section \autoref{sec:levels}.\\
+
+\subsection{Levels}
+\label{sec:levels}
+
+When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included.
+These included files again include further tex-files etc..
+Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.\\
+
+\ednote{show inclusion graph and add an example to explain further}
+
+\subsection{Relational Information}
+\label{sec:relInfo}
+\ednote{needs work}
+
+The Local MathHub Tool (lmh) outputs information about dependencies of topics as shown below in \autoref{fig:reldatacode}. \\
 
@@
   \caption{Code Snippet of Relational Data}
-  \label{fig:SSlide}
+  \label{fig:reldatacode}
   \vspace{12pt}
@@
 
-\ednote{explain further}
+\ednote{add example}
 
-The system itself outputs information about dependencies of topics as shown above.
-Using the \sys tool I created for this research project, it is possible to get the order of the slides as well as dependencies.
+The system \sys parses the output and thus retrieves the dependencies of the topics.
+Combining this information with the order in which these pieces of information occur, i.e.
+with narrative paths and levels, we will be able to create ordered information graphs that allow users to interact with the presentation.
+
 The order of information in certain topics will be referred to as levels.
@@
 \ednote{add somewhere: By adding more levels of context we can allow viewers to understand the subject on a deeper level.}
+
+%Similarly, we will employ visual relations to show related content.
+
+\subsection{Ordered Information Graphs}
+\label{sec:orderedInfoGraphs}
 
@@
 
-\subsubsection{Narrative Paths}
-\subsubsection{Levels}
+\ednote{introduce information graphs}
 
-\subsection{Creating Relational Presentations}
-\label{sec:wp1}
+\ednote{structuring of the presentation - link with primitives and spatial narrative}
+
+\subsection{The Relational Presentations}
+\label{sec:RelationalPresentations}
+\ednote{needs work}
 
@@
 
+\ednote{note to self: status of information -> levels}
+
 \subsection{Technical Details}
@@
 
-\begin{enumerate}
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
 \item Get user input for the location and name of the folder
@@
 \section{Evaluation}
-\label{sec:evalcriteria}
+\label{sec:eval}
+\ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}
 
@@
 The evaluation conducted in the following part is on the one hand, systematic and, on the other hand, cognitive.
-Systematically, the knowledge presentation system \sys that was developed allows for the creation of a full relational presentation from a given annotated document which fulfills the goal of this project.
+Systematically, the knowledge presentation system \sys that was developed allows for the creation of a clearly structured relational presentation from a given annotated document which fulfills the goal of this project.
 It does so in a very timely manner.
@@
 
-%If \sys can create a clearly structured presentation from a given annotated document that provides a better knowledge transfer experience, this research will be a full success.
-If this should fail and we know why it did not or cannot work the research will have succeeded in exploring an interesting way of trying to improve knowledge transfer and will serve to show future researchers which other parameters need to be kept in mind in order to succeed in future.\\
-
-\ednote{ImpressJS had to be changed}
+\ednote{ImpressJS had to be adapted}
 
@@
 \newpage
-\section{References}
 

### 2015-05-08 Thesis.tex
second submission

@@
 These included files again include further tex-files etc..
-Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.\\
+Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.
+In essence, on any level the order of information in that topic is a narrative path.\\
 
@@
 
-\subsection{Relational Information}
-\label{sec:relInfo}
+\subsection{Ordered Information Graphs}
+\label{sec:orderedInfoGraphs}
 \ednote{needs work}
@@
 
-The order of information in certain topics will be referred to as levels.
-If we look at the pythagorean theorem and then realize we lack knowledge the concept of squares we could then read about that topic by going to that resource.
-From there on we are on a different \textit{level} which we can follow and dig deeper into until we understand squares.\\
+If we were to learn about the pythagorean theorem and then suddenly realized that we lack knowledge the concept of squares we could then learn about that topic by going to that resource.
+In other words, we check the dependencies of the pythagorean theorem, go that that level and follow the narrative path about squares until we understand squares.
+By adding a way to explore these other levels, the presentation adds more context and allows viewers to understand the subject on a deeper level.
+
 \ednote{draw the whole graph and add here}
-\ednote{add somewhere: By adding more levels of context we can allow viewers to understand the subject on a deeper level.}
 
@@
 
-\subsection{Ordered Information Graphs}
-\label{sec:orderedInfoGraphs}
+\ednote{add example in slides and explain the different layers again}
 
 \ednote {explain ids of slides}
-
-%narrative and mroe info
 
@@
 \ednote{structuring of the presentation - link with primitives and spatial narrative}
+
+\ednote{note to self: status of information -> levels}
 
@@
 \\
-
-\ednote{note to self: status of information -> levels}
 

### 2015-05-09 Thesis.tex
pre changes version

@@
 Normally we only have one path for a narration.
-That is true for books, movies, Facebook timelines, and also slide-based presentations.
+That is true for books, movies, Facebook timelines, and also traditional slide-based presentations.
 For three out of those four this has not changed in decades.
-With the advancement of technology, we are, however, able to change the way presentations and their narratives work.
-In essence we should be able to make it possible to link content that logically belongs together, in other words, content that is semantically close.
-Through that it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined path, but rather along the path that will allow the audience to make the most out of the presentation.\\
+With the advancement of technology, we are however able to change the way presentations and their narratives work.
+We can make it possible to link content that logically belongs together, in other words, content that is semantically close.
+Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined path, but rather along the path that will allow the audience to make the most out of the presentation.\\
 
@@
 Building on the preliminaries, we will now commence the journey towards building a more effective presentation format.
-To create these presentations automatically, the tool RPresentation \cite{npentrel:npentrel15} was created.\\
+To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.
+The implementation details of \sys will be discussed in \ref{sec:implementation}\\
 
@@
 Using a test document that is supposed to explain the pythagorean theorem and related topics, the \sys tool can retrieve the the order of the slides as well as dependencies.
-This combined creates an information graph which we us to create a relational presentation out of the annotated document.\\
-
-\ednote{should this be longer?}
+The order of the slides and their dependencies combined lead to an information graph which we then use to create a relational presentation out of the annotated document.\\
 
@@
 To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}.
-This code creates \ednote{insert image of just the primary narrative path from example}.
-\\
+This code snippet creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\
 
@@
 
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-20pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}
+    }
+  \end{center}
+\vspace{-16pt}
+  \caption{Primary Narrative Path}
+  \label{fig:primaryNarrativePath}
+\vspace{12pt}
+\end{wrapfigure}
+
 \begin{wrapfigure}{l}{\textwidth}
@@
 The primary narrative path is the traditional path a presenter normally uses when preparing a PowerPoint presentation.
-This path happens to also contain temporal information.
+This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
 This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\
@@
 In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
-\ednote{use Annie example} In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
+Going back to our example of Annie, an example of a subsection would be the information concerning angles.
+In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
 These occur on different levels as explained in the next section \autoref{sec:levels}.\\
@@
 
-\ednote{show inclusion graph and add an example to explain further}
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
+    } 
+\vspace{-5pt}
+  \caption{Inclusion Graph for the Pythagorean Theorem}
+  \label{fig:inclusionGraph}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+The graph for CS looks more like this:
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.3\textwidth]{assets/final/inclusionGraphCS}
+    } 
+\vspace{-5pt}
+  \caption{Inclusion Graph for Gen CS}
+  \label{fig:inclusionGraph}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+sda
 
@@
 \ednote{add example}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/depGraphPythagorean}
+    } 
+\vspace{-5pt}
+  \caption{Dependency Graph}
+  \label{fig:depGraphPythagorean}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
 
@@
 \ednote{needs work}
+
+\begin{wrapfigure}{c}{0.97\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
+    } 
+\vspace{-5pt}
+  \caption{Presentation Overview}
+  \label{fig:fullPresentation}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
 
@@
 
+\ednote{show possible paths thru presentation}
+
 \subsection{Technical Details}
-\label{sec:wp4}
+\label{sec:implementation}
+
+\ednote{this is relatively shallow, about the implementation we only get to know that it is in Java.
+An architecture diagram would be helpful, and if you have that, you can explain it.
+That will give you something to guide the level of presentation.}
+
+\ednote{where to put the screenshot hack?}
 
@@
 
-\ednote{lmh not working :(}
-
 \ednote{ImpressJS had to be adapted}
@@
 \section{Future Work and Possible Extensions}
+
+\ednote{think of more extensions when you write up the rest}
 

### 2015-05-09 Thesis.tex
OMG I LIKE MY INTRO

@@
 \label{sec:introduction}
-\ednote{shorten}
 
-Normally we only have one path for a narration.
-That is true for books, movies, Facebook timelines, and also traditional slide-based presentations.
+\begin{wrapfigure}{l}{0.4\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.38 \textwidth]{assets/final/mountain}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Learning Path}
+  \label{fig:mountain}
+\vspace{-10pt}
+\end{wrapfigure}
+
+Learning new things is a bit like hiking up a mountain.
+If you have ever gone hiking you know that it's relatively hard to hike up a steep mountain directly as shown in AUTOREF.
+Some people do it but most people will rather hike up as shown in AUTOREF.
+Both paths lead to the goal.
+When we look at education, we normally only have one path.
+That is true for the narration in books, movies, Facebook timelines, and also traditional slide-based presentations.
 For three out of those four this has not changed in decades.
@@
 We can make it possible to link content that logically belongs together, in other words, content that is semantically close.
-Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined path, but rather along the path that will allow the audience to make the most out of the presentation.\\
+Through the linking of content it can become possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that will allow the audience to take small detours and ultimately make the most out of the presentation.\\
 
@@
 When Tim Berners-Lee laid out his Semantic Web Roadmap \cite{BernersLee:tsw98}, its intention was to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
-Both strive to connect pieces of information through adding context and thus to not just provide information, but rather knowledge.
-Within presentations, the intention is to present information in a more interconnected way that provides context and thus facilitates understanding and learning.
-\\
+Both the semantic web and the research at hand strive to connect pieces of information through adding context and thus to not just provide information, but rather knowledge.
+Within presentations, the intention is to present information in a more interconnected way that provides context and thus facilitates understanding and learning.\\
 
-\ednote{how relevant?}
-The concept behind the semantic web and changing presentations is quite similar.
-Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content.
-While this led to a lot of information on the web, it provided comparatively little knowledge.
-Here the processing of information to provide knowledge is lacking.
-Similarly, the existence of tools like Powerpoint have lead to virtually everyone creating presentations in this format.
-As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but often lack structure and context.\\
-
-In essence, both issues stem from information being generated without enough context or structure.
-This makes the information hard to process by humans and/or machines.
-The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.\\
-
-The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information.
-It adapts some of the concepts of the semantic web on a smaller scale and connects information logically.
-The end product should be a system that creates presentations which allow users to choose their own narrative path where users can seamlessly look at related topics and brush up on half-forgotten topics.\\
-
-\begin{figure}[H]
-        \centering
-                \fbox{\includegraphics[width=0.8\textwidth]{assets/model2}}
-                \caption{From Data to Knowledge}
-                \label{fig:dataknow}
-\end{figure}
-
-One can define knowledge as "the information necessary to support intelligent reasoning" \cite{Kohlhase:Complog:base}.
-That said, it is imperative to facilitate knowledge transfer.
-Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information.
-From information, we can then obtain knowledge through adding networking.\\
-
-We want to go from merely displaying information to allowing users to interact with information and choosing a learning path that suits them individually.
-The concept of information existing in networks and relatedness of information will be used to display not just the prescribed presentation path but also allow the user to deviate from the path to go back to topics that form the preliminary knowledge base for the current topic.
-Specifically this research examines whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\
-
-To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks).
-For this we will be using the OMDoc (Open Mathematical Documents) format which, given an annotated set of documents, will provide us with the necessary HTML-representation of the information.
-This will also allow us to extract information about the semantic closeness of different pieces of information.
-Taking this as a starting point, we will visualize the dependencies of the information contained in these documents.
-We will visualize the dependencies in a simple but effective approach with basic elements of spatial narrative using the presentation framework impress.js.
-The final product will allow for an interactive way of viewing a presentation.\\
-
-\ednote{readd slide images}
-To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure %\ref{fig:Annie-presentation-teacher}
-).
-She is given a triangle with sides a = 3 cm and b = 4 cm.
+Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem.
+She is then given a triangle with sides a = 3 cm and b = 4 cm.
 Now she wants to use the theorem to calculate the length of side c.
@@
 Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle.
-Now Annie has to try to find out what a right triangle is.
-This shows the dependencies of different pieces of information (see figure %\ref{fig:Annie-presentation-information}
-), i.e.
-the Pythagorean theorem depends on knowledge of squares, triangles, lengths, area calculation, and right angles.
-In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\
+Now Annie has to try to find out what a right triangle is.\\
 
-After this contrived story, it is left to the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time.
-There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole.
+\begin{wrapfigure}{r}{0.4\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.38 \textwidth]{assets/final/PythDep}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Information Dependency of the Pythagorean Theorem}
+  \label{fig:Pythdep}
+\vspace{-10pt}
+\end{wrapfigure}
+
+Annie's example shows the dependencies of different pieces of information (see \autoref{fig:Pythdep}), i.e.
+the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles.
+As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up.
+By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the pythagorean theorem.\\
+
+To achieve our goal to help Annie, we will set out to create a relational presentation system \sys to visually present information and its context which allows Annie to interact with the content and choose a path that matches her knowledge base.
+For this we will be using the OMDoc (Open Mathematical Documents) format which, given an annotated set of documents, will provide us with the necessary HTML-representation and PDF-representation of the information.
+It will also allow us to extract information about the semantic closeness of different pieces of information.\\
+
+This information alone would tell Annie where she might find the information she seeks but we will only use this as a starting point.
+We will use this information to visualize the dependencies of the information in a simple but effective approach using the presentation framework impress.js.
+The visualization of the information will make use of spatial narrative to connect information in a logical way.
+Thus the final product will allow Annie to intuitively interact with the presentation to find the information she needs.\\
+
+Along the way of helping Annie, we will explore the question how to allow users to go through flexible presentations where they can choose their own paths to explore the context of a topic as needed by browsing through related resources seamlessly.
+Specifically this research examines how spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer by providing the flexibility in a presentation to choose a path that fits.\\
+
+Overall, this work will showcase a tool for automatic contextual visualization of information through the usage of both spatial narrative and semantic closeness of information thus connecting information logically.
+The end product should be a system that creates presentations which allow users to choose their own narrative path by interacting with the presentation such that they can seamlessly explore related topics and brush up on half-forgotten topics.\\
+
+It is left to the reader to think about examples in his or her own life where he or she would have appreciated having these type of flexible presentations.
+There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal.
 \\
-
-%\section{Research Questions}
-
-%As we have pointed out in \autoref{sec:introduction}, presenting information in an effective way is essential to foster learning. This research will answer the following basic questions:
-
-%\begin{itemize}
-%\item How can we combine spatial narrative and semantic closeness of information to improve the presentation of information?
-%\item Which ways of visualizing information dependencies are there?
-%\end{itemize}
 
@@
 
+\ednote{not just prerequisite knowledge but also knowledge that builds on the current topic - bored students can thus already learn more!}
+
+machine learning to make smart offers of knowledge.
+
+learn what the user knows and what the user doesnt. - we dont always want to show how to do multiplication
+
 \section{Conclusion}
 \label{sec:conclusion}
-
+Spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.\\
 %The proposed research will evaluate if and how spatial narrative can be combined with semantic closeness to form visual presentations that will facilitate knowledge transfer.

### 2015-05-09 Thesis.tex
1+2 done

@@
 Both paths lead to the goal.
-When we look at education, we normally only have one path.
+When we look at education, we normally only have one straight path.
 That is true for the narration in books, movies, Facebook timelines, and also traditional slide-based presentations.
@@
 
-Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem.
+\begin{wrapfigure}{l}{0.5\textwidth}
+\vspace{-28pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.48 \textwidth]{assets/final/slide_theorem}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Theorem Slide}
+  \label{fig:slideP}
+\vspace{-10pt}
+\end{wrapfigure}
+
+Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem \autoref{fig:slideP}.
 She is then given a triangle with sides a = 3 cm and b = 4 cm.
@@
 It is left to the reader to think about examples in his or her own life where he or she would have appreciated having these type of flexible presentations.
-There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal.
+There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal (see AUTOREF).
 \\
@@
 This creates guided tours on topics depending on the background of the user.
-While following the same ideal to improve knowledge transfer, it differs from this work in the fact that its presentation format is completely different.
+While following the same ideal to improve knowledge transfer, it differs from this work in its presentation format.
 While Siekmann et al., focused on one topic and displaying it differently to users with different backgrounds, this research will show the topics of a whole course while allowing to see dependencies and while allowing to diverge from the prescribed presentation path.\\
@@
 It demonstrates the need for assistance in form of navigation support for the reading of mathematical documents by creating a system that allows for semantic navigation in Excel spreadsheets.
-This research underlines the importance of a system that allows users to navigate information according to dependencies.\\
+This research underlines the importance of a system that allows users like Annie to navigate information according to dependencies.\\
 
@@
 
-In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how Annie's teacher can transfer knowledge more effectively.\\
+In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how the presentation can be improved to transfer knowledge more effectively.\\
 
@@
 The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
-Recalling figure %\ref{fig:PythagoreanTheorem}
-\ednote{readd figures}
- and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
+Recalling \autoref{fig:slideP} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
 For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".

### 2015-05-09 Thesis.tex
3.3 done

@@
 \usepackage{tocloft}
-
+\renewcommand*{\figureautorefname}{figure}
 \def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
@@
   \caption{Information Dependency of the Pythagorean Theorem}
-  \label{fig:Pythdep}
+  \label{fig:deppyg}
 \vspace{-10pt}
@@
 We will define it as knowledge that is made up out of several pieces of information that are connected.
-In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see figure %\ref{fig:Annie-presentation-information}
- ).\\
+In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \autoref{fig:deppyg}).\\
 
@@
 Without this \textit{context}, Annie cannot understand the theorem.
-Figure \ref{fig:Annie-context} illustrates the context by showing the dependencies of the theorem, i.e.
+Figure \ref{fig:deppyg} illustrates the context by showing the dependencies of the theorem, i.e.
 calculating squares, area calculation, triangles, and right angles.
-It semiotically represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}.
+It represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}.
 We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\
@@
 The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations.
-This elevates the net of separate pieces of information that are stored individually to a semantic representation and one step further to knowledge.\\
+This elevates the net of separate pieces of information that are stored individually to a semantic representation and can be used to improve knowledge transfer.\\
 
@@
 These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
-In general we will call the information that the speaker is sharing with the addressees/students \textit{course-new}.
+In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}.
 Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
@@
 The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
-This is marked orange in figure \ref{fig:Annie-ancient}.
 The information about squares which Annie still remembers is \textit{course-old}.
-Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
-\ednote{later on refer to this with the different levels.} \\
+Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.\\
 
@@
 \label{sec:levels}
+
+\ednote{Refer back to status of information within ... later on refer to this with the different levels.}
 

### 2015-05-09 Thesis.tex
done with 1,2,3

@@
 In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate.
-Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}).
+Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to \autoref{fig:deppyg}).
 These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
@@
 
-These relations or connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
-As such the temporal associations show the path that a normal lecture would take.
-The dependencies that are visualized around each frame allow for additional interactiveness.\\
+These relations or connections between different slides do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
+As such the temporal associations show the path that a traditional lecture would take.
+The dependencies that are visualized around each slide, mainly above or below the slide, allow for additional interactiveness.\\
 
@@
 
+\begin{wrapfigure}{r}{0.5\textwidth}
+\vspace{-24pt}
+  \begin{center}
+  \fbox{
+    \includegraphics[width=0.48 \textwidth]{assets/final/arrowsPyth}
+    }
+  \end{center}
+\vspace{-20pt}
+  \caption{Connection of Slide}
+  \label{fig:arrowspyg}
+\vspace{-10pt}
+\end{wrapfigure}
+
 In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
-For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:Annie-guided}).
+For Annie this means that she will be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
 It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\
@@
 
-For the implementation of \sys, we chose to use impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
+For the implementation of \sys, impress.js will be used, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
 The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's.
@@
 \ednote{needs work}
+\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}
 

### 2015-05-09 Thesis.tex
added mountain pics

@@
 
-\begin{wrapfigure}{l}{0.4\textwidth}
-\vspace{-26pt}
+\begin{wrapfigure}{r}{0.3\textwidth}
+\vspace{-28pt}
   \begin{center}
   \fbox{
-    \includegraphics[width=0.38 \textwidth]{assets/final/mountain}
+    \includegraphics[width=0.28 \textwidth]{assets/final/straightMountain}
     }
+\vspace{-20pt}
+  \caption{Straight Learning Path}
+  \label{fig:straight}
+\vspace{5pt}  
+      \fbox{
+    \includegraphics[width=0.28 \textwidth]{assets/final/curvyMountain}
+    }
+
   \end{center}
 \vspace{-20pt}
-  \caption{Learning Path}
-  \label{fig:mountain}
+  \caption{Curvy Learning Path}
+  \label{fig:curvy}
 \vspace{-10pt}
@@
 Learning new things is a bit like hiking up a mountain.
-If you have ever gone hiking you know that it's relatively hard to hike up a steep mountain directly as shown in AUTOREF.
-Some people do it but most people will rather hike up as shown in AUTOREF.
+If you have ever gone hiking you know that it is relatively hard to hike up a steep mountain directly as shown in \autoref{fig:straight}.
+Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}.
 Both paths lead to the goal.
@@
 Both the semantic web and the research at hand strive to connect pieces of information through adding context and thus to not just provide information, but rather knowledge.
-Within presentations, the intention is to present information in a more interconnected way that provides context and thus facilitates understanding and learning.\\
+Within presentations, the intention is to present information in an interconnected way that provides context and thus facilitates understanding and learning.\\
 
-\begin{wrapfigure}{l}{0.5\textwidth}
+\begin{wrapfigure}{l}{0.45\textwidth}
 \vspace{-28pt}
@@
   \fbox{
-    \includegraphics[width=0.48 \textwidth]{assets/final/slide_theorem}
+    \includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}
     }
@@
   \label{fig:slideP}
-\vspace{-10pt}
+\vspace{-15pt}
 \end{wrapfigure}
@@
 
-Annie's example shows the dependencies of different pieces of information (see \autoref{fig:Pythdep}), i.e.
+Annie's example shows the dependencies of different pieces of information (see \autoref{fig:PythDep}), i.e.
 the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles.
@@
 It is left to the reader to think about examples in his or her own life where he or she would have appreciated having these type of flexible presentations.
-There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal (see AUTOREF).
-\\
+There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be straight or curvy.\\
 

### 2015-05-09 Thesis.tex
4.0 done

@@
 \begin{wrapfigure}{r}{0.4\textwidth}
-\vspace{-26pt}
+\vspace{-28pt}
   \begin{center}
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-\vspace{-24pt}
+\begin{wrapfigure}{r}{0.45\textwidth}
+\vspace{-28pt}
   \begin{center}
   \fbox{
-    \includegraphics[width=0.48 \textwidth]{assets/final/arrowsPyth}
+    \includegraphics[width=0.43 \textwidth]{assets/final/arrowsPyth}
     }
@@
 \label{sec:TowardsAMoreEffectivePresentationFormat}
+\ednote{is relatively shallow, about the implementation we only get to know that it is in Java.
+An architecture diagram would be helpful, and if you have that, you can explain it.
+That will give you something to guide the level of presentation.}
 
-Building on the preliminaries, we will now commence the journey towards building a more effective presentation format.
-To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.
-The implementation details of \sys will be discussed in \ref{sec:implementation}\\
+\ednote{screenshot hack?}
+
+Building on the preliminaries, we will now commence the journey towards building a more effective presentation format to improve knowledge transfer by allowing flexibility in presentations.
+To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.\\
+
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.87\textwidth]{assets/final/Architecture}
+    } 
+\vspace{-5pt}
+  \caption{Architecture Diagram}
+  \label{fig:architecture}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
 
 With the OMDoc framework and its tools it is possible to write down course notes or other documents in \stex.
-From this document we can then, in theory, seamlessly create slides both in PDF format as well as in XHTML format.
-Using a test document that is supposed to explain the pythagorean theorem and related topics, the \sys tool can retrieve the the order of the slides as well as dependencies.
-The order of the slides and their dependencies combined lead to an information graph which we then use to create a relational presentation out of the annotated document.\\
+The Local MathHub Tool (lmh) uses these to create, among other things, PDF slides, XHTML slides, and relational information.
+To help Annie, let us use a document that explains the pythagorean theorem and related topics.
+The files that lmh creates, along with the \stex -files will be used as input in the next steps.
+For the implementation of  \sys Java was used.
+It would have been possible to choose other programming languages, however, using Java, we end up with platform-independent code.\\
+
+\sys itself operates in five main steps:\\
+\vspace{-12pt}
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item Get user input for the location and names of folders.
+\item Parse \sTeX to retrieve the order of slides.
+\item Extract dependencies from relationanl info.
+\item Extract necessary XHTML or PDF parts for slides.
+\item Create presentation.
+\end{enumerate}
+\vspace{5pt}
+
+After asking the user for the location and names of the folders we want to work on, \sys can parse the provided \stex files in a recursive fashion to retrieve the slide order.
+It does this by starting with a given top level file which includes other files via \textit{mhinputref}s.\\
+
+In the next step the relational information is parsed and transformed into a hashtable.
+The keys are the slides which link to an array of dependent slides.
+The order of the slides and their dependencies are then combined to an information graph which we use to create a relational presentation out of the annotated document using the slide info.
+This slide information is created by either parsing the XHTML and directly copying the needed parts into the final presentation or by transforming the PDF into PNGs that are then included in the final presentation.\\
+
+For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added.
+The exact details of this process will be explained in more detail in sections \ref{sec:narrativePaths}, \ref{sec:levels}, \ref{sec:orderedInfoGraphs}, and \ref{sec:RelationalPresentations}.
+\ednote{check}\\
+
+To bring the presentation to life the framework impress.js which was introduced in \autoref{sec:Impressjs} was used because it easy to reuse the XHTML code that was automatically generated by lmh.
+An important additional reason for the choice of impress.js is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and \autoref{sec:Impressjs}.
+Due to the choice of impress.js \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
+impress.js works in all modern browsers that support CSS 3D transforms.\\
 
@@
 
-\subsection{Technical Details}
-\label{sec:implementation}
-
-\ednote{this is relatively shallow, about the implementation we only get to know that it is in Java.
-An architecture diagram would be helpful, and if you have that, you can explain it.
-That will give you something to guide the level of presentation.}
-
-\ednote{where to put the screenshot hack?}
-
-To implement \sys we rely on the Local MathHub Tool (lmh) which creates our input data.
-As input data we take, the \sTeX files of the document, the information about dependencies, and the XHTML of the slides.
-We use this information in several steps in our system \sys:
-
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item Get user input for the location and name of the folder
-\item Parsing \sTeX to retrieve the order of information
-\item Extracting relational information from \ednote{ref}
-\item Extracting necessary HTML parts
-\item Creation of presentation
-\end{enumerate}
-
-For the implementation of  \sys Java was used. It would have been possible to choose other programming languages, however, using Java, we end up with platform-independent code.\\
-
-In the last step, where the presentation is created, we use self-created boilerplate code, in which only some coordinates and the HTML for the slide is added.
-For the presentation impress.js was chosen such that the HTML code, automatically generated by lmh, can be reused.
-An important additional reason for the choice of impress.js is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and and \autoref{sec:Impressjs}.\\
-
-Due to the choice of impress.js \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
-mpress.js works in all modern browsers that support CSS 3D transforms.
-
 \section{Evaluation}

### 2015-05-10 Thesis.tex
much added to 4

@@
 \label{sec:TowardsAMoreEffectivePresentationFormat}
-\ednote{is relatively shallow, about the implementation we only get to know that it is in Java.
-An architecture diagram would be helpful, and if you have that, you can explain it.
-That will give you something to guide the level of presentation.}
-
 \ednote{screenshot hack?}
@@
 \item Parse \sTeX to retrieve the order of slides.
-\item Extract dependencies from relationanl info.
+\item Extract dependencies from relational info.
 \item Extract necessary XHTML or PDF parts for slides.
@@
 For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added.
-The exact details of this process will be explained in more detail in sections \ref{sec:narrativePaths}, \ref{sec:levels}, \ref{sec:orderedInfoGraphs}, and \ref{sec:RelationalPresentations}.
-\ednote{check}\\
+The exact details of this process will be explained in more detail in subsection \ref{sec:RelationalPresentations}.
+To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo.
+The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}.
+\ednote{check subsections}\\
 
@@
 
-The information graphs that OMDoc provides us with could also be simply visualized as a tree of information.
+The information that OMDoc provides us with could also be simply visualized as a tree of information.
 But this would not be very engaging and it would be hard for a person to process.
@@
 
-In our system \sys, we parse the \stex files to retrieve the traditional narrative the writer intended to use.
-This is the first narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation.
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
+    } 
+\vspace{-16pt}
+  \caption{Inclusion Graph for the Pythagorean Theorem}
+  \label{fig:inclusionGraph}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{l}{0.3\textwidth}
+\vspace{-12pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.28\textwidth]{assets/final/inclusionGraphCS}
+    } 
+\vspace{-16pt}
+  \caption{Inclusion Graph for GenCS}
+  \label{fig:inclusionGraphGenCS}
+\vspace{-24pt}
+  \end{center}
+\end{wrapfigure}
+
+In our system \sys, we parse the \stex files using a Depth First Search algorithm to retrieve the traditional narrative the writer intended to use.
+For the explanation of the pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}.
+The graph for a whole course like the General Computer Science course (GenCS) at Jacobs University Bremen \cite{Kohlhase:GenCSII:base} is too big to be shown properly (see \autoref{fig:inclusionGraphGenCS}).\\
+
+The retrieved order is the intended narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation.
 To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}.
@@
 
-The primary narrative path is the traditional path a presenter normally uses when preparing a PowerPoint presentation.
+The primary narrative path, formed by a horizontal stream of slides, is the traditional path a presenter normally uses when preparing a PowerPoint presentation.
 This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
@@
 
+\ednote{how to add a slide!}
+by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file.
+Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}.
+\ednote{add picture of this}\\
+
 \subsection{Levels}
 \label{sec:levels}
-
-\ednote{Refer back to status of information within ... later on refer to this with the different levels.}
 
@@
 Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.
-In essence, on any level the order of information in that topic is a narrative path.\\
+In essence, on any level the order of information in that topic is a narrative path.
+In mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
+From these levels we can infer the status of the information.
+Anything that is on the same level or in the sublevels thereof is generally considered to be \textit{course-old} information.\\
 
@@
   \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
+      \includegraphics[width=0.97\textwidth]{assets/final/levels}
     } 
 \vspace{-5pt}
-  \caption{Inclusion Graph for the Pythagorean Theorem}
-  \label{fig:inclusionGraph}
+  \caption{Inclusion Graph with Levels}
+  \label{fig:levelsGraph}
 \vspace{12pt}
@@
 
-The graph for CS looks more like this:
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.3\textwidth]{assets/final/inclusionGraphCS}
-    } 
-\vspace{-5pt}
-  \caption{Inclusion Graph for Gen CS}
-  \label{fig:inclusionGraph}
-\vspace{12pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-sda
+With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation.
+It does this incrementally.
+As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides.
+After adding each slide it checks whether there is \textit{course-ancient} information, i.e.
+whether there are dependencies, for that slide.
+If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).
+This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value.
+\ednote{code snippet}\\
 
@@
 \label{sec:orderedInfoGraphs}
-\ednote{needs work}
 
-The Local MathHub Tool (lmh) outputs information about dependencies of topics as shown below in \autoref{fig:reldatacode}. \\
+As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.
+The general format of one relation can be seen in \autoref{fig:reldatacode} (lines 1-2).
+A specific example showing some of the dependencies for the pythagorean theorem example can be seen in lines 4-11.\\
 
@@
 Includes path/to/file path/to/dependent/file?theory_name
+
+theory 
+pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
+Includes 
+pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
+pythagoreantheorem/measurements/right_angle.omdoc?right_angle
+Includes 
+pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
+pythagoreantheorem/measurements/area.omdoc?angle
 \end{minted}
 \vspace{-5pt}
-  \caption{Code Snippet of Relational Data}
+  \caption[Caption for LOF]{Code Snippet of Relational Data \footnotemark}
   \label{fig:reldatacode}
@@
 
-\ednote{add example}
+\footnotetext{All the above paths were shortened by "http://mathhub.info/MiKoMH/" to maintain readability.}
+
+The system \sys parses the relational data and thus retrieves the dependencies of the topics.
+We already know that the level a piece of information is associated with infers that it is \textit{course-old} information.
+Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information that happened more time ago.\\
 
@@
 
-The system \sys parses the output and thus retrieves the dependencies of the topics.
 Combining this information with the order in which these pieces of information occur, i.e.
-with narrative paths and levels, we will be able to create ordered information graphs that allow users to interact with the presentation.
+with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem.
+We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo}
+    } 
+\vspace{-5pt}
+  \caption{Dependency Graph}
+  \label{fig:depGraphPythagoreanFull}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+\subsection{The Relational Presentation}
+\label{sec:RelationalPresentations}
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.47\textwidth]{assets/final/VisualDependency}
+    } 
+\vspace{-5pt}
+  \caption{Visualization of Dependencies}
+  \label{fig:visualDependency}
+\vspace{-24pt}
+  \end{center}
+\end{wrapfigure}
+
+If they, while browsing through these different levels, realize that they need to refresh their memory or learn more about any of the dependent information they can enter that level.
+The presentation will then continue on that level and give all the slides from that topic in the correct order.
+Once the user has gone through this short excursion, he or she can return to the initial slide and resume the normal narrative path.
+These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
+Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\
+
+\ednote{meaning of moving right and down.}
+\ednote {path of going through the slides - identify didactic things!!}
+\ednote{show possible paths thru presentation}
+\ednote{structuring of the presentation - link with primitives and spatial narrative}
+\ednote{add example in slides and explain the different levels again}
+\ednote {explain ids of slides}
+\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}
+
+%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
+
+%into an interactive presentation.
+
+% Layout
+%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
+Ideally the added expressiveness that impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
+\\
+
+% for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
+Knowing the dependencies and the status of the information will allow us to choose which information to show the user in the close surroundings of the current information we are showing.\\
+
+%Similarly, we will employ visual relations to show related content.
 
@@
 By adding a way to explore these other levels, the presentation adds more context and allows viewers to understand the subject on a deeper level.
-
-\ednote{draw the whole graph and add here}
-
-%Similarly, we will employ visual relations to show related content.
-
-\ednote{add example in slides and explain the different layers again}
-
-\ednote {explain ids of slides}
-
-% for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
-Knowing the dependencies and the status of the information will allow us to choose which information to show the user in the close surroundings of the current information we are showing.\\
-
-\ednote{introduce information graphs}
-
-\ednote{structuring of the presentation - link with primitives and spatial narrative}
-
-\ednote{note to self: status of information -> levels}
-
-\subsection{The Relational Presentations}
-\label{sec:RelationalPresentations}
-\ednote{needs work}
-\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}
 
@@
 
-With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file.
-Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}.
-The primary narrative that the presenter wants to follow is formed by a horizontal stream of slides.
-\ednote{add picture of this}\\
-
-This horizontal stream of slides is achieved by giving the slides incremental \texttt{data-x} values in the attributes.
-If a slide has dependencies then these will be added as slides below the slide itself.
-This, in turn, is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value.
-Thus users can now simply press down and explore all the dependent information.\\
-
-If they, while browsing through these different levels, realize that they need to refresh their memory or learn more about any of the dependent information they can enter that level.
-The presentation will then continue on that level and give all the slides from that topic in the correct order.
-Once the user has gone through this short excursion, he or she can return to the initial slide and resume the normal narrative path.
-These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
-Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\
-
-%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
-Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation.
-In this step we will define several models of how data is presented within a frame.
-Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}).
-Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within impress.js.\\
-
-%Once we have an ordered information graph with all the additional attribute values mentioned in section \ref{sec:wp2}, we will create the knowledge presentation system \sys.
-\sys will visualize the information from the graph including all the attributes we added.
-The outcome of this part should be a general \sys presentation model, that implements the models according to the models chosen in section \ref{sec:wp1}.
-We will then use \sys to visualize information in WP4.\\
-
-% Layout
-%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
-Ideally the added expressiveness that impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
-\\
-
-\ednote{show possible paths thru presentation}
-
 \section{Evaluation}
@@
 Afterwards we will briefly look at future work and possible extensions to our system.
-
-\subsection{General Evaluation}
 
@@
 %Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.\\
-
-\subsection{Shortcomings and Problems with the System}
 

### 2015-05-10 Thesis.tex
4.1-2 done

@@
 
-For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added.
-The exact details of this process will be explained in more detail in subsection \ref{sec:RelationalPresentations}.
+For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added (see \autoref{sec:Impressjs}).
+The details of this process will be explained in subsection \ref{sec:narrativePaths}, \ref{sec:orderedInfoGraphs}, and \ref{sec:levels}.
 To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo.
-The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}.
-\ednote{check subsections}\\
+The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}.\\
 
@@
 
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-80pt}
+\end{wrapfigure}
+
+\newpage
+
 \begin{wrapfigure}{l}{0.3\textwidth}
-\vspace{-12pt}
+\vspace{-28pt}
   \begin{center}
@@
 In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
-These occur on different levels as explained in the next section \autoref{sec:levels}.\\
-
-\ednote{how to add a slide!}
-by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file.
-Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}.
-\ednote{add picture of this}\\
-
-\subsection{Levels}
-\label{sec:levels}
-
-When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included.
-These included files again include further tex-files etc..
-Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.
-In essence, on any level the order of information in that topic is a narrative path.
-In mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
-From these levels we can infer the status of the information.
-Anything that is on the same level or in the sublevels thereof is generally considered to be \textit{course-old} information.\\
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/levels}
-    } 
-\vspace{-5pt}
-  \caption{Inclusion Graph with Levels}
-  \label{fig:levelsGraph}
-\vspace{12pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-
-With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation.
-It does this incrementally.
-As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides.
-After adding each slide it checks whether there is \textit{course-ancient} information, i.e.
-whether there are dependencies, for that slide.
-If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).
-This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value.
-\ednote{code snippet}\\
+These occur on different levels as explained in \autoref{sec:levels}.\\
 
@@
 The system \sys parses the relational data and thus retrieves the dependencies of the topics.
-We already know that the level a piece of information is associated with infers that it is \textit{course-old} information.
+We already know that the level a piece of information is associated with infers that it is \textit{course-old} information \ednote{change order}.
 Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information that happened more time ago.\\
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/depGraphPythagorean}
-    } 
-\vspace{-5pt}
-  \caption{Dependency Graph}
-  \label{fig:depGraphPythagorean}
-\vspace{12pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-
-Combining this information with the order in which these pieces of information occur, i.e.
-with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem.
-We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.
 
@@
 
-\subsection{The Relational Presentation}
-\label{sec:RelationalPresentations}
+With the information about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the pythagorean theorem.
+\sys creates this presentation incrementally.
+As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides.
+After adding each slide it checks whether there is \textit{course-ancient} information, i.e.
+whether there are dependencies, for that slide.
+If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).
+This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value (see \autoref{fig:dependencySnippet}).\\
 
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{wrapfigure}{r}{\textwidth}
+\vspace{-26pt}
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+<div class="step slide" data-x="8750" data-y="0"> Slide </div>
+<div class="step slide" data-x="8750" data-y="800"> Dependency 1 </div>
+<div class="step slide" data-x="8750" data-y="1600"> Dependency 2 </div>
+\end{minted}
+\vspace{-5pt}
+  \caption{Code Snippet for a Dependency}
+  \label{fig:dependencySnippet}
+  \vspace{12pt}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{1\textwidth}
 \vspace{-26pt}
@@
   \fbox{
-      \includegraphics[width=0.47\textwidth]{assets/final/VisualDependency}
+      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
     } 
@@
 
-If they, while browsing through these different levels, realize that they need to refresh their memory or learn more about any of the dependent information they can enter that level.
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+\subsection{Levels}
+\label{sec:levels}
+
+When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included.
+These included files again include further tex-files etc..
+Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.
+In essence, on any level the order of information in that topic is a narrative path.
+In mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
+From these levels we can infer the status of the information.
+Anything that is on the same level or in the sublevels thereof is generally considered to be \textit{course-old} information.\\
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/levels}
+    } 
+\vspace{-5pt}
+  \caption{Inclusion Graph with Levels}
+  \label{fig:levelsGraph}
+\vspace{12pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter that level.
 The presentation will then continue on that level and give all the slides from that topic in the correct order.
-Once the user has gone through this short excursion, he or she can return to the initial slide and resume the normal narrative path.
+Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path.
 These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
@@
 
-\ednote{meaning of moving right and down.}
+\begin{wrapfigure}{r}{\textwidth}
+\vspace{-26pt}
+\begin{minted}[linenos=true, bgcolor=bg]{C}
+<div class="step slide" data-x="8750" data-y="0" data-z="0" data-rotate-y="0"> Slide </div>
+<div class="step slide" data-x="8750" data-y="800" data-z="0" data-rotate-y="0"> Dependency 1 </div>
+<div class="step slide" data-x="8750" data-y="1600" data-z="0" data-rotate-y="0"> Dependency 2 </div>
+\end{minted}
+\vspace{-5pt}
+  \caption{Code Snippet for a Dependency}
+  \label{fig:dependencySnippet}
+  \vspace{12pt}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{1\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
+    } 
+\vspace{-5pt}
+  \caption{Visualization of Dependencies}
+  \label{fig:visualDependency}
+\vspace{-24pt}
+  \end{center}
+\end{wrapfigure}
+
+\begin{wrapfigure}{c}{\textwidth}
+\vspace{-50pt}
+\end{wrapfigure}
+
+\ednote {change image}
+
+%Combining this information with the order in which these pieces of information occur, i.e.
+with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem.
+We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.
+
+\subsection{The Relational Presentation}
+\label{sec:RelationalPresentations}
+
+\ednote{meaning of moving right and down, rotation.}
 \ednote {path of going through the slides - identify didactic things!!}

### 2015-05-10 Thesis.tex
Draft for Meike

@@
 Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path.
-These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
+By adding a way to explore these other levels, the presentation adds more context and allows Annie to understand the subject on a deeper level.
+These modular excursions are included in the presentation in 3D by making use of CSS3-transitions (see \autoref{fig:dependencyLevelSnippet}).
 Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\
@@
 \begin{minted}[linenos=true, bgcolor=bg]{C}
-<div class="step slide" data-x="8750" data-y="0" data-z="0" data-rotate-y="0"> Slide </div>
-<div class="step slide" data-x="8750" data-y="800" data-z="0" data-rotate-y="0"> Dependency 1 </div>
-<div class="step slide" data-x="8750" data-y="1600" data-z="0" data-rotate-y="0"> Dependency 2 </div>
+<div class="step slide" data-x="8750" data-y="0" data-z="0"
+	data-rotate-y="0"> 
+		Slide
+</div>
+<div class="step slide" data-x="8750" data-y="800" data-z="0"
+	data-rotate-y="0">
+		Dependency 1
+</div>
+<div class="step slide" data-x="8750" data-y="1600" data-z="0" 
+	data-rotate-y="0"> 
+		Dependency 2 
+</div>
+<div class="step slide" data-x="8750" data-y="1600" data-z="0" 
+	data-rotate-y="90">
+		Dependency 2 Continuation 1
+</div>
+<div class="step slide" data-x="8750" data-y="1600" data-z="1250" 
+	data-rotate-y="90">
+		Dependency 2 Continuation 2
+</div>
 \end{minted}
 \vspace{-5pt}
-  \caption{Code Snippet for a Dependency}
-  \label{fig:dependencySnippet}
+  \caption{Code Snippet for a Dependency Level}
+  \label{fig:dependencyLevelSnippet}
   \vspace{12pt}
@@
 
-%Combining this information with the order in which these pieces of information occur, i.e.
-with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem.
-We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.
-
 \subsection{The Relational Presentation}
@@
 
+Combining the information about narrative paths, dependencies, and levels, we derived an ordered information graph out of which we have built a presentation that Annie can interact with to learn about the pythagorean theorem.
+In this section we will examine the structure of the created presentation.\\
+
+To begin with, let us examine the choice of layout.
+The goal of this presentation is to have all the information the pythagorean theorem depends on easily accessible so that Annie can reach \textit{course-ancient} information easily.
+The added expressiveness that impress.js offers allowed us to have this in a very structured format.
+Since Prezi was mentioned in the beginning of this paper as a commercial alternative that was considered for this project, let us examine a sample prezi from afar and outline some differences.
+
+draw some conclusions as to why the outcome of this project is so very structured.
+
 \ednote{meaning of moving right and down, rotation.}
-\ednote {path of going through the slides - identify didactic things!!}
-\ednote{show possible paths thru presentation}
-\ednote{structuring of the presentation - link with primitives and spatial narrative}
-\ednote{add example in slides and explain the different levels again}
-\ednote {explain ids of slides}
-\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}
 
+\ednote {path of going through the slides - identify didactic things!!, show possible paths thru presentation}
+
+\ednote{structuring of the presentation - link with primitives and spatial narrative, refer back to primitives: However, the relations can be much more expressive within impress.js.}
 %impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
 
-%into an interactive presentation.
-
-% Layout
-%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft.
-Ideally the added expressiveness that impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.
-\\
+\ednote {explain ids of slides - jsimpress}
 
@@
 %Similarly, we will employ visual relations to show related content.
-
-If we were to learn about the pythagorean theorem and then suddenly realized that we lack knowledge the concept of squares we could then learn about that topic by going to that resource.
-In other words, we check the dependencies of the pythagorean theorem, go that that level and follow the narrative path about squares until we understand squares.
-By adding a way to explore these other levels, the presentation adds more context and allows viewers to understand the subject on a deeper level.
 

### 2015-05-10 Thesis.tex
Im on an angle

@@
 \pagenumbering{arabic}
+
+\newpage
+\thispagestyle{empty}
+\topskip0pt
+\vspace*{\fill}
+\begin{center}
+\textsc{Aut viam inveniam aut faciam}\\
+
+\textit{(I'll either find a path or make one)}\\
+\vspace*{\fill}
+\end{center}
+
+\newpage
 
@@
 \begin{wrapfigure}{l}{\textwidth}
-\vspace{-26pt}
+\vspace{0pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \label{sec:TowardsAMoreEffectivePresentationFormat}
-\ednote{screenshot hack?}
 
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
+\vspace{-0pt}
   \begin{center}
@@
 \end{wrapfigure}
-
+\newpage
 \subsection{Levels}
@@
 These modular excursions are included in the presentation in 3D by making use of CSS3-transitions (see \autoref{fig:dependencyLevelSnippet}).
-Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\
+Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line.\\
 
 \begin{wrapfigure}{r}{\textwidth}
-\vspace{-26pt}
+\vspace{0pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
 <div class="step slide" data-x="8750" data-y="0" data-z="0"
-	data-rotate-y="0"> 
-		Slide
-</div>
+	data-rotate-y="0"> Slide </div>
 <div class="step slide" data-x="8750" data-y="800" data-z="0"
-	data-rotate-y="0">
-		Dependency 1
-</div>
+	data-rotate-y="0"> Dependency 1 </div>
 <div class="step slide" data-x="8750" data-y="1600" data-z="0" 
-	data-rotate-y="0"> 
-		Dependency 2 
-</div>
+	data-rotate-y="0"> Dependency 2  </div>
 <div class="step slide" data-x="8750" data-y="1600" data-z="0" 
-	data-rotate-y="90">
-		Dependency 2 Continuation 1
-</div>
+	data-rotate-y="90"> Dependency 2 Continuation 1 </div>
 <div class="step slide" data-x="8750" data-y="1600" data-z="1250" 
-	data-rotate-y="90">
-		Dependency 2 Continuation 2
-</div>
+	data-rotate-y="90"> Dependency 2 Continuation 2 </div>
 \end{minted}
@@
   \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
+      \includegraphics[width=0.77\textwidth]{assets/final/60degree}
     } 
 \vspace{-5pt}
-  \caption{Visualization of Dependencies}
+  \caption{Visualization of Dependencies and Levels at 60\degree}
   \label{fig:visualDependency}
@@
 \end{wrapfigure}
-
-\ednote {change image}
 
@@
 draw some conclusions as to why the outcome of this project is so very structured.
+
+One might think that this is like a powerpoint with small improvements.
 

### 2015-05-10 Thesis.tex
working on 4.4

@@
   \caption{Visualization of Dependencies and Levels at 60\degree}
-  \label{fig:visualDependency}
+  \label{fig:visualDependencyDegree}
 \vspace{-24pt}
@@
 The added expressiveness that impress.js offers allowed us to have this in a very structured format.
-Since Prezi was mentioned in the beginning of this paper as a commercial alternative that was considered for this project, let us examine a sample prezi from afar and outline some differences.
+Since Prezi was mentioned in the beginning of this paper as a commercial alternative that was considered for this project, let us examine a sample prezi from afar and outline some differences.\\
 
-draw some conclusions as to why the outcome of this project is so very structured.
+\begin{wrapfigure}{l}{0.35\textwidth}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
+      \includegraphics[width=0.32\textwidth]{assets/final/Storytelling}
+    } }
+\vspace{-5pt}
+  \caption{Prezi Example \cite{npentrel2:npentrel15}}
+  \label{fig:preziExample}
+\vspace{-24pt}
+  \end{center}
+\end{wrapfigure}
 
-One might think that this is like a powerpoint with small improvements.
+A prezi, if done right, is generally full of metaphors and visual connections.
+Our tool cannot mimic this creativity as it lacks the capability to abstract on such a high level.
+Therefore our product will be a lot more structure.
+However, it can use the basic elements and use semantic movements to use visual connections similar to those that prezis often feature.
+The movements we have are:
+\vspace{-12pt}
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item movement along the x-axis,
+\item movement along the y-axis, and
+\item rotations.
+\end{enumerate}
+\vspace{5pt}
 
-\ednote{meaning of moving right and down, rotation.}
+The movement along the x-axis has a mostly temporal semantics associated with it.
+Going to the left is connected with going backwards, whereas going to the right is associated with going forwards.
+Apart from going forwards and backwards, we can also move along the y-axis.
+Moving down intuitively means that we dig deeper into a topic and go to the roots whereas moving up means we will be on a higher level.\\
+
+The most interesting movement might be the rotations.
+Rotations aim to give the viewer the feeling that they are entering a topic and a different storyline.
+They come with a change of perspective which is underlined by the 3D transformation that the user sees.\\
+
+One might think that this is like a PowerPoint, since PowerPoint offers similar animations to switch slides.
+The important addition is more obvious when regarding the presentation from a birds perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}.
+The value in these presentation is that through these overviews, dependencies become identifiable.
+More importantly they become accessible and allow viewers to go on small guided tours or small excursions into \textit{course-ancient} topics.\\
 
 \ednote {path of going through the slides - identify didactic things!!, show possible paths thru presentation}
-
 \ednote{structuring of the presentation - link with primitives and spatial narrative, refer back to primitives: However, the relations can be much more expressive within impress.js.}

### 2015-05-10 Thesis.tex
4.4 almost done

@@
 In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
-These occur on different levels as explained in \autoref{sec:levels}.\\
+These occur on different levels as explained in \autoref{sec:levels} and are based on the concept of Spatial Narratives (see \autoref{sec:spatialnarrative}).\\
 
@@
 
-\begin{wrapfigure}{l}{0.35\textwidth}
+\begin{wrapfigure}{l}{0.45\textwidth}
 \vspace{-26pt}
@@
   \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
-      \includegraphics[width=0.32\textwidth]{assets/final/Storytelling}
+      \includegraphics[width=0.42\textwidth]{assets/final/Storytelling}
     } }
@@
 
-A prezi, if done right, is generally full of metaphors and visual connections.
+A prezi, if done right, is generally full of metaphors and meaningful visual connections.
 Our tool cannot mimic this creativity as it lacks the capability to abstract on such a high level.
-Therefore our product will be a lot more structure.
-However, it can use the basic elements and use semantic movements to use visual connections similar to those that prezis often feature.
-The movements we have are:
+Therefore our product will be a lot more structured and focus on visualizing relations between content with movement and closeness.
+This also serves to keep the resulting presentation simple and easily usable.\\
+
+Still, it can use some of the primitives of impress.js (see \autoref{sec:primitives}) to create meaningful visual relations and create semantic movements.
+These meaningful visual connections are similar to those that prezis often feature.
+The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it.
+The following movements add to the meaning:\\
 \vspace{-12pt}
@@
 The movement along the x-axis has a mostly temporal semantics associated with it.
-Going to the left is connected with going backwards, whereas going to the right is associated with going forwards.
+Going to the left is connected with going backwards in the narrative, whereas going to the right is associated with going forwards in the narrative.
 Apart from going forwards and backwards, we can also move along the y-axis.
@@
 Rotations aim to give the viewer the feeling that they are entering a topic and a different storyline.
-They come with a change of perspective which is underlined by the 3D transformation that the user sees.\\
+They come with a change of perspective which is underlined by the 3D transformation that the user sees.
+Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.\\
 
@@
 
-\ednote {path of going through the slides - identify didactic things!!, show possible paths thru presentation}
-\ednote{structuring of the presentation - link with primitives and spatial narrative, refer back to primitives: However, the relations can be much more expressive within impress.js.}
-%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.
+Through this flexibility the presentation allows users to choose their own path while going through the presentation. The didactic element
+
+\ednote {- identify didactic things!!, show possible paths thru presentation}
 
 \ednote {explain ids of slides - jsimpress}
-
-% for creating a spatial narrative as outlined in section \ref{sec:spatialnarrative}.
-Knowing the dependencies and the status of the information will allow us to choose which information to show the user in the close surroundings of the current information we are showing.\\
-
-%Similarly, we will employ visual relations to show related content.
-
-\begin{wrapfigure}{c}{0.97\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
-    } 
-\vspace{-5pt}
-  \caption{Presentation Overview}
-  \label{fig:fullPresentation}
-\vspace{12pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
 
@@
 learn what the user knows and what the user doesnt. - we dont always want to show how to do multiplication
+
+identify didactic things
+
+experiment with layouts
 

### 2015-05-10 Thesis.tex
4.4 done

@@
 The value in these presentation is that through these overviews, dependencies become identifiable.
-More importantly they become accessible and allow viewers to go on small guided tours or small excursions into \textit{course-ancient} topics.\\
-
-Through this flexibility the presentation allows users to choose their own path while going through the presentation. The didactic element
-
-\ednote {- identify didactic things!!, show possible paths thru presentation}
-
-\ednote {explain ids of slides - jsimpress}
+More importantly they become accessible and allow viewers to go on small guided tours or small excursions into \textit{course-ancient} topics giving users the flexibility to choose their own path while going through the presentation.\\
 
@@
 \ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}
+
+\ednote {explain ids of slides - jsimpress}
+
+\ednote {- identify didactic things!!, show possible paths thru presentation}
+
+didactic idioms - digressions - going back to a different topic. 
+not linear but going overall
+
+strawman. - cite MK -> IEEE paer
+
+in thesis a theoretical part like strawman theory
+
+didactic idioms - is there material on that?
+making up
 

### 2015-05-10 Thesis.tex
working on evaluation

@@
 
+\usepackage{quoting}
+\quotingsetup{vskip=50pt}
+
 %\usepackage{csquotes}
@@
 
+\vspace*{1cm}
+
 \textit{(I'll either find a path or make one)}\\
+
+\vspace*{4cm}
+
+\centering
+
+\begin{quoting}
+\begin{center}
+\noindent
+\textit{At this point, I would like to thank Prof.
+Dr.
+Michael Kohlhase for being an inspiring and helpful supervisor.
+Additionally, I would like to thank Mihnea Iancu and Tom Wiesing for aiding me in my research project.\\}
+\end{center}
+\end{quoting}
+
 \vspace*{\fill}
@@
 \end{wrapfigure}
+
+js.impress normally does not support the having different paths depending on pressing the up or down key.
+The JavaScript library had to be slightly adopted to handle this.
+As these are implementation details, this will not be further explained in this paper.
+The interested reader is encouraged to look at the code \cite{npentrel:npentrel15} directly.\\
+
 \newpage
@@
 \label{sec:eval}
-\ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}
-
-\ednote {explain ids of slides - jsimpress}
-
-\ednote {- identify didactic things!!, show possible paths thru presentation}
-
-didactic idioms - digressions - going back to a different topic. 
-not linear but going overall
-
-strawman. - cite MK -> IEEE paer
-
-in thesis a theoretical part like strawman theory
-
-didactic idioms - is there material on that?
-making up
 
@@
 
-For browsers that cannot display the created presentations fallback styles could be added to make the content accessible.
-
-\ednote{ImpressJS had to be adapted}
+\ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}
+
+\ednote {- identify didactic things!!, show possible paths thru presentation}
+didactic idioms - digressions - going back to a different topic. 
+not linear but going overall 
+strawman. - cite MK -> IEEE paper
+in thesis a theoretical part like strawman theory
+didactic idioms - is there material on that? -> making up
 
@@
 experiment with layouts
+
+For browsers that cannot display the created presentations fallback styles could be added to make the content accessible.
 

### 2015-05-10 Thesis.tex
working on evaluation 2

@@
 Even though an evaluation is not fully possible given the limited time frame, the next subsections will attempt to evaluate the created system and the created presentations as well as their shortcomings.
-Afterwards we will briefly look at future work and possible extensions to our system.
+Afterwards we will briefly look at future work and possible extensions to our system.\\
 
@@
 It does so in a very timely manner.
-
-%Cognitively, we will be exploring the space of information systems.
-Therefore we will be examining whether the developed system provides a better system for knowledge transfer.
-For this a qualitative analysis will be conducted as outlined in section \ref{sec:wp5}.
-Based on that we will be able to understand the positive and possibly negative effects of the combination of Spatial Narrative and OMDoc within \sys .\\
-
-%Furthermore, with the above evaluation, we want to answer the main question of this proposed research, namely how and whether spatial narrative can be combined with inherent semantic closeness to facilitate and improve knowledge transfer.\\
+In the starting phase of this research, I imagined the created presentations should look a lot more like clustered graphs \ednote{add image}.
+While implementing the system, I not only found that such an implementation would be very difficult but also that it would likely confuse the potential user.\\
+
+When using Prezi, it is a human being that can creatively think of links and therefore make more graphical presentations.
+Due to the fact that we built a system that only has limited intelligence, we end up with a far more structured presentation.
+However, considering that the goal of the created presentation is to allow users to intuitively understand dependencies and to allow them to deviate from the primary narrative path to enter the level of one of the dependencies and follow its narrative path for a while, it became obvious that a simple structure for this presentation was even preferable.\\
+
+After having considere the systematic aspects, let us now look at the cognitive aspects.
+Cognitively, we explored a part of the field of information systems.
+It is still an open question whether the developed system provides a better system for knowledge transfer.
+I strongly believe that the created system \sys adds value to presentation and has the power to facilitate and improve knowledge transfer due to the following reasons:\\
+Missing this info def shortcoming btu also future work
 
 \ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}
-
 \ednote {- identify didactic things!!, show possible paths thru presentation}

### 2015-05-10 Thesis.tex
working on evaluation 3

@@
 It is still an open question whether the developed system provides a better system for knowledge transfer.
-I strongly believe that the created system \sys adds value to presentation and has the power to facilitate and improve knowledge transfer due to the following reasons:\\
-Missing this info def shortcoming btu also future work
+I strongly believe that the created system \sys adds value to presentation and has the power to facilitate and improve knowledge transfer due to some reasons that were already shown in the \autoref{sec:relatedworks}.
+These sources argued that the linking of learning materials is useful for the user and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.\\
+
+\begin{wrapfigure}{l}{0.45\textwidth}
+\vspace{-28pt}
+  \begin{center}
+  \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
+      \includegraphics[width=0.42\textwidth]{assets/final/ExamplePathTriangle}
+    } }
+\vspace{-5pt}
+  \caption{Path Example}
+  \label{fig:pathExample}
+\vspace{-24pt}
+  \end{center}
+\end{wrapfigure}
+
+Since a qualitative analysis was unfortunately not possible in this time frame, we can only make an educated guess at the usefulness.
+To strengthen these educated guesses, we will look at the potential path a user could take through the presentation we created by examining \autoref{fig:pathExample}.\\
 

### 2015-05-10 Thesis.tex
eval done

@@
 The most interesting movement might be the rotations.
-Rotations aim to give the viewer the feeling that they are entering a topic and a different storyline.
+It should be briefly mentioned that too much rotation leads to seasickness in users, as anyone who has seen a bad prezi can attest to.
+These are generally rotations around the x-axis that rotate more than 20\degree, therefore our rotations are not affected.
+Instead of causing seasickness, our rotations aim to give the viewer the feeling that they are entering a topic and a different storyline.
 They come with a change of perspective which is underlined by the 3D transformation that the user sees.
@@
 
+\begin{wrapfigure}{l}{0.4\textwidth}
+\vspace{-28pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.37\textwidth]{assets/final/initialIdea}
+    }
+\vspace{-5pt}
+  \caption{Initial Presentation Idea}
+  \label{fig:initialIdea}
+\vspace{-24pt}
+  \end{center}
+\end{wrapfigure}
+
 The evaluation conducted in the following part is on the one hand, systematic and, on the other hand, cognitive.
@@
 It does so in a very timely manner.
-In the starting phase of this research, I imagined the created presentations should look a lot more like clustered graphs \ednote{add image}.
+In the starting phase of this research, I imagined the created presentations should look a lot more like clustered graphs such as in \autoref{fig:initialIdea}.
+Possibly with nodes that are close if they are semantically close and the size of the nodes reflecting the importance of the node.
 While implementing the system, I not only found that such an implementation would be very difficult but also that it would likely confuse the potential user.\\
@@
 
-\ednote {rueckschauend bewerten und mit anderen dingen vergleichen so wie prezi best practices und prezis in general}
-\ednote {- identify didactic things!!, show possible paths thru presentation}
-didactic idioms - digressions - going back to a different topic. 
-not linear but going overall 
-strawman. - cite MK -> IEEE paper
-in thesis a theoretical part like strawman theory
-didactic idioms - is there material on that? -> making up
+In the book \textit{OMDoc - An Open Markup Format for Mathematical Documents} \cite{URL:omdocspec}, a didactic figure called the straw-man theory is introduced as an example for a naïve reduced approximation of the real theory that aims to show an example to explain why this approximation does not work.
+Our system is not sophisticated enough to examine these structures on its own and figure out which information is best to be shown.
+Instead, \sys simply finds where the dependent information has been taught before and reuses the order in which it was taught before.
+In essence, our system heavily relies on sensible input.\\
+
+Given this sensible input we offer the user digressions, where the user can go back to a different topic and follow its narrative path for a while.
+An example for this is highlighted with a blue triangle in \autoref{fig:pathExample}.
+These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to what I call relational presentations.\\
 

### 2015-05-10 Thesis.tex
added crappy conclusion

@@
 
-\ednote{think of more extensions when you write up the rest}
-
 This section lists some ideas on future work regarding this topic and the created system \sys.
@@
 
-\ednote{not just prerequisite knowledge but also knowledge that builds on the current topic - bored students can thus already learn more!}
-
-machine learning to make smart offers of knowledge.
-
-learn what the user knows and what the user doesnt. - we dont always want to show how to do multiplication
-
-identify didactic things
-
-experiment with layouts
-
-For browsers that cannot display the created presentations fallback styles could be added to make the content accessible.
+In terms of improving content, it would be interesting to not just provide paths to dependencies or prerequisite knowledge but also to knowledge that builds on the current topic.
+That way students that learn fast can already explore higher levels.\\
+
+This whole research project would also benefit from machine learning which could allow us to make smart offers of likely dependencies.
+On an individual basis we could use it to learn what the user knows and what the user does not know.
+Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn.
+Combining machine learning with the identification of more didactic paths or figures within the data could further improve knowledge transfer.\\
 
@@
 \label{sec:conclusion}
-Spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer.\\
-%The proposed research will evaluate if and how spatial narrative can be combined with semantic closeness to form visual presentations that will facilitate knowledge transfer.
-The knowledge presentation systen \sys that we will implement will allow us to automatically create these visual presentations from the OMDoc format.
-Through using semantic closeness the presentations can be created with meaningful visual connections between information.
-Similarly to how the Semantic Web tries to add relations between different resources for machines, \sys will add meaningful relations between course content.\\
-
-%Going back to our contrived example, \sys will provide Annie's teacher with a tool that allows her to use her normal lecture material in a more interactive way.
-Thus when the teacher realizes that Annie needs to revise previous material, the teacher can easily go to that material and provide Annie with a good learning experience.
+
+In this research project we set out to help Annie understand the pythagorean theorem.
+Her problem was that she did not know about some of the dependent information, i.e.
+right angles, and since there was no easy way to access this information she could not understand the topic fully.
+To help her, we created a system \sys that parses the documents that the instructor wrote and created a relational presentation out of it.\\
+
+This relational presentation combines spatial narrative with information about the relations between different pieces of information.
+In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation.
+This allows Annie choose her own path in going through the presentation while seamlessly looking up related information.\\
+
+Not just Annie has an easier way of going through the presentation on her own, Annie's teacher now has a tool that allows her to use her normal lecture material in a more interactive way.
+Thus when the teacher realizes that the students need to revise previous material, the teacher can easily go to that material and provide them with a good learning experience.
 This facilitates knowledge transfer and allows for a more engaging and interactive education.\\
@@
 
-%In essence, this proposed research will be beneficial for education and knowledge transfer.
-It aims to make the creation of engaging and interactive presentations simple and fast for current users of OMDoc.
-Should this research prove successful it could be adapted for other areas.
-In the future creating a meaningful, interactive presentation might be just a matter of uploading an annotated document.
+%Should this research prove successful it could be adapted for other areas. In the future creating a meaningful, interactive presentation might be just a matter of uploading an annotated document.
 

### 2015-05-10 Thesis.tex
typos

@@
     \huge
-    \textbf{The Combination of Spatial Narrative and Semantic Closeness to Derive Visualizations of Theory Graphs}
+    \textbf{The Combination of Spatial Narrative and Semantic Closeness to Derive Visualizations of Information Graphs}
   \end{center}
@@
 
-The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
+The OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
 Using OMDoc, the implemented system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
-Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning while discussing several different presentation schemata that are valuable for learning.
+Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning.
 This approach to presenting learning materials changes how we interact with course material which will allow students to learn better.
@@
 \clearpage
-\pagenumbering{arabic}
 
@@
 \newpage
+\pagenumbering{arabic}
 
@@
 Learning new things is a bit like hiking up a mountain.
-If you have ever gone hiking you know that it is relatively hard to hike up a steep mountain directly as shown in \autoref{fig:straight}.
+If you have ever gone hiking, you know that it is relatively hard to hike up a steep mountain directly as shown in \autoref{fig:straight}.
 Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}.
@@
 When we look at education, we normally only have one straight path.
-That is true for the narration in books, movies, Facebook timelines, and also traditional slide-based presentations.
-For three out of those four this has not changed in decades.
+That is true for the narration in books, movies, and also traditional slide-based presentations.
+This has not changed in decades.
 With the advancement of technology, we are however able to change the way presentations and their narratives work.
@@
 
-Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem \autoref{fig:slideP}.
+Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see \autoref{fig:slideP}).
 She is then given a triangle with sides a = 3 cm and b = 4 cm.
@@
 
-Annie's example shows the dependencies of different pieces of information (see \autoref{fig:PythDep}), i.e.
+Annie's example shows the dependencies of different pieces of information (see \autoref{fig:deppyg}), i.e.
 the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles.
@@
 To achieve our goal to help Annie, we will set out to create a relational presentation system \sys to visually present information and its context which allows Annie to interact with the content and choose a path that matches her knowledge base.
-For this we will be using the OMDoc (Open Mathematical Documents) format which, given an annotated set of documents, will provide us with the necessary HTML-representation and PDF-representation of the information.
+For this we will be using the OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) format which, given an annotated set of documents, will provide us with the necessary XHTML-representation and PDF-representation of the information \cite{Kohlhase:OMDoc1.2}.
 It will also allow us to extract information about the semantic closeness of different pieces of information.\\
 
-This information alone would tell Annie where she might find the information she seeks but we will only use this as a starting point.
-We will use this information to visualize the dependencies of the information in a simple but effective approach using the presentation framework impress.js.
+This information alone would tell Annie where she might find the information she seeks but it will only serve as a starting point.
+In face, this information will be used to visualize the dependencies of the information in a simple but effective approach using the presentation framework impress.js \cite{JSImpress:npentrel14}.
 The visualization of the information will make use of spatial narrative to connect information in a logical way.
@@
 
-Along the way of helping Annie, we will explore the question how to allow users to go through flexible presentations where they can choose their own paths to explore the context of a topic as needed by browsing through related resources seamlessly.
-Specifically this research examines how spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer by providing the flexibility in a presentation to choose a path that fits.\\
+Along the way of helping Annie, we will explore the question of how to create a flexible presentation which allows Annie to choose her own path to explore the context of a topic as needed by browsing through related resources seamlessly.
+Specifically this research examines how spatial narrative can be combined with inherent semantic closeness of different pieces of information in order to facilitate knowledge transfer by providing the flexibility in a presentation to choose a path that fits.\\
 
@@
 It is left to the reader to think about examples in his or her own life where he or she would have appreciated having these type of flexible presentations.
-There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be straight or curvy.\\
+There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be straight or curvy.
 
@@
 Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}.
-For this systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
+For this purpose, systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
 Some of these systems use temporal information \cite{DBLP:dblp_journals/isci/ChungS97} to show multiple resources in sync as they appeared in the lecture.
@@
 This creates guided tours on topics depending on the background of the user.
-While following the same ideal to improve knowledge transfer, it differs from this work in its presentation format.
+While working towards the same goal, namely to improve knowledge transfer, it differs from this work in its presentation format.
 While Siekmann et al., focused on one topic and displaying it differently to users with different backgrounds, this research will show the topics of a whole course while allowing to see dependencies and while allowing to diverge from the prescribed presentation path.\\
@@
 It demonstrates the need for assistance in form of navigation support for the reading of mathematical documents by creating a system that allows for semantic navigation in Excel spreadsheets.
-This research underlines the importance of a system that allows users like Annie to navigate information according to dependencies.\\
+This research underlines the importance of a system that allows users like Annie to navigate information according to dependencies.
 
@@
 
-In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how the presentation can be improved to transfer knowledge more effectively.\\
+In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how the presentation can be improved to transfer knowledge more effectively.
 
@@
 We will define it as knowledge that is made up out of several pieces of information that are connected.
-In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \autoref{fig:deppyg}).\\
+In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \autoref{fig:deppyg} above).\\
 
@@
 Without this \textit{context}, Annie cannot understand the theorem.
-Figure \ref{fig:deppyg} illustrates the context by showing the dependencies of the theorem, i.e.
+Figure \ref{fig:deppyg} above illustrates the context by showing the dependencies of the theorem, i.e.
 calculating squares, area calculation, triangles, and right angles.
 It represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}.
-We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.\\
+The relatedness between the relevant concepts can also be imagined as a network.
+We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.
 
@@
 
-OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
+OMDoc \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
 As such it is a semi-formal domain ontology.
@@
 
-If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in different ways.
+If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in various ways.
 This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts.
 The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations.
-This elevates the net of separate pieces of information that are stored individually to a semantic representation and can be used to improve knowledge transfer.\\
+This elevates the net of separate pieces of information that are stored individually to a semantic representation and can be used to improve knowledge transfer.
 
@@
 The information about squares which Annie still remembers is \textit{course-old}.
-Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.\\
+Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
 
@@
 For impress.js, the primitive elements are text, images, slides, and the visual relation between the different frame-like structures.
-The slides can be mapped directly to the nodes/concepts that graphs use.
+The slides can be mapped directly to the nodes/concepts which graphs use.
 Text and images are taken for granted within the slides.
@@
 As such the temporal associations show the path that a traditional lecture would take.
-The dependencies that are visualized around each slide, mainly above or below the slide, allow for additional interactiveness.\\
+The dependencies that are visualized around each slide, mainly above or below the slide, allow for additional interactivity.
 
@@
 
-The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'" \cite{SpatialNarratives:npentrel14}.
+The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile \textit{guided tours} based on the thematically and narrative linking of a set of locations within an area into a \textit{spatial narrative}" \cite{SpatialNarratives:npentrel14}.
 Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\
@@
 In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
-For Annie this means that she will be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
-It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\
+For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
+It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.
 
@@
 \end{minted}
-\vspace{-5pt}
+\vspace{-8pt}
   \caption{Code Snippet to Create a Slide}
@@
 
-In the following code snippets, a few other basic functionalities we will be using are explained \cite{andismith:npentrel15}.
+In the following code snippets, a few other basic functionalities we will be using are illustrated \cite{andismith:npentrel15}.
 The opacity attribute allows us to discriminate between active and inactive slides which will later on allow us to hide content so as to not throw too much information at a user.
-Adding an overview can be accomplished with the last past of the CSS snippet and the html snippet below that.\\
+Adding an overview can be accomplished with the last past of the CSS snippet and the html snippet below that.
 
@@
 \end{minted}
-\vspace{-5pt}
+\vspace{-8pt}
   \caption{Code Snippet to Show and Hide Content}
   \label{fig:SSlide}
-  \vspace{30pt}
+  \vspace{20pt}
 \end{wrapfigure}
@@
 \begin{wrapfigure}{l}{\textwidth}
-\vspace{-26pt}
+\vspace{-10pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
-\vspace{-7pt}
+\vspace{-11pt}
   \caption{Code Snippet for an Overview}
@@
   \fbox{
-      \includegraphics[width=0.87\textwidth]{assets/final/Architecture}
-    } 
-\vspace{-5pt}
+      \includegraphics[width=0.70\textwidth]{assets/final/Architecture}
+    } 
+\vspace{-6pt}
   \caption{Architecture Diagram}
@@
 
-With the OMDoc framework and its tools it is possible to write down course notes or other documents in \stex.
+With the OMDoc framework and its tools it is possible to write down course notes or other documents in \textbf{S}emantically enhanced \TeX / \LaTeX\ (\stex).
 The Local MathHub Tool (lmh) uses these to create, among other things, PDF slides, XHTML slides, and relational information.
@@
 To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo.
-The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}.\\
-
-To bring the presentation to life the framework impress.js which was introduced in \autoref{sec:Impressjs} was used because it easy to reuse the XHTML code that was automatically generated by lmh.
+The design of the template is based on a presentation by S.
+Wolf \cite{Wolf:npentrel15}.\\
+
+To bring the presentation to life the framework impress.js which was introduced in \autoref{sec:Impressjs} was used because it is simple to reuse the XHTML code that was automatically generated by lmh.
 An important additional reason for the choice of impress.js is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and \autoref{sec:Impressjs}.
 Due to the choice of impress.js \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
-impress.js works in all modern browsers that support CSS 3D transforms.\\
+The library impress.js works in all modern browsers that support CSS 3D transforms.
 
@@
     } 
-\vspace{-16pt}
+\vspace{-20pt}
   \caption{Inclusion Graph for the Pythagorean Theorem}
@@
 \begin{wrapfigure}{l}{\textwidth}
-\vspace{-80pt}
-\end{wrapfigure}
-
-\newpage
+\vspace{-60pt}
+\end{wrapfigure}
 
@@
     } 
-\vspace{-16pt}
+\vspace{-20pt}
   \caption{Inclusion Graph for GenCS}
@@
 \begin{wrapfigure}{r}{\textwidth}
-\vspace{-26pt}
+\vspace{-0pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
-\vspace{-5pt}
+\vspace{-8pt}
   \caption{Code Snippet for a Narrative Path}
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-20pt}
+\vspace{-30pt}
   \begin{center}
@@
   \end{center}
-\vspace{-16pt}
+\vspace{-20pt}
   \caption{Primary Narrative Path}
@@
 This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
-This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\
+This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear.\\
 
 This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic.
-In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
+These narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
 Going back to our example of Annie, an example of a subsection would be the information concerning angles.
 In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
-These occur on different levels as explained in \autoref{sec:levels} and are based on the concept of Spatial Narratives (see \autoref{sec:spatialnarrative}).\\
+These occur on different levels as explained in \autoref{sec:levels} and are based on the concept of Spatial Narratives (see \autoref{sec:spatialnarrative}).
 
@@
 The system \sys parses the relational data and thus retrieves the dependencies of the topics.
-We already know that the level a piece of information is associated with infers that it is \textit{course-old} information \ednote{change order}.
-Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information that happened more time ago.\\
+We already know that the level with which a piece of information is associated infers that it is \textit{course-old} information \ednote{change order}.
+Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained ago.\\
 
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-0pt}
+\vspace{-26pt}
   \begin{center}
@@
     } 
-\vspace{-5pt}
+\vspace{-20pt}
   \caption{Dependency Graph}
@@
 
-With the information about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the pythagorean theorem.
+With the data about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the pythagorean theorem.
 \sys creates this presentation incrementally.
-As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides.
+As outlined in \autoref{sec:narrativePaths} and illustrated in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides.
 After adding each slide it checks whether there is \textit{course-ancient} information, i.e.
@@
 If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).
-This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value (see \autoref{fig:dependencySnippet}).\\
+This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value (see \autoref{fig:dependencySnippet}).
 
 \begin{wrapfigure}{r}{\textwidth}
-\vspace{-26pt}
+\vspace{-0pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 \end{minted}
-\vspace{-5pt}
+\vspace{-8pt}
   \caption{Code Snippet for a Dependency}
@@
     } 
-\vspace{-5pt}
+\vspace{-20pt}
   \caption{Visualization of Dependencies}
   \label{fig:visualDependency}
-\vspace{-24pt}
+\vspace{12pt}
   \end{center}
@@
 
-js.impress normally does not support the having different paths depending on pressing the up or down key.
+The library impress.js normally does not support the having different paths depending on pressing the up or down key.
 The JavaScript library had to be slightly adopted to handle this.
 As these are implementation details, this will not be further explained in this paper.
-The interested reader is encouraged to look at the code \cite{npentrel:npentrel15} directly.\\
-
-\newpage
+The interested reader is encouraged to look at the code \cite{npentrel:npentrel15} directly.
+
 \subsection{Levels}
@@
 In essence, on any level the order of information in that topic is a narrative path.
-In mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
+Expressed in mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
 From these levels we can infer the status of the information.
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
+\vspace{0pt}
   \begin{center}
@@
     } 
-\vspace{-5pt}
+\vspace{-20pt}
   \caption{Inclusion Graph with Levels}
@@
 \end{minted}
-\vspace{-5pt}
+\vspace{-8pt}
   \caption{Code Snippet for a Dependency Level}
@@
 \begin{wrapfigure}{c}{1\textwidth}
-\vspace{-26pt}
+\vspace{-0pt}
   \begin{center}
@@
     } }
-\vspace{-5pt}
+\vspace{-20pt}
   \caption{Prezi Example \cite{npentrel2:npentrel15}}
@@
 The value in these presentation is that through these overviews, dependencies become identifiable.
-More importantly they become accessible and allow viewers to go on small guided tours or small excursions into \textit{course-ancient} topics giving users the flexibility to choose their own path while going through the presentation.\\
+More importantly they become accessible and allow viewers to go on small guided tours or small excursions into \textit{course-ancient} topics giving users the flexibility to choose their own path while going through the presentation.
 
@@
     }
-\vspace{-5pt}
+\vspace{-20pt}
   \caption{Initial Presentation Idea}
@@
     } }
-\vspace{-5pt}
+\vspace{-20pt}
   \caption{Path Example}
@@
 An example for this is highlighted with a blue triangle in \autoref{fig:pathExample}.
-These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to what I call relational presentations.\\
+These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to what I call relational presentations.
 
@@
 Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn.
-Combining machine learning with the identification of more didactic paths or figures within the data could further improve knowledge transfer.\\
+Combining machine learning with the identification of more didactic paths or figures within the data could further improve knowledge transfer.
 
@@
 
-%But not only will \sys make courses more engaging, interactive, and easier to follow, it will also lead to better knowledge absorption because students learn the concepts and in addition intuitively understand how they relate to one another.
-This allows faster revision of material and facilitates studying without a teacher present.\\
-
-%Should this research prove successful it could be adapted for other areas. In the future creating a meaningful, interactive presentation might be just a matter of uploading an annotated document.
+In the future, I believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them.
+In the introduction, I introduced the metaphor of hiking up a mountain which can be done in different ways.
+The type of presentations this research built allow for a lot of different paths to reach a learning goal that fit individuals and allow for more interactivity.\\
+
+The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits.\\
 

### 2015-05-10 Thesis.tex
proofed till 3

@@
 Both paths lead to the goal.
-When we look at education, we normally only have one straight path.
+Within education, there is normally only one straight path.
 That is true for the narration in books, movies, and also traditional slide-based presentations.
@@
 As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up.
-By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the pythagorean theorem.\\
+By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.\\
 
@@
 Along the way of helping Annie, we will explore the question of how to create a flexible presentation which allows Annie to choose her own path to explore the context of a topic as needed by browsing through related resources seamlessly.
-Specifically this research examines how spatial narrative can be combined with inherent semantic closeness of different pieces of information in order to facilitate knowledge transfer by providing the flexibility in a presentation to choose a path that fits.\\
-
-Overall, this work will showcase a tool for automatic contextual visualization of information through the usage of both spatial narrative and semantic closeness of information thus connecting information logically.
-The end product should be a system that creates presentations which allow users to choose their own narrative path by interacting with the presentation such that they can seamlessly explore related topics and brush up on half-forgotten topics.\\
-
-It is left to the reader to think about examples in his or her own life where he or she would have appreciated having these type of flexible presentations.
-There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be straight or curvy.
+To create this presentation a tool for automatic contextual visualization of information will be introduced.
+Through the usage of both spatial narrative and semantic closeness of information it will connect information logically.
+The end product will be a presentations which allow Annie to choose her own path by interacting with the presentation to seamlessly explore related topics and brush up on half-forgotten topics like right angles.\\
+
+It is left to the reader to think about examples in his or her own life where he or she would have appreciated having this type of flexible presentations.
+There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be by following a straight or a curvy path.
 
@@
 For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map.
-We, on the other hand, will focus on exactly that, i.e.
+This research, on the other hand, will focus on exactly that, i.e.
 dependencies and the creation of interactive presentations.\\
@@
 \textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
-In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
+In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
 
@@
 
-In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus are introduced.
+In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus is introduced.
 In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
@@
 Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to \autoref{fig:deppyg}).
-These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
-
-For impress.js, the primitive elements are text, images, slides, and the visual relation between the different frame-like structures.
+These structural primitives and semantic primitives provide the basics that information graphs can be built on.\\
+
+For impress.js, the primitive elements are text, images, slides, and the visual relation between the different slide-like structures.
 The slides can be mapped directly to the nodes/concepts which graphs use.
@@
 
-The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile \textit{guided tours} based on the thematically and narrative linking of a set of locations within an area into a \textit{spatial narrative}" \cite{SpatialNarratives:npentrel14}.
+The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexible \textit{guided tours} based on the thematically and narrative linking of a set of locations within an area into a \textit{spatial narrative}" \cite{SpatialNarratives:npentrel14}.
 Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\
 
-The benefits of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
+The benefit of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
 By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
-That is because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \cite{Storytelling:npentrel14}.\\
+That is the case because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \cite{Storytelling:npentrel14}.\\
 
@@
 
-In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+In this research we will use this knowledge to form an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
 For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
-It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.
+It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in an instant.
 
@@
 For the implementation of \sys, impress.js will be used, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
-The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's.
+The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka.
 It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
-The presentation data is entered in the html file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide.
-The \texttt{data-x} and \texttt{data-y} axis change the position of the element according to the normal x- and y-axes.
+The presentation data is entered in the HTML file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide.
+The \texttt{data-x} and \texttt{data-y} attributes change the position of the element according to the normal x- and y-axes.
 The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
@@
 Apart from these basic attributes, impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}.
-As shown in \autoref{fig:Rotate} this allows the dependency graph to go into the third dimension.\\
-
-In the following code snippets, a few other basic functionalities we will be using are illustrated \cite{andismith:npentrel15}.
-The opacity attribute allows us to discriminate between active and inactive slides which will later on allow us to hide content so as to not throw too much information at a user.
-Adding an overview can be accomplished with the last past of the CSS snippet and the html snippet below that.
+As shown in \autoref{fig:Rotate} this allows the presentation to go into the third dimension.\\
+
+In the following code snippets, a few other basic functionalities are illustrated \cite{andismith:npentrel15}.
+The opacity attribute allows us to discriminate between active and inactive slides which allows us to hide content so as not show too much information to a user at once.
+Adding an overview can be accomplished with the last part of the CSS snippet and the HTML snippet below that.
 
@@
 The Local MathHub Tool (lmh) uses these to create, among other things, PDF slides, XHTML slides, and relational information.
-To help Annie, let us use a document that explains the pythagorean theorem and related topics.
+To help Annie, let us use a document that explains the Pythagorean theorem and related topics.
 The files that lmh creates, along with the \stex -files will be used as input in the next steps.
@@
 In our system \sys, we parse the \stex files using a Depth First Search algorithm to retrieve the traditional narrative the writer intended to use.
-For the explanation of the pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}.
+For the explanation of the Pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}.
 The graph for a whole course like the General Computer Science course (GenCS) at Jacobs University Bremen \cite{Kohlhase:GenCSII:base} is too big to be shown properly (see \autoref{fig:inclusionGraphGenCS}).\\
@@
 The general format of one relation can be seen in \autoref{fig:reldatacode} (lines 1-2).
-A specific example showing some of the dependencies for the pythagorean theorem example can be seen in lines 4-11.\\
+A specific example showing some of the dependencies for the Pythagorean theorem example can be seen in lines 4-11.\\
 
@@
 
-With the data about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the pythagorean theorem.
+With the data about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the Pythagorean theorem.
 \sys creates this presentation incrementally.
@@
 
-Combining the information about narrative paths, dependencies, and levels, we derived an ordered information graph out of which we have built a presentation that Annie can interact with to learn about the pythagorean theorem.
+Combining the information about narrative paths, dependencies, and levels, we derived an ordered information graph out of which we have built a presentation that Annie can interact with to learn about the Pythagorean theorem.
 In this section we will examine the structure of the created presentation.\\
@@
 To begin with, let us examine the choice of layout.
-The goal of this presentation is to have all the information the pythagorean theorem depends on easily accessible so that Annie can reach \textit{course-ancient} information easily.
+The goal of this presentation is to have all the information the Pythagorean theorem depends on easily accessible so that Annie can reach \textit{course-ancient} information easily.
 The added expressiveness that impress.js offers allowed us to have this in a very structured format.
@@
 
-In this research project we set out to help Annie understand the pythagorean theorem.
+In this research project we set out to help Annie understand the Pythagorean theorem.
 Her problem was that she did not know about some of the dependent information, i.e.

### 2015-05-10 Thesis.tex
1-5 done

@@
 \begin{wrapfigure}{l}{\textwidth}
-\vspace{-26pt}
+\vspace{-0pt}
   \begin{center}
@@
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item Get user input for the location and names of folders.
+\item Get user input for the locations and names of folders.
 \item Parse \sTeX to retrieve the order of slides.
 \item Extract dependencies from relational info.
-\item Extract necessary XHTML or PDF parts for slides.
+\item Extract necessary XHTML or PNG parts for slides.
 \item Create presentation.
@@
 
-In the next step the relational information is parsed and transformed into a hashtable.
+In the next step the relational information is parsed and put into a hashtable.
 The keys are the slides which link to an array of dependent slides.
@@
 The details of this process will be explained in subsection \ref{sec:narrativePaths}, \ref{sec:orderedInfoGraphs}, and \ref{sec:levels}.
-To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo.
+To complement the HTML, a CSS stylesheet is added which adds the some design elements.
 The design of the template is based on a presentation by S.
@@
 
-To bring the presentation to life the framework impress.js which was introduced in \autoref{sec:Impressjs} was used because it is simple to reuse the XHTML code that was automatically generated by lmh.
-An important additional reason for the choice of impress.js is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and \autoref{sec:Impressjs}.
-Due to the choice of impress.js \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly.
-The library impress.js works in all modern browsers that support CSS 3D transforms.
+To bring the presentation to life the library impress.js which was introduced in \autoref{sec:Impressjs} is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh.
+An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and \autoref{sec:Impressjs}.
+The library impress.js works in all modern browsers that support CSS 3D transforms; some older and mobile browsers are, however, not able to display the created presentations properly.
 
@@
 the statements or theories.
-Narrative layers refer to the order the mathematical objects from content layers are presented.\\
+Narrative layers refer to the order in which the mathematical objects from content layers are presented.\\
 
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
-    } 
-\vspace{-20pt}
+\vspace{-0pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.87\textwidth]{assets/final/inclusionGraphPythagorean}
+    } 
+\vspace{-8pt}
   \caption{Inclusion Graph for the Pythagorean Theorem}
@@
 
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-60pt}
-\end{wrapfigure}
-
 \begin{wrapfigure}{l}{0.3\textwidth}
@@
 
-In our system \sys, we parse the \stex files using a Depth First Search algorithm to retrieve the traditional narrative the writer intended to use.
+In our system, the \stex files are parsed using a Depth First Search algorithm to retrieve the narrative the writer intended to use.
 For the explanation of the Pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}.
@@
 To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}.
-This code snippet creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\
+This code then creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\
 
 \begin{wrapfigure}{r}{\textwidth}
-\vspace{-0pt}
+\vspace{-20pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 <div class="step" data-x="2500" data-y="0"> ... </div>
-<div class="step" data-x="3750" data-y="0"> ... </div>
-<div class="step" data-x="5000" data-y="0"> ... </div>
 \end{minted}
@@
 This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
-This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear.\\
+This temporal information is what we extracted from the \stex files as the order in which the slides (or the information on the slides) should appear.\\
 
@@
 In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
-These occur on different levels as explained in \autoref{sec:levels} and are based on the concept of Spatial Narratives (see \autoref{sec:spatialnarrative}).
+These occur on different levels as explained in \autoref{sec:levels} and are based on the concept of spatial parratives (see \autoref{sec:spatialnarrative}).
 
@@
 pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
-pythagoreantheorem/measurements/area.omdoc?angle
+pythagoreantheorem/measurements/area.omdoc?area
 \end{minted}
@@
 
-The system \sys parses the relational data and thus retrieves the dependencies of the topics.
-We already know that the level with which a piece of information is associated infers that it is \textit{course-old} information \ednote{change order}.
-Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained ago.\\
+The system \sys parses the relational data and thus retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
+Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information likely obtained longer ago.\\
 
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-26pt}
+\vspace{-30pt}
   \begin{center}
@@
   \label{fig:depGraphPythagoreanFull}
-\vspace{12pt}
+\vspace{0pt}
   \end{center}
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
+\vspace{-60pt}
 \end{wrapfigure}
@@
 \begin{wrapfigure}{c}{1\textwidth}
-\vspace{-26pt}
+\vspace{-16pt}
   \begin{center}
@@
 
-The library impress.js normally does not support the having different paths depending on pressing the up or down key.
-The JavaScript library had to be slightly adopted to handle this.
-As these are implementation details, this will not be further explained in this paper.
+The library impress.js normally does not support having different paths depending on pressing the right or down key.
+Therefore it had to be slightly adapted to handle this behavior.
+As these are implementation details, this will not be further explained here.
 The interested reader is encouraged to look at the code \cite{npentrel:npentrel15} directly.
@@
 
-When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included.
-These included files again include further tex-files etc..
+When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other \TeX\ files are included.
+These included files again include further \TeX\ files etc..
 Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.
-In essence, on any level the order of information in that topic is a narrative path.
+In essence, on any level the order of information in that topic is a narrative path itself.
 Expressed in mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
 From these levels we can infer the status of the information.
-Anything that is on the same level or in the sublevels thereof is generally considered to be \textit{course-old} information.\\
+We already know that a dependent piece of information infers that it is \textit{course-ancient} information.
+Anything that is on the same level or in the sublevels thereof is considered to be \textit{course-old} information.
 
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{0pt}
+\vspace{-16pt}
   \begin{center}
@@
   \label{fig:levelsGraph}
-\vspace{12pt}
+\vspace{0pt}
   \end{center}
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-
-If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter that level.
-The presentation will then continue on that level and give all the slides from that topic in the correct order.
+\vspace{-70pt}
+\end{wrapfigure}
+
+If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter the respective level.
+The presentation will then continue on that level and show all the slides from that topic in the correct order.
 Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path.
@@
 These modular excursions are included in the presentation in 3D by making use of CSS3-transitions (see \autoref{fig:dependencyLevelSnippet}).
-Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line.\\
+Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line (see \autoref{fig:visualDependencyDegree}).
 
 \begin{wrapfigure}{r}{\textwidth}
-\vspace{0pt}
+\vspace{-22pt}
 \begin{minted}[linenos=true, bgcolor=bg]{C}
@@
 	data-rotate-y="0"> Dependency 1  </div>
-<div class="step slide" data-x="8750" data-y="1600" data-z="0" 
-	data-rotate-y="0"> Dependency 2  </div>
-<div class="step slide" data-x="8750" data-y="1600" data-z="0" 
-	data-rotate-y="90"> Dependency 2 Continuation 1 </div>
-<div class="step slide" data-x="8750" data-y="1600" data-z="1250" 
-	data-rotate-y="90"> Dependency 2 Continuation 2 </div>
+<div class="step slide" data-x="8750" data-y="800" data-z="0" 
+	data-rotate-y="90"> Dependency 1 Continuation 1 </div>
+<div class="step slide" data-x="8750" data-y="800" data-z="1250" 
+	data-rotate-y="90"> Dependency 1 Continuation 2 </div>
 \end{minted}
@@
 \begin{wrapfigure}{c}{1\textwidth}
-\vspace{-0pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.77\textwidth]{assets/final/60degree}
+\vspace{-26pt}
+  \begin{center}
+  \fbox{
+      \includegraphics[width=0.65\textwidth]{assets/final/60degree}
     } 
 \vspace{-5pt}
-  \caption{Visualization of Dependencies and Levels at 60\degree}
+  \caption [Caption for LOF]{Visualization of Dependencies and Levels at 60\degree\ \footnotemark}
   \label{fig:visualDependencyDegree}
@@
 \end{wrapfigure}
+
+\footnotetext{The overlapping slides do not interfere as they are at a 90\degree\ angle.
+Therefore when seeing one slide, the other slide will be visible only from the slide.
+Since a slide is very thin this makes it invisible.}
 
@@
 Our tool cannot mimic this creativity as it lacks the capability to abstract on such a high level.
-Therefore our product will be a lot more structured and focus on visualizing relations between content with movement and closeness.
+Therefore our product is a lot more structured and focused on visualizing relations between content with movement and closeness.
 This also serves to keep the resulting presentation simple and easily usable.\\
 
-Still, it can use some of the primitives of impress.js (see \autoref{sec:primitives}) to create meaningful visual relations and create semantic movements.
+While focusing on closeness and movement, it can use some of the primitives of impress.js (see \autoref{sec:primitives}) to create meaningful visual relations and semantic movements.
 These meaningful visual connections are similar to those that prezis often feature.
 The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it.
-The following movements add to the meaning:\\
+The following movements exist:\\
 \vspace{-12pt}
@@
 Apart from going forwards and backwards, we can also move along the y-axis.
-Moving down intuitively means that we dig deeper into a topic and go to the roots whereas moving up means we will be on a higher level.\\
-
-The most interesting movement might be the rotations.
+Moving down intuitively means that we dig deeper into a topic and go to the roots of a problem, whereas moving back up means we will be on a higher level.\\
+
+The most interesting movement is the rotations.
 It should be briefly mentioned that too much rotation leads to seasickness in users, as anyone who has seen a bad prezi can attest to.
-These are generally rotations around the x-axis that rotate more than 20\degree, therefore our rotations are not affected.
-Instead of causing seasickness, our rotations aim to give the viewer the feeling that they are entering a topic and a different storyline.
-They come with a change of perspective which is underlined by the 3D transformation that the user sees.
+These are generally rotations around the x-axis that rotate more than 20\degree.
+Since we only rotate around the y-axis, our rotations are not affected.
+Instead of causing seasickness, our rotations aim to give the viewer the feeling of entering a topic and a different storyline.
+Thus entering a different topic comes with a change of perspective which is underlined by the 3D transformation that the user sees.
 Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.\\
@@
 The important addition is more obvious when regarding the presentation from a birds perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}.
-The value in these presentation is that through these overviews, dependencies become identifiable.
-More importantly they become accessible and allow viewers to go on small guided tours or small excursions into \textit{course-ancient} topics giving users the flexibility to choose their own path while going through the presentation.
+The value in these presentations is that through these overviews, dependencies become identifiable.
+More importantly this means that for Annie, dependencies become accessible and allow her to go on small guided tours or small excursions into \textit{course-ancient} topics giving her the flexibility to choose her own path while going through the presentation.
 
@@
 
-Even though an evaluation is not fully possible given the limited time frame, the next subsections will attempt to evaluate the created system and the created presentations as well as their shortcomings.
+Even though an evaluation is not fully possible given the limited time frame, we will attempt to evaluate the created system and the created presentations as well as their shortcomings.
 Afterwards we will briefly look at future work and possible extensions to our system.\\
 
-\begin{wrapfigure}{l}{0.4\textwidth}
+\begin{wrapfigure}{l}{0.35\textwidth}
 \vspace{-28pt}
@@
   \fbox{
-      \includegraphics[width=0.37\textwidth]{assets/final/initialIdea}
+      \includegraphics[width=0.33\textwidth]{assets/final/initialIdea}
     }
@@
 Systematically, the knowledge presentation system \sys that was developed allows for the creation of a clearly structured relational presentation from a given annotated document which fulfills the goal of this project.
-It does so in a very timely manner.
-In the starting phase of this research, I imagined the created presentations should look a lot more like clustered graphs such as in \autoref{fig:initialIdea}.
+It does so in a very timely manner within seconds.
+In the starting phase of this research, the created presentations were supposed to look a lot more like clustered graphs such as \autoref{fig:initialIdea}.
 Possibly with nodes that are close if they are semantically close and the size of the nodes reflecting the importance of the node.
-While implementing the system, I not only found that such an implementation would be very difficult but also that it would likely confuse the potential user.\\
+While implementing the system, it not only became obvious that such an implementation would be very difficult but also that it would likely confuse our persona, Annie.\\
 
 When using Prezi, it is a human being that can creatively think of links and therefore make more graphical presentations.
-Due to the fact that we built a system that only has limited intelligence, we end up with a far more structured presentation.
-However, considering that the goal of the created presentation is to allow users to intuitively understand dependencies and to allow them to deviate from the primary narrative path to enter the level of one of the dependencies and follow its narrative path for a while, it became obvious that a simple structure for this presentation was even preferable.\\
-
-After having considere the systematic aspects, let us now look at the cognitive aspects.
+Due to the fact that our system only has limited intelligence, we end up with a far more structured presentation.
+However, considering that the goal of the created presentation is to allow users to intuitively understand dependencies and to allow them to deviate from the primary narrative path to enter the level of one of the dependencies and follow its narrative path for a while, it became obvious that a simple structure for this presentation is even preferable.\\
+
+After having considered the systematic aspects, let us now look at the cognitive aspects.
 Cognitively, we explored a part of the field of information systems.
@@
 I strongly believe that the created system \sys adds value to presentation and has the power to facilitate and improve knowledge transfer due to some reasons that were already shown in the \autoref{sec:relatedworks}.
-These sources argued that the linking of learning materials is useful for the user and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.\\
-
-\begin{wrapfigure}{l}{0.45\textwidth}
+These sources argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.\\
+
+\begin{wrapfigure}{l}{0.35\textwidth}
 \vspace{-28pt}
@@
   \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
-      \includegraphics[width=0.42\textwidth]{assets/final/ExamplePathTriangle}
+      \includegraphics[width=0.33\textwidth]{assets/final/ExamplePathTriangle}
     } }
@@
   \label{fig:pathExample}
-\vspace{-24pt}
+\vspace{-40pt}
   \end{center}
@@
 Since a qualitative analysis was unfortunately not possible in this time frame, we can only make an educated guess at the usefulness.
-To strengthen these educated guesses, we will look at the potential path a user could take through the presentation we created by examining \autoref{fig:pathExample}.\\
-
-In the book \textit{OMDoc - An Open Markup Format for Mathematical Documents} \cite{URL:omdocspec}, a didactic figure called the straw-man theory is introduced as an example for a naïve reduced approximation of the real theory that aims to show an example to explain why this approximation does not work.
+To strengthen this educated guess, we will look at the potential path a user could take through the presentation we created by examining \autoref{fig:pathExample}.\\
+
+In the book \textit{OMDoc - An Open Markup Format for Mathematical Documents} \cite{URL:omdocspec}, a didactic figure called the straw-man theory is introduced as an example for a na\"{i}ve reduced approximation of the real theory that aims to show an example to explain why said approximation does not work.
 Our system is not sophisticated enough to examine these structures on its own and figure out which information is best to be shown.
 Instead, \sys simply finds where the dependent information has been taught before and reuses the order in which it was taught before.
-In essence, our system heavily relies on sensible input.\\
-
-Given this sensible input we offer the user digressions, where the user can go back to a different topic and follow its narrative path for a while.
+Subsequently, our system heavily relies on sensible input.\\
+
+Given this sensible input our persona, Annie can make use of digressions, where she can go back to a different topic and follow its narrative path for a while.
 An example for this is highlighted with a blue triangle in \autoref{fig:pathExample}.
-These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to what I call relational presentations.
+These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.
 

### 2015-05-10 Thesis.tex
just the conclusion

@@
   \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo}
+      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}
     } 
@@
   \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
+      \includegraphics[width=0.87\textwidth]{assets/final/fullPresentation2}
     } 
@@
 By improving the creation user interface and allowing for users to choose their own designs, it becomes more easy to use and more attractive for users.
-Adding an editor would make this much more user friendly for creators as well.
+Adding an editor would make this more user friendly for creators as well.
 To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\
@@
 Possibly the system could even suggest dependencies.
-As an example, I could very well envision a biology presentation that explains Photosynthesis and allows the attentive student to catch up on processes that transform ADP to ATP.\\
+As an example, I could very well envision a biology presentation that explains photosynthesis and allows the attentive student to catch up on dependencies such as the process that transforms ADP to ATP.\\
 
@@
 
-This whole research project would also benefit from machine learning which could allow us to make smart offers of likely dependencies.
+This whole research project might also benefit from machine learning which could allow us to make smart offers of likely dependencies.
 On an individual basis we could use it to learn what the user knows and what the user does not know.
 Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn.
-Combining machine learning with the identification of more didactic paths or figures within the data could further improve knowledge transfer.
+Combining machine learning with the identification of more didactic paths or figures within the data such as the example in \autoref{fig:pathExample} could further improve knowledge transfer.
 

### 2015-05-10 Thesis.tex
done?

@@
 
-This relational presentation combines spatial narrative with information about the relations between different pieces of information.
+This relational presentation combines spatial narrative with information about the relations between different pieces of information into a visual information graph.
 In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation.
@@
 
-Not just Annie has an easier way of going through the presentation on her own, Annie's teacher now has a tool that allows her to use her normal lecture material in a more interactive way.
-Thus when the teacher realizes that the students need to revise previous material, the teacher can easily go to that material and provide them with a good learning experience.
+The benefits are not just for Annie when she is going through the presentation on her own, though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way.
+Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience.
 This facilitates knowledge transfer and allows for a more engaging and interactive education.\\
@@
 In the introduction, I introduced the metaphor of hiking up a mountain which can be done in different ways.
-The type of presentations this research built allow for a lot of different paths to reach a learning goal that fit individuals and allow for more interactivity.\\
-
-The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits.\\
+The type of presentations this research built allows for a lot of different paths to reach a learning goal.
+The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.\\
 

### 2015-05-10 Thesis.tex
prettier :)

@@
 We can make it possible to link content that logically belongs together, in other words, content that is semantically close.
-Through the linking of content it can become possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that will allow the audience to take small detours and ultimately make the most out of the presentation.\\
+Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.\\
 
@@
 
-Along the way of helping Annie, we will explore the question of how to create a flexible presentation which allows Annie to choose her own path to explore the context of a topic as needed by browsing through related resources seamlessly.
+Along the way of helping Annie, we will explore the question of how to create a flexible presentation, which allows Annie to choose her own path to explore the context of a topic by browsing through related resources as needed.
 To create this presentation a tool for automatic contextual visualization of information will be introduced.
@@
 It is left to the reader to think about examples in his or her own life where he or she would have appreciated having this type of flexible presentations.
-There are many stories such as Annie's in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be by following a straight or a curvy path.
+There are many stories such as Annie's in real life and it is therefore important to provide information with its context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be by following a straight or a curvy path.
 
@@
     } 
-\vspace{-20pt}
+\vspace{-8pt}
   \caption{Visualization of Dependencies}
@@
 To begin with, let us examine the choice of layout.
-The goal of this presentation is to have all the information the Pythagorean theorem depends on easily accessible so that Annie can reach \textit{course-ancient} information easily.
+The goal of this presentation is to have all the information the Pythagorean theorem depends on easily accessible so that Annie can access \textit{course-ancient} information easily.
 The added expressiveness that impress.js offers allowed us to have this in a very structured format.
@@
 
-A prezi, if done right, is generally full of metaphors and meaningful visual connections.
+A prezi, if done correctly, is generally full of metaphors and meaningful visual connections.
 Our tool cannot mimic this creativity as it lacks the capability to abstract on such a high level.
@@
 Thus entering a different topic comes with a change of perspective which is underlined by the 3D transformation that the user sees.
-Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.\\
-
-One might think that this is like a PowerPoint, since PowerPoint offers similar animations to switch slides.
-The important addition is more obvious when regarding the presentation from a birds perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}.
+Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.
+\footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}}\\
+
+One might think that this is similar to a PowerPoint presentation, since PowerPoint offers similar animations to switch slides.
+The important addition is more obvious when regarding the presentation from a bird's eye perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}.
 The value in these presentations is that through these overviews, dependencies become identifiable.
@@
 
-Even though an evaluation is not fully possible given the limited time frame, we will attempt to evaluate the created system and the created presentations as well as their shortcomings.
-Afterwards we will briefly look at future work and possible extensions to our system.\\
+Even though an evaluation is not fully possible given the limited time frame, we will attempt to evaluate the created system and presentations as well as their shortcomings.
+Afterwards we will look at future work and possible extensions to our system.\\
 
@@
   \label{fig:initialIdea}
-\vspace{-24pt}
+\vspace{-34pt}
   \end{center}
@@
 
-When using Prezi, it is a human being that can creatively think of links and therefore make more graphical presentations.
+When using Prezi, human beings can creatively think of links and therefore make more graphical presentations.
 Due to the fact that our system only has limited intelligence, we end up with a far more structured presentation.
-However, considering that the goal of the created presentation is to allow users to intuitively understand dependencies and to allow them to deviate from the primary narrative path to enter the level of one of the dependencies and follow its narrative path for a while, it became obvious that a simple structure for this presentation is even preferable.\\
-
-After having considered the systematic aspects, let us now look at the cognitive aspects.
+However, considering that the goal of the created presentation is to allow users to intuitively understand dependencies and to allow them to deviate from the primary narrative path to enter the level of one of the dependencies and follow its narrative path for a while, it became obvious that a simple structure for this presentation is actually preferable.\\
+
+After having considered the systematic aspects, let us now look at the other aspects.
 Cognitively, we explored a part of the field of information systems.
@@
 I strongly believe that the created system \sys adds value to presentation and has the power to facilitate and improve knowledge transfer due to some reasons that were already shown in the \autoref{sec:relatedworks}.
-These sources argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.\\
-
-\begin{wrapfigure}{l}{0.35\textwidth}
+There some argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.\\
+
+\begin{wrapfigure}{l}{0.3\textwidth}
 \vspace{-28pt}
@@
   \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
-      \includegraphics[width=0.33\textwidth]{assets/final/ExamplePathTriangle}
+      \includegraphics[width=0.28\textwidth]{assets/final/ExamplePathTriangle}
     } }
@@
 This section lists some ideas on future work regarding this topic and the created system \sys.
-Before embarking on improvements of the system, a qualitative and quantitative analysis of the produced visual presentations should be conducted to confirm that this system helps users.
+Before embarking on improvements of the system, a qualitative and quantitative analysis of the produced visual presentations should be conducted to confirm that this system aids users in understanding content better.
 For the quantitative analysis it would be ideal to take a course that has already been taught using a more traditional approach to presentations which can then function as a control group.
-After teaching the whole course using the newly created presentation, the data of how the students in this test group performed can be compared with the gathered data from how students used to perform in the course.
+After teaching the whole course using the newly created presentations, the data of how the students in this test group performed can be compared with the gathered data from how students used to perform in the course.
 For a qualitative analysis, students who have been subject to the use of and who have actively used the new presentation could be interviewed.\\
@@
 Apart from an analysis to evaluate the effectiveness of the created presentations, the whole system could be made more user friendly for both the creator and the users of the presentations.
-By improving the creation user interface and allowing for users to choose their own designs, it becomes more easy to use and more attractive for users.
-Adding an editor would make this more user friendly for creators as well.
+By improving the creation user interface and allowing for users to choose their own designs, it becomes easier to use and more attractive for users.
+Adding an editor would make \sys more user friendly for creators as well.
 To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\
@@
 
-Overall it is even thinkable to create a different version of this system that could be made available to common users outside this research domain.
+Overall it is even thinkable to create a different version of this system that could be made available to general users outside this research domain.
 The idea would be to allow users to add slides in an editor and to allow them to add dependencies themselves.
@@
 
-This whole research project might also benefit from machine learning which could allow us to make smart offers of likely dependencies.
+This whole research project might also benefit from machine learning which could allow us to suggest likely dependencies.
 On an individual basis we could use it to learn what the user knows and what the user does not know.

### 2015-05-26 Paper.tex
first cuts

--- 2015-05-10 Thesis.tex
@@
 \fancyfoot{} % Blank out the default footer
-\fancyhead[C]{Naomi Pentrel $\cdot$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\cdot$ \today} % Custom header text
+\fancyhead[C]{\href{mailto:npentrel@gmail.com}{Naomi Pentrel} $\cdot$ \href{mailto:m.kohlhase@jacobs-university.de}{Michael Kohlhase} $\cdot$ \today} % Custom header text
 \fancyfoot[RO,LE]{\thepage} % Custom footer text
@@
 
+\definecolor{bg}{rgb}{0.90,0.90,0.90}
+
 %\doublespacing
@@
     \huge
-    \textbf{The Combination of Spatial Narrative and Semantic Closeness to Derive Visualizations of Information Graphs}
+    \textbf{Relational Presentation Using Semantic Closeness}\\
+    \vspace*{2mm}
+	\Large
+	\textbf{-\\Spatial Narrative for Mathematical Content}
   \end{center}
-  \vspace*{4mm}
+  \vspace*{2mm}
   \begin{center}
@@
     \Large
-    \textbf{Naomi Pentrel}
+    \textbf{Naomi Pentrel\\ \& \\ Prof. Dr. Michael Kohlhase}
   \end{center}
-  \vspace*{20mm}
+  \vspace*{4mm}
   \begin{center}
     \large
-    Bachelor Thesis in Computer Science
   \end{center}
@@
     \begin{tabular}{l}      
-
-      \hline
-      Prof. Dr. Michael Kohlhase \\
       \\
@@
   \end{flushright}
-  \vspace*{8mm}
+  \vspace*{0mm}
   \begin{flushleft}
@@
   \end{center}
-
-\newpage
-\noindent
-With my signature, I certify that this thesis has been written by me using only the indicated resources and materials.
-Where I have presented data and results, the data and results are complete, genuine, and have been obtained by me unless otherwise acknowledged; where my results derive from computer programs, these computer programs have been written by me unless otherwise acknowledged.
-I further confirm that this thesis has not been submitted, either in part or as a whole, for any other academic degree at this or another institution.
-
-  \vspace{20mm}
-
-    \includegraphics[scale=0.2]{assets/Signature}
- \hfill Bremen, \today
 
@@
 Visualization of knowledge is important to foster learning.
-To optimize the visualization of information and its interdependencies, we focus on identifying ways to present information without loosing context.
+Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts.
+To optimize the visualization of information and its interdependencies, a way to present information without loosing context is necessary.
 The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
@@
 
-Taking the typical lecture as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics.
-When a new topic is introduced it would be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\
+Taking the typical Mathematics lecture as an example, it is often the case that students have different backgrounds.
+Some might have learned linear algebra while other have not yet.
+Additionally, especially towards the end of the semester, students often have difficulties remembering earlier topics.
+When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\
 
-The OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents.
-Using OMDoc, the implemented system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories.
+The OMDoc (OpenMathematical Documents) format is a content markup scheme for mathematical documents.
+Using OMDoc, the proposed system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on by taking a small detour through those topics, should they need to refresh their memories.
 Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning.
@@
 \newpage
-\tableofcontents
+%\tableofcontents
 
-\clearpage
+%\clearpage
 
-\newpage
-\thispagestyle{empty}
-\topskip0pt
-\vspace*{\fill}
-\begin{center}
-\textsc{Aut viam inveniam aut faciam}\\
+%\newpage
+%\thispagestyle{empty}
+%\topskip0pt
+%\vspace*{\fill}
+%\begin{center}
+%\textsc{Aut viam inveniam aut faciam}\\
 
-\vspace*{1cm}
+%\vspace*{1cm}
 
-\textit{(I'll either find a path or make one)}\\
+%\textit{(I'll either find a path or make one)}\\
 
-\vspace*{4cm}
+%\vspace*{4cm}
 
-\centering
+%\centering
 
-\begin{quoting}
-\begin{center}
-\noindent
-\textit{At this point, I would like to thank Prof.
-Dr.
-Michael Kohlhase for being an inspiring and helpful supervisor.
-Additionally, I would like to thank Mihnea Iancu and Tom Wiesing for aiding me in my research project.\\}
-\end{center}
-\end{quoting}
+%\vspace*{\fill}
+%\end{center}
 
-\vspace*{\fill}
-\end{center}
-
-\newpage
+%\newpage
 \pagenumbering{arabic}
@@
 Both paths lead to the goal.
-Within education, there is normally only one straight path.
-That is true for the narration in books, movies, and also traditional slide-based presentations.
-This has not changed in decades.
+Within Mathematics classes, there is normally only one straight path and this has not changed in decades.
 With the advancement of technology, we are however able to change the way presentations and their narratives work.
@@
 Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.\\
-
-This idea of linking content is not new.
-When Tim Berners-Lee laid out his Semantic Web Roadmap \cite{BernersLee:tsw98}, its intention was to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources.
-Both the semantic web and the research at hand strive to connect pieces of information through adding context and thus to not just provide information, but rather knowledge.
-Within presentations, the intention is to present information in an interconnected way that provides context and thus facilitates understanding and learning.\\
 
@@
 As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up.
+However, especially in mathematics, students would benefit from the possibility to take detours through half-forgotten topics.
 By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.\\
@@
 
-\section{Related Work}
-\label{sec:relatedworks}
-
-When searching for related work there is little to be found.
-Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}.
-For this purpose, systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}.
-Some of these systems use temporal information \cite{DBLP:dblp_journals/isci/ChungS97} to show multiple resources in sync as they appeared in the lecture.
-However, while this approach also aims at improving the learning experience, it does not in any way link content semantically based on dependencies or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\
-
-Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}.
-The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects.
-While the research at hand also intends to show the relation between pieces of information, it does it on a different level.
-For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map.
-This research, on the other hand, will focus on exactly that, i.e.
-dependencies and the creation of interactive presentations.\\
-
-There has also been research focusing on guided tours in mathematics \cite{SieBen:acgap00}.
-This creates guided tours on topics depending on the background of the user.
-While working towards the same goal, namely to improve knowledge transfer, it differs from this work in its presentation format.
-While Siekmann et al., focused on one topic and displaying it differently to users with different backgrounds, this research will show the topics of a whole course while allowing to see dependencies and while allowing to diverge from the prescribed presentation path.\\
-
-Adding on to the research about guided tours in mathematics, there has also been research on semantic document navigation \cite{Koh:NavigationInMathDocs2012}.
-It demonstrates the need for assistance in form of navigation support for the reading of mathematical documents by creating a system that allows for semantic navigation in Excel spreadsheets.
-This research underlines the importance of a system that allows users like Annie to navigate information according to dependencies.
-
-\section{Preliminaries}
-\label{sec:preliminaries}
-
-In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how the presentation can be improved to transfer knowledge more effectively.
-
-\subsection{Terminology}
-\label{sec:terminology}
-
-Before discussing the buzzword knowledge transfer further, we will first engage in the conceptualization of the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\
-
-The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things".
-Recalling \autoref{fig:slideP} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}.
-For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association".
-This \textit{association} is of special importance for the current project.
-We will define it as knowledge that is made up out of several pieces of information that are connected.
-In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \autoref{fig:deppyg} above).\\
-
-According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning".
-Context can be easily explained with the example of Annie learning the Pythagorean theorem.
-The \textit{information} about the calculation of the length of the third side of the triangle is only helpful for Annie within the \textit{context} of the pieces of \textit{information} this depends on.
-Without this \textit{context}, Annie cannot understand the theorem.
-Figure \ref{fig:deppyg} above illustrates the context by showing the dependencies of the theorem, i.e.
-calculating squares, area calculation, triangles, and right angles.
-It represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}.
-The relatedness between the relevant concepts can also be imagined as a network.
-We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.
-
-\subsection{OMDoc}
-\label{sec:OMDoc}
-
-OMDoc \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents.
-As such it is a semi-formal domain ontology.
-An ontology provides the framework for creating a semantic structure.
-It formally describes concepts within a specified area.
-A semi-formal ontology \cite{Sheth:npentrel14} is an ontology where formality of semantics is not a given.
-The semi-formal ontology can consist of partial or incomplete knowledge.
-\\
-
-If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in various ways.
-This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts.
-The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations.
-This elevates the net of separate pieces of information that are stored individually to a semantic representation and can be used to improve knowledge transfer.
-
-\subsection{Status of Information within the (Dis)Course}
-\label{sec:infostatus}
-
-In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
-Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information.
-\textit{Familiar/ old} information is shared by speaker and addressee, i.e.
-it is in the intersection of knowledge of student and teacher.
-\textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
-In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
-
-\begin{center}
-\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}\\
-\end{center}
-
-In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus is introduced.
-In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
-These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}.
-The accessibility depends on the relative \textit{newness}, i.e.
-recency of mention, of this information.\\
-
-These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
-In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}.
-Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
-We will additionally introduce a third modus for information called \textit{course-ancient}.
-This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e.
-\textit{course-ancient}.\\
-
-Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
-The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
-The information about squares which Annie still remembers is \textit{course-old}.
-Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
-
-\subsection{Primitives}
-\label{sec:primitives}
-
-Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness.
-Primitives are the different elements of representation.
-In terms of evaluation it is important to have intuitive primitive elements.
-The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}.
-The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\
-
-Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter.
-When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes.
-Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is.
-In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate.
-Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to \autoref{fig:deppyg}).
-These structural primitives and semantic primitives provide the basics that information graphs can be built on.\\
-
-For impress.js, the primitive elements are text, images, slides, and the visual relation between the different slide-like structures.
-The slides can be mapped directly to the nodes/concepts which graphs use.
-Text and images are taken for granted within the slides.
-Similarly, the visual relation between different slides is very much like the relations between nodes.
-However, the relations can be much more expressive within impress.js.\\
-
-These relations or connections between different slides do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another.
-As such the temporal associations show the path that a traditional lecture would take.
-The dependencies that are visualized around each slide, mainly above or below the slide, allow for additional interactivity.
-
-\subsection{Spatial Narrative}
-\label{sec:spatialnarrative}
-
-The development of presentation tools like impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative.
-Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}.
-When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.\\
-
-The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexible \textit{guided tours} based on the thematically and narrative linking of a set of locations within an area into a \textit{spatial narrative}" \cite{SpatialNarratives:npentrel14}.
-Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\
-
-The benefit of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information.
-By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter.
-That is the case because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \cite{Storytelling:npentrel14}.\\
-
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-28pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.43 \textwidth]{assets/final/arrowsPyth}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Connection of Slide}
-  \label{fig:arrowspyg}
-\vspace{-10pt}
-\end{wrapfigure}
-
-In this research we will use this knowledge to form an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
-For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
-It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in an instant.
-
-\subsection{impress.js}
-\label{sec:Impressjs}
-
-For the implementation of \sys, impress.js will be used, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations.
-The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka.
-It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers.
-The presentation data is entered in the HTML file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide.
-The \texttt{data-x} and \texttt{data-y} attributes change the position of the element according to the normal x- and y-axes.
-The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
-\definecolor{bg}{rgb}{0.90,0.90,0.90}
-
-\begin{wrapfigure}{r}{\textwidth}
-\vspace{-0pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-<div class="step" data-x="1000" data-y="0">
-  Slide Content
-</div>
-\end{minted}
-\vspace{-8pt}
-  \caption{Code Snippet to Create a Slide}
-  \label{fig:SSlide}
-  \vspace{12pt}
-\end{wrapfigure}
-
-\begin{wrapfigure}{r}{0.3\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.28 \textwidth]{assets/rotate}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Rotations \cite{Rotations:npentrel14}}
-  \label{fig:Rotate}
-\vspace{-10pt}
-\end{wrapfigure}
-
-Apart from these basic attributes, impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}.
-As shown in \autoref{fig:Rotate} this allows the presentation to go into the third dimension.\\
-
-In the following code snippets, a few other basic functionalities are illustrated \cite{andismith:npentrel15}.
-The opacity attribute allows us to discriminate between active and inactive slides which allows us to hide content so as not show too much information to a user at once.
-Adding an overview can be accomplished with the last part of the CSS snippet and the HTML snippet below that.
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{0pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-.step { opacity: 0.2; }
-.step.active { opacity: 1; }
-.step-overview .step { opacity: 1; cursor: pointer; }
-\end{minted}
-\vspace{-8pt}
-  \caption{Code Snippet to Show and Hide Content}
-  \label{fig:SSlide}
-  \vspace{20pt}
-\end{wrapfigure}
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-10pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-<div id="overview" class="step" data-x="8000" data-y="1000" data-scale="10">
-</div>
-\end{minted}
-\vspace{-11pt}
-  \caption{Code Snippet for an Overview}
-  \label{fig:SSlide}
-  \vspace{12pt}
-\end{wrapfigure}
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-
-To link back to a slide, slides are accessible via IDs. The slide with the ID \texttt{conclusion} will thus be accessible by appending \texttt{\#/conclusion} to the end of the URL.
-
 \section{Towards a More Effective Presentation Format}
@@
 
-Building on the preliminaries, we will now commence the journey towards building a more effective presentation format to improve knowledge transfer by allowing flexibility in presentations.
-To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.\\
+We will now commence the journey towards building a more effective presentation format to improve knowledge transfer in Mathematics by allowing flexibility in presentations.
+In the following we will assume the reader is familiar with OMDoc \cite{Kohlhase:OMDoc1.2} and with the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.
+\\
 
@@
 
-To bring the presentation to life the library impress.js which was introduced in \autoref{sec:Impressjs} is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh.
-An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and \autoref{sec:Impressjs}.
+To bring the presentation to life the library impress.js is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh.
+An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.
 The library impress.js works in all modern browsers that support CSS 3D transforms; some older and mobile browsers are, however, not able to display the created presentations properly.
+
+\subsection{Status of Information within the (Dis)Course}
+\label{sec:infostatus}
+\ednote{not sure where to put this}
+In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
+Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information.
+\textit{Familiar/ old} information is shared by speaker and addressee, i.e.
+it is in the intersection of knowledge of student and teacher.
+\textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
+In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
+
+\begin{center}
+\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}\\
+\end{center}
+
+In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus is introduced.
+In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
+These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}.
+The accessibility depends on the relative \textit{newness}, i.e.
+recency of mention, of this information.\\
+
+These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
+In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}.
+Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
+We will additionally introduce a third modus for information called \textit{course-ancient}.
+This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e.
+\textit{course-ancient}.\\
+
+Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
+The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
+The information about squares which Annie still remembers is \textit{course-old}.
+Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
+
+\ednote{For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
+It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in an instant.}
 
@@
 Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.
-\footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}}\\
+\footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}\\
 
@@
 
-\section{Future Work and Possible Extensions}
-
-This section lists some ideas on future work regarding this topic and the created system \sys.
-Before embarking on improvements of the system, a qualitative and quantitative analysis of the produced visual presentations should be conducted to confirm that this system aids users in understanding content better.
-For the quantitative analysis it would be ideal to take a course that has already been taught using a more traditional approach to presentations which can then function as a control group.
-After teaching the whole course using the newly created presentations, the data of how the students in this test group performed can be compared with the gathered data from how students used to perform in the course.
-For a qualitative analysis, students who have been subject to the use of and who have actively used the new presentation could be interviewed.\\
-
-Apart from an analysis to evaluate the effectiveness of the created presentations, the whole system could be made more user friendly for both the creator and the users of the presentations.
-By improving the creation user interface and allowing for users to choose their own designs, it becomes easier to use and more attractive for users.
-Adding an editor would make \sys more user friendly for creators as well.
-To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\
-
-In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make use of relative size to additionally convey importance using impress.js' \texttt{data-scale} attribute.
-This would further add more semantic meaning to the slides.
-Additionally, one could think about adding a progress bar by using the work of Matthias Bilger \cite{bilger:npentrel15} to motivate users to continue.\\
-
-Overall it is even thinkable to create a different version of this system that could be made available to general users outside this research domain.
-The idea would be to allow users to add slides in an editor and to allow them to add dependencies themselves.
-Possibly the system could even suggest dependencies.
-As an example, I could very well envision a biology presentation that explains photosynthesis and allows the attentive student to catch up on dependencies such as the process that transforms ADP to ATP.\\
-
-In terms of improving content, it would be interesting to not just provide paths to dependencies or prerequisite knowledge but also to knowledge that builds on the current topic.
-That way students that learn fast can already explore higher levels.\\
-
-This whole research project might also benefit from machine learning which could allow us to suggest likely dependencies.
-On an individual basis we could use it to learn what the user knows and what the user does not know.
-Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn.
-Combining machine learning with the identification of more didactic paths or figures within the data such as the example in \autoref{fig:pathExample} could further improve knowledge transfer.
-
 \section{Conclusion}
@@
 In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation.
-This allows Annie choose her own path in going through the presentation while seamlessly looking up related information.\\
+This allows Annie to choose her own path while going through the presentation and seamlessly looking up related information.\\
 
-The benefits are not just for Annie when she is going through the presentation on her own, though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way.
+The benefits are not just for Annie when she is going through the presentation on her own though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way.
 Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience.
@@
 
+To conclude, I leave the reader to ponder how much education would change if we could allow individuals to learn at their own pace following their own path and easily learning course-ancient information in guided tours.
+\sys definitely helped Annie and I strongly believe that the mentioned benefits would benefit all of us, whether in the role of the presenter or in the role of the viewer.
+
 \newpage

### 2015-05-27 Paper.tex
massive cuts

@@
 \usepackage{tocloft}
-\renewcommand*{\figureautorefname}{figure}
+\renewcommand*{\figureautorefname}{Figure}
 \def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
@@
 Learning new things is a bit like hiking up a mountain.
-If you have ever gone hiking, you know that it is relatively hard to hike up a steep mountain directly as shown in \autoref{fig:straight}.
+If you have ever gone hiking, you know that it is hard to hike up a steep mountain directly as shown in \autoref{fig:straight}.
 Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}.
-Both paths lead to the goal.
+Both paths lead to the goal though.
 Within Mathematics classes, there is normally only one straight path and this has not changed in decades.
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
-\vspace{-28pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.38 \textwidth]{assets/final/PythDep}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Information Dependency of the Pythagorean Theorem}
-  \label{fig:deppyg}
-\vspace{-10pt}
-\end{wrapfigure}
-
-Annie's example shows the dependencies of different pieces of information (see \autoref{fig:deppyg}), i.e.
+Annie's example shows the dependencies of different pieces of information, i.e.
 the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles.
 As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up.
-However, especially in mathematics, students would benefit from the possibility to take detours through half-forgotten topics.
+However, especially in mathematics, students would benefit from the possibility to take detours through half-forgotten topics as topics are often closely linked and interdependent.
 By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.\\
@@
 To achieve our goal to help Annie, we will set out to create a relational presentation system \sys to visually present information and its context which allows Annie to interact with the content and choose a path that matches her knowledge base.
-For this we will be using the OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) format which, given an annotated set of documents, will provide us with the necessary XHTML-representation and PDF-representation of the information \cite{Kohlhase:OMDoc1.2}.
-It will also allow us to extract information about the semantic closeness of different pieces of information.\\
-
-This information alone would tell Annie where she might find the information she seeks but it will only serve as a starting point.
-In face, this information will be used to visualize the dependencies of the information in a simple but effective approach using the presentation framework impress.js \cite{JSImpress:npentrel14}.
 The visualization of the information will make use of spatial narrative to connect information in a logical way.
@@
 Through the usage of both spatial narrative and semantic closeness of information it will connect information logically.
-The end product will be a presentations which allow Annie to choose her own path by interacting with the presentation to seamlessly explore related topics and brush up on half-forgotten topics like right angles.\\
-
-It is left to the reader to think about examples in his or her own life where he or she would have appreciated having this type of flexible presentations.
+The end product will be a presentations which allow Annie to choose her own path by interacting with the presentation to seamlessly explore related topics and brush up on half-forgotten topics like right angles.
 There are many stories such as Annie's in real life and it is therefore important to provide information with its context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be by following a straight or a curvy path.
@@
 
-For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added (see \autoref{sec:Impressjs}).
+For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added.
 The details of this process will be explained in subsection \ref{sec:narrativePaths}, \ref{sec:orderedInfoGraphs}, and \ref{sec:levels}.
@@
 The design of the template is based on a presentation by S.
-Wolf \cite{Wolf:npentrel15}.\\
-
+Wolf \cite{Wolf:npentrel15}.
 To bring the presentation to life the library impress.js is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh.
 An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.
-The library impress.js works in all modern browsers that support CSS 3D transforms; some older and mobile browsers are, however, not able to display the created presentations properly.
 
@@
 \label{sec:infostatus}
-\ednote{not sure where to put this}
 In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
@@
 
-\ednote{For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}).
-It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in an instant.}
-
 \subsection{Narrative Paths}
@@
 The information that OMDoc provides us with could also be simply visualized as a tree of information.
-But this would not be very engaging and it would be hard for a person to process.
+However, this would not be very engaging and it would be hard for a person to process.
 Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-0pt}
+\vspace{-35pt}
   \begin{center}
   \fbox{
-      \includegraphics[width=0.87\textwidth]{assets/final/inclusionGraphPythagorean}
+      \includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}
     } 
-\vspace{-8pt}
+\vspace{-0pt}
   \caption{Inclusion Graph for the Pythagorean Theorem}
@@
 
-\begin{wrapfigure}{l}{0.3\textwidth}
-\vspace{-28pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.28\textwidth]{assets/final/inclusionGraphCS}
-    } 
-\vspace{-20pt}
-  \caption{Inclusion Graph for GenCS}
-  \label{fig:inclusionGraphGenCS}
-\vspace{-24pt}
-  \end{center}
+\begin{wrapfigure}{l}{\textwidth}
+\vspace{-50pt}
 \end{wrapfigure}
@@
 For the explanation of the Pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}.
-The graph for a whole course like the General Computer Science course (GenCS) at Jacobs University Bremen \cite{Kohlhase:GenCSII:base} is too big to be shown properly (see \autoref{fig:inclusionGraphGenCS}).\\
-
-The retrieved order is the intended narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation.
-To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}.
-This code then creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\
-
-\begin{wrapfigure}{r}{\textwidth}
-\vspace{-20pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-<div class="step" data-x="1250" data-y="0"> ... </div>
-<div class="step" data-x="2500" data-y="0"> ... </div>
-\end{minted}
-\vspace{-8pt}
-  \caption{Code Snippet for a Narrative Path}
-  \label{fig:narrativePathCode}
-  \vspace{12pt}
-\end{wrapfigure}
+We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation.
+To create this primary narrative path we need to add several slides with increasing x-coordinates as portrayed in \autoref{fig:primaryNarrativePath}.\\
 
@@
 The primary narrative path, formed by a horizontal stream of slides, is the traditional path a presenter normally uses when preparing a PowerPoint presentation.
-This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
+Thus it contains also temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
 This temporal information is what we extracted from the \stex files as the order in which the slides (or the information on the slides) should appear.\\
 
-This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic.
-These narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
+Temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic.
+These narrative paths are similar to short guided tours in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
 Going back to our example of Annie, an example of a subsection would be the information concerning angles.
-In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own.
-These occur on different levels as explained in \autoref{sec:levels} and are based on the concept of spatial parratives (see \autoref{sec:spatialnarrative}).
+In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own which occur on different levels as explained in \autoref{sec:levels}.
 
@@
 
-As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.
-The general format of one relation can be seen in \autoref{fig:reldatacode} (lines 1-2).
-A specific example showing some of the dependencies for the Pythagorean theorem example can be seen in lines 4-11.\\
-
-\begin{wrapfigure}{r}{\textwidth}
-\vspace{-0pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-theory path/to/file?theory_name
-Includes path/to/file path/to/dependent/file?theory_name
-
-theory 
-pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
-Includes 
-pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
-pythagoreantheorem/measurements/right_angle.omdoc?right_angle
-Includes 
-pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
-pythagoreantheorem/measurements/area.omdoc?area
-\end{minted}
-\vspace{-5pt}
-  \caption[Caption for LOF]{Code Snippet of Relational Data \footnotemark}
-  \label{fig:reldatacode}
-  \vspace{12pt}
-\end{wrapfigure}
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-
-\footnotetext{All the above paths were shortened by "http://mathhub.info/MiKoMH/" to maintain readability.}
-
-The system \sys parses the relational data and thus retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
-Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information likely obtained longer ago.\\
+As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.The system \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
+Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.\\
 
@@
 whether there are dependencies, for that slide.
-If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).
-This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value (see \autoref{fig:dependencySnippet}).
-
-\begin{wrapfigure}{r}{\textwidth}
-\vspace{-0pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-<div class="step slide" data-x="8750" data-y="0"> Slide </div>
-<div class="step slide" data-x="8750" data-y="800"> Dependency 1 </div>
-<div class="step slide" data-x="8750" data-y="1600"> Dependency 2 </div>
-\end{minted}
-\vspace{-8pt}
-  \caption{Code Snippet for a Dependency}
-  \label{fig:dependencySnippet}
-  \vspace{12pt}
-\end{wrapfigure}
+If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the choosing of different paths by pressing the right or down key \cite{npentrel:npentrel15}.}
 
@@
     } 
-\vspace{-8pt}
+\vspace{-7pt}
   \caption{Visualization of Dependencies}
   \label{fig:visualDependency}
-\vspace{12pt}
+\vspace{-15pt}
   \end{center}
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
+\vspace{-140pt}
 \end{wrapfigure}
-
-The library impress.js normally does not support having different paths depending on pressing the right or down key.
-Therefore it had to be slightly adapted to handle this behavior.
-As these are implementation details, this will not be further explained here.
-The interested reader is encouraged to look at the code \cite{npentrel:npentrel15} directly.
 
@@
 \begin{wrapfigure}{c}{\textwidth}
-\vspace{-16pt}
+\vspace{-12pt}
   \begin{center}
   \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/levels}
+      \includegraphics[width=0.6\textwidth]{assets/final/levels}
     } 
-\vspace{-20pt}
+\vspace{-0pt}
   \caption{Inclusion Graph with Levels}
   \label{fig:levelsGraph}
-\vspace{0pt}
+\vspace{12pt}
   \end{center}
@@
 
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-70pt}
-\end{wrapfigure}
-
-If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter the respective level.
-The presentation will then continue on that level and show all the slides from that topic in the correct order.
-Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path.
-By adding a way to explore these other levels, the presentation adds more context and allows Annie to understand the subject on a deeper level.
-These modular excursions are included in the presentation in 3D by making use of CSS3-transitions (see \autoref{fig:dependencyLevelSnippet}).
-Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line (see \autoref{fig:visualDependencyDegree}).
-
-\begin{wrapfigure}{r}{\textwidth}
-\vspace{-22pt}
-\begin{minted}[linenos=true, bgcolor=bg]{C}
-<div class="step slide" data-x="8750" data-y="0" data-z="0"
-	data-rotate-y="0"> Slide </div>
-<div class="step slide" data-x="8750" data-y="800" data-z="0" 
-	data-rotate-y="0"> Dependency 1  </div>
-<div class="step slide" data-x="8750" data-y="800" data-z="0" 
-	data-rotate-y="90"> Dependency 1 Continuation 1 </div>
-<div class="step slide" data-x="8750" data-y="800" data-z="1250" 
-	data-rotate-y="90"> Dependency 1 Continuation 2 </div>
-\end{minted}
-\vspace{-8pt}
-  \caption{Code Snippet for a Dependency Level}
-  \label{fig:dependencyLevelSnippet}
-  \vspace{12pt}
-\end{wrapfigure}
-
-\begin{wrapfigure}{c}{1\textwidth}
+\begin{wrapfigure}{l}{0.57\textwidth}
 \vspace{-26pt}
@@
   \fbox{
-      \includegraphics[width=0.65\textwidth]{assets/final/60degree}
+      \includegraphics[width=0.55\textwidth]{assets/final/60degree}
     } 
@@
 
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
+If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter the respective level.
+The presentation will then continue on that level and show all the slides from that topic in the correct order.
+Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path.
+By adding a way to explore these other levels, the presentation adds more context and allows Annie to understand the subject on a deeper level.
+These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
+Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line (see \autoref{fig:visualDependencyDegree}).
 
 \footnotetext{The overlapping slides do not interfere as they are at a 90\degree\ angle.
-Therefore when seeing one slide, the other slide will be visible only from the slide.
+Therefore when seeing one slide, the other slide will be visible only from the side.
 Since a slide is very thin this makes it invisible.}
@@
 The goal of this presentation is to have all the information the Pythagorean theorem depends on easily accessible so that Annie can access \textit{course-ancient} information easily.
-The added expressiveness that impress.js offers allowed us to have this in a very structured format.
-Since Prezi was mentioned in the beginning of this paper as a commercial alternative that was considered for this project, let us examine a sample prezi from afar and outline some differences.\\
-
-\begin{wrapfigure}{l}{0.45\textwidth}
-\vspace{-26pt}
-  \begin{center}
-  \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
-      \includegraphics[width=0.42\textwidth]{assets/final/Storytelling}
-    } }
-\vspace{-20pt}
-  \caption{Prezi Example \cite{npentrel2:npentrel15}}
-  \label{fig:preziExample}
-\vspace{-24pt}
-  \end{center}
-\end{wrapfigure}
-
-A prezi, if done correctly, is generally full of metaphors and meaningful visual connections.
-Our tool cannot mimic this creativity as it lacks the capability to abstract on such a high level.
-Therefore our product is a lot more structured and focused on visualizing relations between content with movement and closeness.
+The added expressiveness that impress.js offers allowed us to have this in a very structured format while focusing on visualizing relations between content with movement and closeness.
 This also serves to keep the resulting presentation simple and easily usable.\\
 
-While focusing on closeness and movement, it can use some of the primitives of impress.js (see \autoref{sec:primitives}) to create meaningful visual relations and semantic movements.
-These meaningful visual connections are similar to those that prezis often feature.
+While focusing on closeness and movement, it creates meaningful visual relations and semantic movements.
 The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it.
@@
 
-The most interesting movement is the rotations.
-It should be briefly mentioned that too much rotation leads to seasickness in users, as anyone who has seen a bad prezi can attest to.
-These are generally rotations around the x-axis that rotate more than 20\degree.
-Since we only rotate around the y-axis, our rotations are not affected.
-Instead of causing seasickness, our rotations aim to give the viewer the feeling of entering a topic and a different storyline.
+The most interesting movement is the rotations which aim to give the viewer the feeling of entering a topic and a different storyline.
 Thus entering a different topic comes with a change of perspective which is underlined by the 3D transformation that the user sees.
@@
 More importantly this means that for Annie, dependencies become accessible and allow her to go on small guided tours or small excursions into \textit{course-ancient} topics giving her the flexibility to choose her own path while going through the presentation.
-
-\section{Evaluation}
-\label{sec:eval}
-
-Even though an evaluation is not fully possible given the limited time frame, we will attempt to evaluate the created system and presentations as well as their shortcomings.
-Afterwards we will look at future work and possible extensions to our system.\\
-
-\begin{wrapfigure}{l}{0.35\textwidth}
-\vspace{-28pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.33\textwidth]{assets/final/initialIdea}
-    }
-\vspace{-20pt}
-  \caption{Initial Presentation Idea}
-  \label{fig:initialIdea}
-\vspace{-34pt}
-  \end{center}
-\end{wrapfigure}
-
-The evaluation conducted in the following part is on the one hand, systematic and, on the other hand, cognitive.
-Systematically, the knowledge presentation system \sys that was developed allows for the creation of a clearly structured relational presentation from a given annotated document which fulfills the goal of this project.
-It does so in a very timely manner within seconds.
-In the starting phase of this research, the created presentations were supposed to look a lot more like clustered graphs such as \autoref{fig:initialIdea}.
-Possibly with nodes that are close if they are semantically close and the size of the nodes reflecting the importance of the node.
-While implementing the system, it not only became obvious that such an implementation would be very difficult but also that it would likely confuse our persona, Annie.\\
-
-When using Prezi, human beings can creatively think of links and therefore make more graphical presentations.
-Due to the fact that our system only has limited intelligence, we end up with a far more structured presentation.
-However, considering that the goal of the created presentation is to allow users to intuitively understand dependencies and to allow them to deviate from the primary narrative path to enter the level of one of the dependencies and follow its narrative path for a while, it became obvious that a simple structure for this presentation is actually preferable.\\
-
-After having considered the systematic aspects, let us now look at the other aspects.
-Cognitively, we explored a part of the field of information systems.
-It is still an open question whether the developed system provides a better system for knowledge transfer.
-I strongly believe that the created system \sys adds value to presentation and has the power to facilitate and improve knowledge transfer due to some reasons that were already shown in the \autoref{sec:relatedworks}.
-There some argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.\\
-
-\begin{wrapfigure}{l}{0.3\textwidth}
-\vspace{-28pt}
-  \begin{center}
-  \fbox{\href{http://prezi.com/i-bhj8xahg3u/?utm_campaign=share&utm_medium=copy&rc=ex0share}{
-      \includegraphics[width=0.28\textwidth]{assets/final/ExamplePathTriangle}
-    } }
-\vspace{-20pt}
-  \caption{Path Example}
-  \label{fig:pathExample}
-\vspace{-40pt}
-  \end{center}
-\end{wrapfigure}
-
-Since a qualitative analysis was unfortunately not possible in this time frame, we can only make an educated guess at the usefulness.
-To strengthen this educated guess, we will look at the potential path a user could take through the presentation we created by examining \autoref{fig:pathExample}.\\
-
-In the book \textit{OMDoc - An Open Markup Format for Mathematical Documents} \cite{URL:omdocspec}, a didactic figure called the straw-man theory is introduced as an example for a na\"{i}ve reduced approximation of the real theory that aims to show an example to explain why said approximation does not work.
-Our system is not sophisticated enough to examine these structures on its own and figure out which information is best to be shown.
-Instead, \sys simply finds where the dependent information has been taught before and reuses the order in which it was taught before.
-Subsequently, our system heavily relies on sensible input.\\
-
-Given this sensible input our persona, Annie can make use of digressions, where she can go back to a different topic and follow its narrative path for a while.
-An example for this is highlighted with a blue triangle in \autoref{fig:pathExample}.
-These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.
 
@@
 
+\ednote{There some argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.}
+
+\ednote{These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.}
+
 \newpage

### 2015-05-27 Paper.tex
10 pages

@@
 \begin{wrapfigure}{l}{\textwidth}
-\vspace{-0pt}
+\vspace{-22pt}
   \begin{center}
   \fbox{
-      \includegraphics[width=0.70\textwidth]{assets/final/Architecture}
+      \includegraphics[width=0.55\textwidth]{assets/final/Architecture}
     } 
@@
   \label{fig:architecture}
-\vspace{12pt}
+\vspace{0pt}
   \end{center}
@@
 The files that lmh creates, along with the \stex -files will be used as input in the next steps.
-For the implementation of  \sys Java was used.
-It would have been possible to choose other programming languages, however, using Java, we end up with platform-independent code.\\
+For the implementation of  \sys Java was used.\\
 
@@
 In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}.
-Since we are in the setting of a university course, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
+Since we are in a classroom setting, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
 We will additionally introduce a third modus for information called \textit{course-ancient}.
@@
 
-As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.The system \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
+As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.
+\sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
 Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.\\
@@
   \fbox{
-      \includegraphics[width=0.87\textwidth]{assets/final/fullPresentation2}
+      \includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}
     } 
@@
 
-\begin{wrapfigure}{l}{0.57\textwidth}
-\vspace{-26pt}
+\begin{wrapfigure}{l}{0.42\textwidth}
+\vspace{-20pt}
   \begin{center}
   \fbox{
-      \includegraphics[width=0.55\textwidth]{assets/final/60degree}
+      \includegraphics[width=0.4\textwidth]{assets/final/60degree}
     } 
-\vspace{-5pt}
+\vspace{-15pt}
   \caption [Caption for LOF]{Visualization of Dependencies and Levels at 60\degree\ \footnotemark}
@@
 The important addition is more obvious when regarding the presentation from a bird's eye perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}.
-The value in these presentations is that through these overviews, dependencies become identifiable.
+The value in these presentations is that dependencies become identifiable.
 More importantly this means that for Annie, dependencies become accessible and allow her to go on small guided tours or small excursions into \textit{course-ancient} topics giving her the flexibility to choose her own path while going through the presentation.
@@
 
-In this research project we set out to help Annie understand the Pythagorean theorem.
+We set out to help Annie understand the Pythagorean theorem.
 Her problem was that she did not know about some of the dependent information, i.e.
@@
 Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience.
-This facilitates knowledge transfer and allows for a more engaging and interactive education.\\
+These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.
+Overall this facilitates knowledge transfer and allows for a more engaging and interactive education.\\
 
-In the future, I believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them.
+Linking learning materials is useful for knowledge transfer and especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.
+In future, I believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them.
 In the introduction, I introduced the metaphor of hiking up a mountain which can be done in different ways.
-The type of presentations this research built allows for a lot of different paths to reach a learning goal.
+The type of presentations this research built allows for a lot of different paths to reaching a learning goal.
 The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.\\
@@
 \sys definitely helped Annie and I strongly believe that the mentioned benefits would benefit all of us, whether in the role of the presenter or in the role of the viewer.
-
-\ednote{There some argued that the linking of learning materials is useful for knowledge transfer and that especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.}
-
-\ednote{These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.}
 

### 2015-05-27 Paper.tex
llncs and getting rid of lots of used packages

@@
-\documentclass[twoside, 12pt]{article}
+\documentclass{llncs}
 \usepackage{amsmath}
-\usepackage{lipsum} % Package to generate dummy text throughout this template
-\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
-\usepackage{pgfgantt}
 \usepackage[show]{ed}
-\setlength{\parindent}{0pt}
-\usepackage[sc]{mathpazo} % Use the Palatino font
-\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.2} % Line spacing - Palatino needs more space between lines
-\usepackage{microtype} % Slightly tweak font spacing for aesthetics
-\usepackage{minted}
+\usepackage{xspace}
+\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
+%\usepackage{etoolbox}
 \usepackage{enumitem}
-\usepackage[section]{placeins}
-\usepackage{nameref}
-\usemintedstyle{autumn}
-\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
-\usepackage{multicol} % Used for the two-column layout of the document
-\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
-\usepackage{booktabs} % Horizontal rules in tables
-\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
-\usepackage{hyperref} % For hyperlinks in the PDF
-\usepackage{xspace}
-\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
-\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
-\usepackage{etoolbox}
 \usepackage{eurosym}
-\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
-\usepackage{abstract} % Allows abstract customization
-\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
-\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text
-
-\usepackage{titlesec} % Allows customization of titles
-%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
-%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
-\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
-\titleformat{\subsection}[block]{\large\scshape}{\thesubsection.}{1em}{} % Change the look of the section titles
-\usepackage{cite}
-\usepackage{fancyhdr} % Headers and footers
-\pagestyle{fancy} % All pages have headers and footers
-\fancyhead{} % Blank out the default header
-\fancyfoot{} % Blank out the default footer
-\fancyhead[C]{\href{mailto:npentrel@gmail.com}{Naomi Pentrel} $\cdot$ \href{mailto:m.kohlhase@jacobs-university.de}{Michael Kohlhase} $\cdot$ \today} % Custom header text
-\fancyfoot[RO,LE]{\thepage} % Custom footer text
 \usepackage{graphicx}
 \usepackage{wrapfig}
-\usepackage[]{natbib}
-\usepackage{tocloft}
-\renewcommand*{\figureautorefname}{Figure}
 \def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
 \def\sTeX{\stex}
+\usepackage{hyperref}
 
-\usepackage{quoting}
-\quotingsetup{vskip=50pt}
-
-%\usepackage{csquotes}
-%\MakeOuterQuote{"}
-
-\hypersetup{
-    bookmarks=true,
-    unicode=false,
-    pdftoolbar=true,
-    pdfmenubar=true,
-    pdffitwindow=false,
-    pdfstartview={FitH},
-    pdftitle={My title},
-    pdfauthor={Author},
-    pdfsubject={Subject},
-    pdfcreator={Creator},
-    pdfproducer={Producer},
-    pdfkeywords={keyword1} {key2} {key3},
-    pdfnewwindow=true,
-    colorlinks=false,
-    %linkcolor=red,
-    %citecolor=green,
-    %filecolor=magenta,
-    %urlcolor=cyan
-    pdfborder={0 0 0},
-}
-
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage[section]{placeins}
-\usepackage{qtree}
-\usepackage{gensymb}
-
-\usepackage{setspace}
-
-\usepackage{color}
-
-\definecolor{bg}{rgb}{0.90,0.90,0.90}
-
-%\doublespacing
-% or:
-%\onehalfspacing
-
-%\renewcommand\cftchapafterpnum{\vskip10pt}
-%\renewcommand\cftsecafterpnum{\vskip15pt}
+\def\degree{\ensuremath{^\circ}}
+\newcommand{\sys}{\textsc{RPresentation}\xspace}
 
@@
 
-\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}} % Article title
-
-\newenvironment{myfont}{\fontfamily{\sfdefault}\selectfont}{\par}
-
+\title{Relational Presentation Using Semantic Closeness\\Spatial Narrative for
+  Mathematical Content}
+\author{Naomi Pentrel, Michael Kohlhase}
+\institute{Jacobs University Bremen}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\newcommand{\sys}{\textsc{RPresentation}\xspace}
 
@@
 \begin{document}
-\thispagestyle{empty}
-\pagenumbering{roman}
-\begin{flushright}
-    \includegraphics[scale=1.0]{assets/Logo}
-  \end{flushright}
-  \vspace{20mm}
-  \begin{center}
-    \huge
-    \textbf{Relational Presentation Using Semantic Closeness}\\
-    \vspace*{2mm}
-	\Large
-	\textbf{-\\Spatial Narrative for Mathematical Content}
-  \end{center}
-  \vspace*{2mm}
-  \begin{center}
-   \Large by
-  \end{center}
-  \vspace*{4mm}
-  \begin{center}
-    \Large
-    \textbf{Naomi Pentrel\\ \& \\ Prof. Dr. Michael Kohlhase}
-  \end{center}
-  \vspace*{4mm}
-  \begin{center}
-    \large
-  \end{center}
-  \vfill
-  \begin{flushright}
-    \large
-    \begin{tabular}{l}      
-      \\
-    \end{tabular}
-  \end{flushright}
-  \vspace*{0mm}
-  \begin{flushleft}
-    \large
-    Date of Submission: \today \\
-    \rule{\textwidth}{1pt}
-  \end{flushleft}
-  \begin{center}
-    \Large Jacobs University Bremen - School of Engineering and Science
-  \end{center}
-
-\newpage
-
-\thispagestyle{fancy} % All pages have headers and footers
+\maketitle
 
@@
 
- \section*{Abstract}
- \label{sec:abstract}
+ \begin{abstract}
 Visualization of knowledge is important to foster learning.
@@
 The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
-This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.\\
+This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.
 
@@
 Additionally, especially towards the end of the semester, students often have difficulties remembering earlier topics.
-When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\
+When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up.
 
@@
 This approach to presenting learning materials changes how we interact with course material which will allow students to learn better.
-Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.\\
-
-\newpage
-%\tableofcontents
-
-%\clearpage
-
-%\newpage
-%\thispagestyle{empty}
-%\topskip0pt
-%\vspace*{\fill}
-%\begin{center}
-%\textsc{Aut viam inveniam aut faciam}\\
-
-%\vspace*{1cm}
-
-%\textit{(I'll either find a path or make one)}\\
-
-%\vspace*{4cm}
-
-%\centering
-
-%\vspace*{\fill}
-%\end{center}
-
-%\newpage
-\pagenumbering{arabic}
+Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.
+\end{abstract}
 
@@
 We can make it possible to link content that logically belongs together, in other words, content that is semantically close.
-Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.\\
+Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.
 
@@
 Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle.
-Now Annie has to try to find out what a right triangle is.\\
+Now Annie has to try to find out what a right triangle is.
 
@@
 However, especially in mathematics, students would benefit from the possibility to take detours through half-forgotten topics as topics are often closely linked and interdependent.
-By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.\\
+By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.
 
@@
 The visualization of the information will make use of spatial narrative to connect information in a logical way.
-Thus the final product will allow Annie to intuitively interact with the presentation to find the information she needs.\\
+Thus the final product will allow Annie to intuitively interact with the presentation to find the information she needs.
 
@@
 To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.
-\\
 
@@
 The files that lmh creates, along with the \stex -files will be used as input in the next steps.
-For the implementation of  \sys Java was used.\\
+For the implementation of  \sys Java was used.
 
-\sys itself operates in five main steps:\\
+\sys itself operates in five main steps:
 \vspace{-12pt}
@@
 After asking the user for the location and names of the folders we want to work on, \sys can parse the provided \stex files in a recursive fashion to retrieve the slide order.
-It does this by starting with a given top level file which includes other files via \textit{mhinputref}s.\\
+It does this by starting with a given top level file which includes other files via \textit{mhinputref}s.
 
@@
 The order of the slides and their dependencies are then combined to an information graph which we use to create a relational presentation out of the annotated document using the slide info.
-This slide information is created by either parsing the XHTML and directly copying the needed parts into the final presentation or by transforming the PDF into PNGs that are then included in the final presentation.\\
+This slide information is created by either parsing the XHTML and directly copying the needed parts into the final presentation or by transforming the PDF into PNGs that are then included in the final presentation.
 
@@
 \begin{center}
-\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}\\
+\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}
 \end{center}
@@
 The accessibility depends on the relative \textit{newness}, i.e.
-recency of mention, of this information.\\
+recency of mention, of this information.
 
@@
 This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e.
-\textit{course-ancient}.\\
+\textit{course-ancient}.
 
@@
 Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
-Therefore we will focus on using spatial narrative to make presentations more engaging and enhance knowledge transfer.\\
+Therefore we will focus on using spatial narrative to make presentations more engaging and enhance knowledge transfer.
 
@@
 the statements or theories.
-Narrative layers refer to the order in which the mathematical objects from content layers are presented.\\
+Narrative layers refer to the order in which the mathematical objects from content layers are presented.
 
@@
 We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation.
-To create this primary narrative path we need to add several slides with increasing x-coordinates as portrayed in \autoref{fig:primaryNarrativePath}.\\
+To create this primary narrative path we need to add several slides with increasing x-coordinates as portrayed in \autoref{fig:primaryNarrativePath}.
 
@@
 Thus it contains also temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
-This temporal information is what we extracted from the \stex files as the order in which the slides (or the information on the slides) should appear.\\
+This temporal information is what we extracted from the \stex files as the order in which the slides (or the information on the slides) should appear.
 
@@
 \sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
-Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.\\
+Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.
 
@@
 Combining the information about narrative paths, dependencies, and levels, we derived an ordered information graph out of which we have built a presentation that Annie can interact with to learn about the Pythagorean theorem.
-In this section we will examine the structure of the created presentation.\\
+In this section we will examine the structure of the created presentation.
 
@@
 The added expressiveness that impress.js offers allowed us to have this in a very structured format while focusing on visualizing relations between content with movement and closeness.
-This also serves to keep the resulting presentation simple and easily usable.\\
+This also serves to keep the resulting presentation simple and easily usable.
 
@@
 The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it.
-The following movements exist:\\
+The following movements exist:
 \vspace{-12pt}
@@
 Apart from going forwards and backwards, we can also move along the y-axis.
-Moving down intuitively means that we dig deeper into a topic and go to the roots of a problem, whereas moving back up means we will be on a higher level.\\
+Moving down intuitively means that we dig deeper into a topic and go to the roots of a problem, whereas moving back up means we will be on a higher level.
 
@@
 Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.
-\footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}\\
+\footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}
 
@@
 right angles, and since there was no easy way to access this information she could not understand the topic fully.
-To help her, we created a system \sys that parses the documents that the instructor wrote and created a relational presentation out of it.\\
+To help her, we created a system \sys that parses the documents that the instructor wrote and created a relational presentation out of it.
 
@@
 In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation.
-This allows Annie to choose her own path while going through the presentation and seamlessly looking up related information.\\
+This allows Annie to choose her own path while going through the presentation and seamlessly looking up related information.
 
@@
 These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.
-Overall this facilitates knowledge transfer and allows for a more engaging and interactive education.\\
+Overall this facilitates knowledge transfer and allows for a more engaging and interactive education.
 
@@
 The type of presentations this research built allows for a lot of different paths to reaching a learning goal.
-The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.\\
+The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.
 
@@
 
-\newpage
-
-\bibliography{kwarc}{}
+\bibliography{kwarc}
 \bibliographystyle{alpha}
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2015-05-28 Paper.tex
fix for title
tweaks

@@
 
-\begin{wrapfigure}{r}{0.3\textwidth}
-\vspace{-28pt}
-  \begin{center}
+\begin{wrapfigure}{r}{0.36\textwidth}
+\vspace{-2em}\centering
   \fbox{
-    \includegraphics[width=0.28 \textwidth]{assets/final/straightMountain}
-    }
+    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-20pt}
+    \caption{Straight Learning Path}\label{fig:straight}
+    \vspace{5pt}  
+      \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
       \vspace{-20pt}
-  \caption{Straight Learning Path}
-  \label{fig:straight}
-\vspace{5pt}  
-      \fbox{
-    \includegraphics[width=0.28 \textwidth]{assets/final/curvyMountain}
-    }
-
-  \end{center}
-\vspace{-20pt}
-  \caption{Curvy Learning Path}
-  \label{fig:curvy}
+      \caption{Winding Learning Path}\label{fig:curvy}
       \vspace{-10pt}
@@
 
-\begin{wrapfigure}{l}{0.45\textwidth}
-\vspace{-28pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Theorem Slide}
-  \label{fig:slideP}
+\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
+  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}}\vspace{-.5em}
+  \caption{Theorem Slide}\label{fig:slideP}
   \vspace{-15pt}
@@
 
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-22pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.55\textwidth]{assets/final/Architecture}
-    } 
-\vspace{-6pt}
-  \caption{Architecture Diagram}
-  \label{fig:architecture}
-\vspace{0pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-50pt}
+\begin{wrapfigure}{l}{.55\textwidth}\centering\vspace{-2em}
+  \fbox{\includegraphics[width=0.55\textwidth]{assets/final/Architecture}} 
+  \vspace{-1em}
+  \caption{Architecture Diagram}\label{fig:architecture}\vspace{-1em}
 \end{wrapfigure}
@@
 \sys itself operates in five main steps:
-\vspace{-12pt}
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-35pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}
-    } 
-\vspace{-0pt}
-  \caption{Inclusion Graph for the Pythagorean Theorem}
-  \label{fig:inclusionGraph}
-\vspace{12pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-50pt}
+\begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
+  \fbox{\includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}} 
+  \caption{Inclusion Graph for the Pythagorean Theorem}\label{fig:inclusionGraph}
 \end{wrapfigure}
@@
 In our system, the \stex files are parsed using a Depth First Search algorithm to retrieve the narrative the writer intended to use.
-For the explanation of the Pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}.
+For the explanation of the Pytha\-go\-rean theorem this can be seen in \autoref{fig:inclusionGraph}.
 We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation.
@@
 
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-30pt}
-  \begin{center}
-  \fbox{
-    \includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}
-    }
-  \end{center}
-\vspace{-20pt}
-  \caption{Primary Narrative Path}
-  \label{fig:primaryNarrativePath}
-\vspace{12pt}
+\begin{wrapfigure}{c}{\textwidth}\centering\vspace{-2em}
+  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}}
+  \vspace{-1em}
+  \caption{Primary Narrative Path}\label{fig:primaryNarrativePath}
+  \vspace{-1em}
 \end{wrapfigure}
-
-\begin{wrapfigure}{l}{\textwidth}
-\vspace{-50pt}
-\end{wrapfigure}
-
-The primary narrative path, formed by a horizontal stream of slides, is the traditional path a presenter normally uses when preparing a PowerPoint presentation.
-Thus it contains also temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}.
-This temporal information is what we extracted from the \stex files as the order in which the slides (or the information on the slides) should appear.
+The primary narrative path, formed by a horizontal stream of slides, is the traditional
+path a presenter normally uses when preparing a PowerPoint presentation. Thus it contains
+also temporal information which is illustrated by the arrow in
+\autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from
+the \stex files as the order in which the slides (or the information on the slides) should
+appear.
 
@@
 
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-30pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}
-    } 
-\vspace{-20pt}
-  \caption{Dependency Graph}
-  \label{fig:depGraphPythagoreanFull}
-\vspace{0pt}
-  \end{center}
+\begin{figure}[ht]\vspace{-1em}
+  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}} 
+  \vspace{-.5em}
+  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
+\end{figure}
+
+\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
+  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
+  \vspace{-1em}
+  \caption{Visualization of Dependencies}\label{fig:visualDependency}
+  \vspace{-1em}
 \end{wrapfigure}
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-60pt}
-\end{wrapfigure}
-
-With the data about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the Pythagorean theorem.
-\sys creates this presentation incrementally.
-As outlined in \autoref{sec:narrativePaths} and illustrated in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides.
-After adding each slide it checks whether there is \textit{course-ancient} information, i.e.
-whether there are dependencies, for that slide.
-If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the choosing of different paths by pressing the right or down key \cite{npentrel:npentrel15}.}
-
-\begin{wrapfigure}{c}{1\textwidth}
-\vspace{-16pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}
-    } 
-\vspace{-7pt}
-  \caption{Visualization of Dependencies}
-  \label{fig:visualDependency}
-\vspace{-15pt}
-  \end{center}
-\end{wrapfigure}
-
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-140pt}
-\end{wrapfigure}
+With the data about the order and the dependencies of information within the paper, we now
+have an ordered information graph out of which we can build a first presentation that
+Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
+presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
+\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
+of the slides. After adding each slide it checks whether there is \textit{course-ancient}
+information, i.e. whether there are dependencies, for that slide. If there are
+dependencies those are added below the slide itself (see
+\autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the
+  choosing of different paths by pressing the right or down key
+  \cite{npentrel:npentrel15}.}
 
@@
 
-When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other \TeX\ files are included.
-These included files again include further \TeX\ files etc..
-Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.
-In essence, on any level the order of information in that topic is a narrative path itself.
-Expressed in mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$.
-From these levels we can infer the status of the information.
-We already know that a dependent piece of information infers that it is \textit{course-ancient} information.
-Anything that is on the same level or in the sublevels thereof is considered to be \textit{course-old} information.
+\begin{wrapfigure}r{.6\textwidth}\vspace{-2em}
+  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
+  \vspace{-1em}
+  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
+\vspace{-1em}
+\end{wrapfigure}
+When writing a document or course notes in \stex, the creator general writes a top-level
+file such as \textit{notes.tex} from where other \TeX\ files are included. These included
+files again include further \TeX\ files etc.. Thus we are automatically provided with
+levels that we can use for splicing our primary narrative path into smaller narrative
+paths. In essence, on any level the order of information in that topic is a narrative path
+itself. Expressed in mathematical notation a level within a directed graph
+$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
+set of directed edges, is the set
+$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
+the status of the information. We already know that a dependent piece of information
+infers that it is \textit{course-ancient} information. Anything that is on the same level
+or in the sublevels thereof is considered to be \textit{course-old} information.
 
-\begin{wrapfigure}{c}{\textwidth}
-\vspace{-12pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.6\textwidth]{assets/final/levels}
-    } 
-\vspace{-0pt}
-  \caption{Inclusion Graph with Levels}
-  \label{fig:levelsGraph}
-\vspace{12pt}
-  \end{center}
+\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
+  \fbox{\includegraphics[width=0.4\textwidth]{assets/final/60degree}} 
+  \vspace{-.5em}
+  \caption[Caption for LOF]{Visualization\footnotemark of Dependencies and Levels at
+    60\degree}
+  \label{fig:visualDependencyDegree}
+\vspace{-1em}
 \end{wrapfigure}
+If Annie, while browsing through the different dependencies, realizes that she needs to
+refresh her memory or learn more about any of the dependent information she can enter the
+respective level. The presentation will then continue on that level and show all the
+slides from that topic in the correct order. Once Annie has gone through this short
+excursion, she can return to the initial slide and resume the primary narrative path. By
+adding a way to explore these other levels, the presentation adds more context and allows
+Annie to understand the subject on a deeper level. These modular excursions are included
+in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
+excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
+story line (see \autoref{fig:visualDependencyDegree}).
 
-\begin{wrapfigure}{l}{0.42\textwidth}
-\vspace{-20pt}
-  \begin{center}
-  \fbox{
-      \includegraphics[width=0.4\textwidth]{assets/final/60degree}
-    } 
-\vspace{-15pt}
-  \caption [Caption for LOF]{Visualization of Dependencies and Levels at 60\degree\ \footnotemark}
-  \label{fig:visualDependencyDegree}
-\vspace{-24pt}
-  \end{center}
-\end{wrapfigure}
-
-If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter the respective level.
-The presentation will then continue on that level and show all the slides from that topic in the correct order.
-Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path.
-By adding a way to explore these other levels, the presentation adds more context and allows Annie to understand the subject on a deeper level.
-These modular excursions are included in the presentation in 3D by making use of CSS3-transitions.
-Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line (see \autoref{fig:visualDependencyDegree}).
-
-\footnotetext{The overlapping slides do not interfere as they are at a 90\degree\ angle.
-Therefore when seeing one slide, the other slide will be visible only from the side.
-Since a slide is very thin this makes it invisible.}
+\footnotetext{The overlapping slides do not interfere as they are at a 90\degree\
+  angle. Therefore when seeing one slide, the other slide will be visible only from the
+  side. Since a slide is very thin this makes it invisible.}
 
@@
 The following movements exist:
-\vspace{-12pt}
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\begin{inparaenum}[\em a\rm)]
 \item movement along the x-axis,
@@
 \end{enumerate}
-\vspace{5pt}
 
@@
 
-The most interesting movement is the rotations which aim to give the viewer the feeling of entering a topic and a different storyline.
-Thus entering a different topic comes with a change of perspective which is underlined by the 3D transformation that the user sees.
-Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation.
-\footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}
+The most interesting movement is the rotations which aim to give the viewer the feeling of
+entering a topic and a different storyline. Thus entering a different topic comes with a
+change of perspective which is underlined by the 3D transformation that the user
+sees. Overall, these movements add expressiveness to the relations and allow for intuitive
+interaction with the presentation. \footnote{To see the presentation in action visit:
+  \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}
 
-One might think that this is similar to a PowerPoint presentation, since PowerPoint offers similar animations to switch slides.
-The important addition is more obvious when regarding the presentation from a bird's eye perspective by looking at the overview in \autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}.
-The value in these presentations is that dependencies become identifiable.
-More importantly this means that for Annie, dependencies become accessible and allow her to go on small guided tours or small excursions into \textit{course-ancient} topics giving her the flexibility to choose her own path while going through the presentation.
+One might think that this is similar to a PowerPoint presentation, since PowerPoint offers
+similar animations to switch slides. The important addition is more obvious when regarding
+the presentation from a bird's eye perspective by looking at the overview in
+\autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}. The value in these
+presentations is that dependencies become identifiable. More importantly this means that
+for Annie, dependencies become accessible and allow her to go on small guided tours or
+small excursions into \textit{course-ancient} topics giving her the flexibility to choose
+her own path while going through the presentation.
 

### 2015-05-28 Paper.tex
beautification (figures)

@@
 %\usepackage{etoolbox}
-\usepackage{enumitem}
 \usepackage{eurosym}
@@
 \sys itself operates in five main steps:
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\begin{compactenum}
 \item Get user input for the locations and names of folders.
@@
 \item Create presentation.
-\end{enumerate}
-\vspace{5pt}
+\end{compactenum}
 
@@
 
-\begin{wrapfigure}{c}{\textwidth}\centering\vspace{-2em}
+\begin{figure}[ht]\centering
   \fbox{\includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}}
-  \vspace{-1em}
+  \vspace{-.5em}
   \caption{Primary Narrative Path}\label{fig:primaryNarrativePath}
   \vspace{-1em}
-\end{wrapfigure}
+\end{figure}
+
 The primary narrative path, formed by a horizontal stream of slides, is the traditional
@@
 \item rotations.
-\end{enumerate}
+\end{inparaenum}
 

### 2015-05-28 Paper.tex
abstract shortened

@@
 
-\title{Relational Presentation Using Semantic Closeness\\Spatial Narrative for
+\title{Relational Presentations Using Semantic Closeness\\Spatial Narrative for
   Mathematical Content}
@@
 Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts.
-To optimize the visualization of information and its interdependencies, a way to present information without loosing context is necessary.
-The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics.
-This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.
-
-Taking the typical Mathematics lecture as an example, it is often the case that students have different backgrounds.
-Some might have learned linear algebra while other have not yet.
-Additionally, especially towards the end of the semester, students often have difficulties remembering earlier topics.
-When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up.
-
-The OMDoc (OpenMathematical Documents) format is a content markup scheme for mathematical documents.
-Using OMDoc, the proposed system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on by taking a small detour through those topics, should they need to refresh their memories.
-Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning.
-This approach to presenting learning materials changes how we interact with course material which will allow students to learn better.
-Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.
+Taking the typical Mathematics lecture as an example, it is often the case that students come from different backgrounds.
+When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up on topics they have not learned.
+To optimize the visualization of information and its interdependencies, a way to present information without loosing context is therefore necessary.
+The following research takes an existing annotated corpus and presents its contents while allowing students to see dependencies between topics and encouraging them to explore related mathematical concepts.
+Thus students can interactively learn the concepts the current topic depends on by taking small detours through those topics, should they need to refresh their memories.
+This approach to presenting learning materials changes how we interact with course materials and it is ultimately applicable to almost all areas in which knowledge needs to be transferred.
 \end{abstract}

### 2015-05-29 Paper.tex
coppred
more

@@
   \fbox{
-    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-20pt}
+    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
     \caption{Straight Learning Path}\label{fig:straight}
@@
       \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
-      \vspace{-20pt}
+      \vspace{-1.8em}
       \caption{Winding Learning Path}\label{fig:curvy}
-      \vspace{-10pt}
+      \vspace{-2em}
 \end{wrapfigure}
 
-Learning new things is a bit like hiking up a mountain.
-If you have ever gone hiking, you know that it is hard to hike up a steep mountain directly as shown in \autoref{fig:straight}.
-Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}.
-Both paths lead to the goal though.
-Within Mathematics classes, there is normally only one straight path and this has not changed in decades.
-With the advancement of technology, we are however able to change the way presentations and their narratives work.
-We can make it possible to link content that logically belongs together, in other words, content that is semantically close.
-Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.
+Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you
+know that it is hard to hike up a steep mountain directly as shown in
+\autoref{fig:straight}. Some people do it but most people will rather hike up as shown in
+\autoref{fig:curvy}. Both paths lead to the goal though. Within Mathematics classes, there
+is normally only one straight path and this has not changed in decades. With the
+advancement of technology, we are however able to change the way presentations and their
+narratives work. We can make it possible to link content that logically belongs together,
+in other words, content that is semantically close. Through the linking of content it
+becomes possible for a presenter to seamlessly lead an audience, not along a predetermined
+straight path, but rather along the path that allows the audience to take small detours
+and ultimately make the most out of the presentation.\ednote{This intro does not work for
+  math. Math instruction is mostly done via blackboard, and teachers can flexibly take any
+  path they want with that in response to student understanding (or lack, ... ). Maybe we
+  can turn this around: math uses blackboard, because it is flexible. Presentations are
+  too inflexible for math, let's make them better.}
 
 \begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
-  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}}\vspace{-.5em}
+  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem_cropped}}\vspace{-.5em}
   \caption{Theorem Slide}\label{fig:slideP}
@@
 
-Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see \autoref{fig:slideP}).
-She is then given a triangle with sides a = 3 cm and b = 4 cm.
-Now she wants to use the theorem to calculate the length of side c.
-Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$.
-However Annie made a mistake and did not know what a right triangle is.
-Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle.
-Now Annie has to try to find out what a right triangle is.
+Let us use a contrived story to guide our intuitions: Annie, a young student learning
+mathematics, is watching her teacher give a slide-based presentation on how to use the
+Pythagorean theorem (see \autoref{fig:slideP}). She is then given a triangle with sides
+$a = 3 cm$ and $b = 4 cm$. Now she wants to use the theorem to calculate the length of
+side $c$. Annie already knows how to calculate the square of a number and thus calculates
+that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right
+triangle is. Her teacher tells her that the question was a trick question and that the
+answer is wrong because the triangle she calculated this for is not a right triangle. Now
+Annie has to try to find out what a right triangle is.
 
@@
 
-After asking the user for the location and names of the folders we want to work on, \sys can parse the provided \stex files in a recursive fashion to retrieve the slide order.
-It does this by starting with a given top level file which includes other files via \textit{mhinputref}s.
+After asking the user for the location and names of the folders we want to work on, \sys
+can parse the provided \stex files in a recursive fashion to retrieve the slide order. It
+does this by starting with a given top level file which includes other files via
+\texttt{\textbackslash mhinputref} macros.
 
@@
 
-\begin{center}
-\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}
-\end{center}
+\begin{quote}\em
+  My sister went to the circus the other day; \underline{she} said \underline{it} was
+  brilliant.
+\end{quote}
 

### 2015-05-29 Paper.tex
tweaks

@@
 
-For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added.
-The details of this process will be explained in subsection \ref{sec:narrativePaths}, \ref{sec:orderedInfoGraphs}, and \ref{sec:levels}.
-To complement the HTML, a CSS stylesheet is added which adds the some design elements.
-The design of the template is based on a presentation by S.
-Wolf \cite{Wolf:npentrel15}.
-To bring the presentation to life the library impress.js is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh.
-An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.
+For including the XHTML or the PNGs we use self-created boilerplate code, in which only
+some coordinates and the XHTML or the PNGs for the slide are added. The details of this
+process will be explained in Section \ref{sec:narrativePaths},
+\ref{sec:orderedInfoGraphs}, and \ref{sec:levels}. To complement the HTML, a CSS
+stylesheet is added which adds the some design elements. The design of the template is
+based on a presentation by S. Wolf \cite{Wolf:npentrel15}. To bring the presentation to
+life the library impress.js is used because it makes it simple to reuse the XHTML code
+that was automatically generated by lmh. An important additional reason for the choice of
+impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.
 
@@
   \caption{Visualization of Dependencies}\label{fig:visualDependency}
-  \vspace{-1em}
+  \vspace{-2em}
 \end{wrapfigure}
@@
 
-\begin{wrapfigure}r{.6\textwidth}\vspace{-2em}
+\begin{wrapfigure}r{.63\textwidth}\vspace{-2em}
   \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
@@
   \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
-\vspace{-1em}
+\vspace{-2em}
 \end{wrapfigure}
@@
   \vspace{-.5em}
-  \caption[Caption for LOF]{Visualization\footnotemark of Dependencies and Levels at
-    60\degree}
+  \caption{Visualization of Dependencies and Levels at 60\degree}
   \label{fig:visualDependencyDegree}
@@
 excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
-story line (see \autoref{fig:visualDependencyDegree}).
-
-\footnotetext{The overlapping slides do not interfere as they are at a 90\degree\
-  angle. Therefore when seeing one slide, the other slide will be visible only from the
-  side. Since a slide is very thin this makes it invisible.}
+story line -- see \autoref{fig:visualDependencyDegree}. The overlapping slides do not
+interfere as they are at a 90\degree\ angle. Therefore when seeing one slide, the other
+slide will be visible only from the side. Since a slide is very thin this makes it
+invisible.
 
@@
 sees. Overall, these movements add expressiveness to the relations and allow for intuitive
-interaction with the presentation. \footnote{To see the presentation in action visit:
-  \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}
+interaction with the presentation. The presentation can be found at
+\url{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.
 

### 2015-05-29 Paper.tex
changes to intro and fixes for images

@@
 
-\begin{wrapfigure}{r}{0.36\textwidth}
-\vspace{-2em}\centering
+\begin{wrapfigure}{r}{0.38\textwidth}
+\vspace{-2.1em}\centering
   \fbox{
-    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
+    \includegraphics[width=0.37 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
     \caption{Straight Learning Path}\label{fig:straight}
     \vspace{5pt}  
-      \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
+      \fbox{\includegraphics[width=0.38 \textwidth]{assets/final/curvyMountain}}
       \vspace{-1.8em}
       \caption{Winding Learning Path}\label{fig:curvy}
-      \vspace{-2em}
+      \vspace{-2.8em}
 \end{wrapfigure}
@@
 \autoref{fig:straight}. Some people do it but most people will rather hike up as shown in
-\autoref{fig:curvy}. Both paths lead to the goal though. Within Mathematics classes, there
-is normally only one straight path and this has not changed in decades. With the
-advancement of technology, we are however able to change the way presentations and their
+\autoref{fig:curvy}.
+Both paths lead to the goal though.
+Within Mathematics classes, professors that teach using a blackboard have the ability to diverge from their teaching plan when needed.
+The lack of flexibility of slides might in fact be why the blackboard teaching approach prevails especially in Mathematics.
+Yet offline materials given to students such as slides, books, or other documents prescribe one straight path and this has not changed in decades.
+With the advancement of technology, we are however able to change the way classroom materials and their
 narratives work. We can make it possible to link content that logically belongs together,
@@
 straight path, but rather along the path that allows the audience to take small detours
-and ultimately make the most out of the presentation.\ednote{This intro does not work for
-  math. Math instruction is mostly done via blackboard, and teachers can flexibly take any
-  path they want with that in response to student understanding (or lack, ... ). Maybe we
-  can turn this around: math uses blackboard, because it is flexible. Presentations are
-  too inflexible for math, let's make them better.}
+and ultimately make the most out of the presentation.
 
@@
   \caption{Theorem Slide}\label{fig:slideP}
-  \vspace{-15pt}
+  \vspace{-20pt}
 \end{wrapfigure}
@@
 \begin{wrapfigure}{l}{.55\textwidth}\centering\vspace{-2em}
-  \fbox{\includegraphics[width=0.55\textwidth]{assets/final/Architecture}} 
-  \vspace{-1em}
-  \caption{Architecture Diagram}\label{fig:architecture}\vspace{-1em}
+  \fbox{\includegraphics[width=0.53\textwidth]{assets/final/Architecture}} 
+  \vspace{-1.7em}
+  \caption{Architecture Diagram}\label{fig:architecture}
+  \vspace{-1.5em}
 \end{wrapfigure}
@@
 \begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}} 
-  \caption{Inclusion Graph for the Pythagorean Theorem}\label{fig:inclusionGraph}
+  \fbox{\includegraphics[width=0.63\textwidth]{assets/final/inclusionGraphPythagorean}} 
+  \vspace{-1.8em}
+  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
+  \vspace{-2em}
 \end{wrapfigure}
@@
   \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
-  \vspace{-1em}
+  \vspace{-1.8em}
   \caption{Visualization of Dependencies}\label{fig:visualDependency}
@@
 dependencies those are added below the slide itself (see
-\autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the
+\autoref{fig:visualDependency}).\footnote{The library impress.js was adapted to support the
   choosing of different paths by pressing the right or down key
@@
 
+\newpage
 \subsection{Levels}
@@
   \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
-  \vspace{-1em}
+  \vspace{-0.8em}
   \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
@@
 \begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.4\textwidth]{assets/final/60degree}} 
-  \vspace{-.5em}
+  \fbox{\includegraphics[width=0.41\textwidth]{assets/final/60degree}} 
+  \vspace{-1.8em}
   \caption{Visualization of Dependencies and Levels at 60\degree}
   \label{fig:visualDependencyDegree}
-\vspace{-1em}
+\vspace{-1.8em}
 \end{wrapfigure}

### 2015-06-13 Paper.tex
fix image
reviews added
added todos, fixed I mistake

@@
 When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up on topics they have not learned.
-To optimize the visualization of information and its interdependencies, a way to present information without loosing context is therefore necessary.
+To optimize the visualization of information and its interdependencies, a way to present information without losing context is therefore necessary.
 The following research takes an existing annotated corpus and presents its contents while allowing students to see dependencies between topics and encouraging them to explore related mathematical concepts.
@@
 
-\begin{wrapfigure}{r}{0.38\textwidth}
-\vspace{-2.1em}\centering
+\begin{wrapfigure}{r}{0.45\textwidth}
+\vspace{-2.2em}\centering
   \fbox{
-    \includegraphics[width=0.37 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
+    \includegraphics[width=0.39 \textwidth]{assets/final/straightMountain}}    \vspace{-0.8em}
     \caption{Straight Learning Path}\label{fig:straight}
     \vspace{5pt}  
-      \fbox{\includegraphics[width=0.38 \textwidth]{assets/final/curvyMountain}}
-      \vspace{-1.8em}
+      \fbox{\includegraphics[width=0.4 \textwidth]{assets/final/curvyMountain}}
+      \vspace{-0.8em}
       \caption{Winding Learning Path}\label{fig:curvy}
-      \vspace{-2.8em}
+      \vspace{-2.1em}
 \end{wrapfigure}
@@
 Linking learning materials is useful for knowledge transfer and especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.
-In future, I believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them.
-In the introduction, I introduced the metaphor of hiking up a mountain which can be done in different ways.
+In future, we believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them.
+In the introduction, we introduced the metaphor of hiking up a mountain which can be done in different ways.
 The type of presentations this research built allows for a lot of different paths to reaching a learning goal.
@@
 
-To conclude, I leave the reader to ponder how much education would change if we could allow individuals to learn at their own pace following their own path and easily learning course-ancient information in guided tours.
-\sys definitely helped Annie and I strongly believe that the mentioned benefits would benefit all of us, whether in the role of the presenter or in the role of the viewer.
+To conclude, we leave the reader to ponder how much education would change if we could allow individuals to learn at their own pace following their own path and easily learning course-ancient information in guided tours.
+\sys definitely helped Annie and we strongly believe that the mentioned benefits would benefit all of us, whether in the role of the presenter or in the role of the viewer.
 

### 2015-06-13 Paper.tex
fixed redundancy as pointed out by review 2

@@
 We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation.
-To create this primary narrative path we need to add several slides with increasing x-coordinates as portrayed in \autoref{fig:primaryNarrativePath}.
-
-\begin{figure}[ht]\centering
-  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}}
-  \vspace{-.5em}
-  \caption{Primary Narrative Path}\label{fig:primaryNarrativePath}
-  \vspace{-1em}
-\end{figure}
+To create this primary narrative path we add several slides with increasing x-coordinates.
 
@@
 Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
-presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
-\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
+presentation incrementally. As outlined in \autoref{sec:narrativePaths}, \sys creates the primary narrative path from the order
 of the slides. After adding each slide it checks whether there is \textit{course-ancient}
@@
 
-\newpage
 \subsection{Levels}

### 2015-06-13 Paper.tex
addressed Review 2 comment 2

@@
 We will now commence the journey towards building a more effective presentation format to improve knowledge transfer in Mathematics by allowing flexibility in presentations.
-In the following we will assume the reader is familiar with OMDoc \cite{Kohlhase:OMDoc1.2} and with the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+In the following we will use OMDoc \cite{Kohlhase:OMDoc1.2} and the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
+The paper will point out some functions of OMDoc as needed; the interested reader is encouraged to explore OMDoc in the cited paper.
+JSImpress merely serves for visualization, further understanding of the tool is not needed for the purpose of the paper.
 To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.

### 2015-06-13 Paper.tex
fixed dimensions of images'

@@
 
-\begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.63\textwidth]{assets/final/inclusionGraphPythagorean}} 
-  \vspace{-1.8em}
+\begin{figure}[ht]\vspace{-1.5em}
+  \fbox{\includegraphics[width=1\textwidth]{assets/final/inclusionGraphPythagorean}} 
+  \vspace{-1.5em}
   \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
 \vspace{-2em}
-\end{wrapfigure}
+\end{figure}
 
@@
 
+\begin{wrapfigure}l{.42\textwidth}\vspace{-2em}
+  \fbox{\includegraphics[width=0.40\textwidth]{assets/final/pythdep2}} 
+  \vspace{-1.9em}
+  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
+  \vspace{-2em}
+\end{wrapfigure}
 As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.
@@
 
-\begin{figure}[ht]\vspace{-1em}
-  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}} 
-  \vspace{-.5em}
-  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
-\end{figure}
-
-\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
-  \vspace{-1.8em}
-  \caption{Visualization of Dependencies}\label{fig:visualDependency}
-  \vspace{-2em}
-\end{wrapfigure}
 With the data about the order and the dependencies of information within the paper, we now
@@
 
+\begin{figure}[ht]\vspace{-1.5em}
+  \fbox{\includegraphics[width=1\textwidth]{assets/final/fullPresentation2}} 
+  \vspace{-1.5em}
+  \caption{Visualization of Dependencies}\label{fig:visualDependency}
+\vspace{-2em}
+\end{figure}
+
 \subsection{Levels}
@@
 
-\begin{wrapfigure}r{.63\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
-  \vspace{-0.8em}
-  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
-\vspace{-2em}
-\end{wrapfigure}
 When writing a document or course notes in \stex, the creator general writes a top-level
@@
 or in the sublevels thereof is considered to be \textit{course-old} information.
+
+\begin{figure}[ht]\vspace{-1.5em}
+  \fbox{\includegraphics[width=1\textwidth]{assets/final/levels}} 
+  \vspace{-1.5em}
+  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
+\vspace{-2em}
+\end{figure}
 

### 2015-06-16 Paper.tex
citation comment addressed
tweaks

@@
 \begin{abstract}
-Visualization of knowledge is important to foster learning.
-Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts.
-Taking the typical Mathematics lecture as an example, it is often the case that students come from different backgrounds.
-When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up on topics they have not learned.
-To optimize the visualization of information and its interdependencies, a way to present information without losing context is therefore necessary.
-The following research takes an existing annotated corpus and presents its contents while allowing students to see dependencies between topics and encouraging them to explore related mathematical concepts.
-Thus students can interactively learn the concepts the current topic depends on by taking small detours through those topics, should they need to refresh their memories.
-This approach to presenting learning materials changes how we interact with course materials and it is ultimately applicable to almost all areas in which knowledge needs to be transferred.
+  Visualization of knowledge is important to foster learning. Especially so in Mathematics
+  where students have to understand not just the topic hand but also related concepts. It
+  would therefore be ideal to have a simple way to find dependencies and present students
+  with an easy way to catch up on topics they have not learned yet without losing
+  context.
+
+  Our research takes an existing annotated corpus and presents its contents while allowing
+  students to see dependencies between topics and encouraging them to explore related
+  mathematical concepts. Thus students can interactively learn the concepts the current
+  topic depends on by taking small detours through those topics, should they need to
+  refresh their memories. This approach to presenting learning materials changes how we
+  interact with course materials and it is ultimately applicable to almost all areas in
+  which knowledge needs to be transferred.
 \end{abstract}
@@
 it is in the intersection of knowledge of student and teacher.
-\textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
+\textit{New/ unfamiliar} information is not in the shared knowledge base.
 In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
@@
 \begin{figure}[ht]\vspace{-1.5em}
-  \fbox{\includegraphics[width=1\textwidth]{assets/final/inclusionGraphPythagorean}} 
-  \vspace{-1.5em}
+  \fbox{\includegraphics[width=.97\textwidth]{assets/final/inclusionGraphPythagorean}} 
+  \vspace{-.5em}
   \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
@@
 \begin{figure}[ht]\vspace{-1.5em}
-  \fbox{\includegraphics[width=1\textwidth]{assets/final/fullPresentation2}} 
-  \vspace{-1.5em}
+  \fbox{\includegraphics[width=.97\textwidth]{assets/final/fullPresentation2}} 
+  \vspace{-.5em}
   \caption{Visualization of Dependencies}\label{fig:visualDependency}

### 2015-09-08 Resubmission.tex
addting Resubmission.tex

--- 2015-06-13 Paper.tex
@@
 
-\title{Relational Presentations Using Semantic Closeness\\Spatial Narrative for
-  Mathematical Content}
+\title{Relational Presentations Using Semantic Closeness\\ Spatial Narrative for Mathematical Content \thanks{{\it Copyright \copyright\, 2015 by the paper's authors.
+Copying permitted only for private and academic purposes.} In: R.
+Bergmann, S.
+G{\"o}rg, G.
+M{\"u}ller (Eds.): Proceedings of the LWA 2015 Workshops: KDML, FGWM, IR, and FGDB.
+Trier, Germany, 7.-9.
+October 2015,  published at http://ceur-ws.org}}
+\renewcommand\footnotemark{}
+
 \author{Naomi Pentrel, Michael Kohlhase}
@@
 
-\section{Introduction \& Motivation}
-\label{sec:introduction}
+Original Publication at:\\ \href{http://www.cermat.org/events/MathUI/15/proceedings/Pentrel-Kohlhase_Semantic_Closness-MathUI_15.pdf}{http://www.cermat.org/events/MathUI/15/proceedings/Pentrel-Kohlhase\\\_Semantic\_Closness-MathUI\_15.pdf}
 
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-2.2em}\centering
-  \fbox{
-    \includegraphics[width=0.39 \textwidth]{assets/final/straightMountain}}    \vspace{-0.8em}
-    \caption{Straight Learning Path}\label{fig:straight}
-    \vspace{5pt}  
-      \fbox{\includegraphics[width=0.4 \textwidth]{assets/final/curvyMountain}}
-      \vspace{-0.8em}
-      \caption{Winding Learning Path}\label{fig:curvy}
-      \vspace{-2.1em}
-\end{wrapfigure}
-
-Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you
-know that it is hard to hike up a steep mountain directly as shown in
-\autoref{fig:straight}. Some people do it but most people will rather hike up as shown in
-\autoref{fig:curvy}.
-Both paths lead to the goal though.
-Within Mathematics classes, professors that teach using a blackboard have the ability to diverge from their teaching plan when needed.
-The lack of flexibility of slides might in fact be why the blackboard teaching approach prevails especially in Mathematics.
-Yet offline materials given to students such as slides, books, or other documents prescribe one straight path and this has not changed in decades.
-With the advancement of technology, we are however able to change the way classroom materials and their
-narratives work. We can make it possible to link content that logically belongs together,
-in other words, content that is semantically close. Through the linking of content it
-becomes possible for a presenter to seamlessly lead an audience, not along a predetermined
-straight path, but rather along the path that allows the audience to take small detours
-and ultimately make the most out of the presentation.
-
-\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
-  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem_cropped}}\vspace{-.5em}
-  \caption{Theorem Slide}\label{fig:slideP}
-  \vspace{-20pt}
-\end{wrapfigure}
-
-Let us use a contrived story to guide our intuitions: Annie, a young student learning
-mathematics, is watching her teacher give a slide-based presentation on how to use the
-Pythagorean theorem (see \autoref{fig:slideP}). She is then given a triangle with sides
-$a = 3 cm$ and $b = 4 cm$. Now she wants to use the theorem to calculate the length of
-side $c$. Annie already knows how to calculate the square of a number and thus calculates
-that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right
-triangle is. Her teacher tells her that the question was a trick question and that the
-answer is wrong because the triangle she calculated this for is not a right triangle. Now
-Annie has to try to find out what a right triangle is.
-
-Annie's example shows the dependencies of different pieces of information, i.e.
-the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles.
-As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up.
-However, especially in mathematics, students would benefit from the possibility to take detours through half-forgotten topics as topics are often closely linked and interdependent.
-By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.
-
-To achieve our goal to help Annie, we will set out to create a relational presentation system \sys to visually present information and its context which allows Annie to interact with the content and choose a path that matches her knowledge base.
-The visualization of the information will make use of spatial narrative to connect information in a logical way.
-Thus the final product will allow Annie to intuitively interact with the presentation to find the information she needs.
-
-Along the way of helping Annie, we will explore the question of how to create a flexible presentation, which allows Annie to choose her own path to explore the context of a topic by browsing through related resources as needed.
-To create this presentation a tool for automatic contextual visualization of information will be introduced.
-Through the usage of both spatial narrative and semantic closeness of information it will connect information logically.
-The end product will be a presentations which allow Annie to choose her own path by interacting with the presentation to seamlessly explore related topics and brush up on half-forgotten topics like right angles.
-There are many stories such as Annie's in real life and it is therefore important to provide information with its context to facilitate learning and knowledge transfer as a whole so that each of us can choose a learning path that allows us to reach the goal, whether it be by following a straight or a curvy path.
-
-\section{Towards a More Effective Presentation Format}
-\label{sec:TowardsAMoreEffectivePresentationFormat}
-
-We will now commence the journey towards building a more effective presentation format to improve knowledge transfer in Mathematics by allowing flexibility in presentations.
-In the following we will use OMDoc \cite{Kohlhase:OMDoc1.2} and the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge.
-The paper will point out some functions of OMDoc as needed; the interested reader is encouraged to explore OMDoc in the cited paper.
-JSImpress merely serves for visualization, further understanding of the tool is not needed for the purpose of the paper.
-To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.
-
-\begin{wrapfigure}{l}{.55\textwidth}\centering\vspace{-2em}
-  \fbox{\includegraphics[width=0.53\textwidth]{assets/final/Architecture}} 
-  \vspace{-1.7em}
-  \caption{Architecture Diagram}\label{fig:architecture}
-  \vspace{-1.5em}
-\end{wrapfigure}
-
-With the OMDoc framework and its tools it is possible to write down course notes or other documents in \textbf{S}emantically enhanced \TeX / \LaTeX\ (\stex).
-The Local MathHub Tool (lmh) uses these to create, among other things, PDF slides, XHTML slides, and relational information.
-To help Annie, let us use a document that explains the Pythagorean theorem and related topics.
-The files that lmh creates, along with the \stex -files will be used as input in the next steps.
-For the implementation of  \sys Java was used.
-
-\sys itself operates in five main steps:
-\begin{compactenum}
-\item Get user input for the locations and names of folders.
-\item Parse \sTeX to retrieve the order of slides.
-\item Extract dependencies from relational info.
-\item Extract necessary XHTML or PNG parts for slides.
-\item Create presentation.
-\end{compactenum}
-
-After asking the user for the location and names of the folders we want to work on, \sys
-can parse the provided \stex files in a recursive fashion to retrieve the slide order. It
-does this by starting with a given top level file which includes other files via
-\texttt{\textbackslash mhinputref} macros.
-
-In the next step the relational information is parsed and put into a hashtable.
-The keys are the slides which link to an array of dependent slides.
-The order of the slides and their dependencies are then combined to an information graph which we use to create a relational presentation out of the annotated document using the slide info.
-This slide information is created by either parsing the XHTML and directly copying the needed parts into the final presentation or by transforming the PDF into PNGs that are then included in the final presentation.
-
-For including the XHTML or the PNGs we use self-created boilerplate code, in which only
-some coordinates and the XHTML or the PNGs for the slide are added. The details of this
-process will be explained in Section \ref{sec:narrativePaths},
-\ref{sec:orderedInfoGraphs}, and \ref{sec:levels}. To complement the HTML, a CSS
-stylesheet is added which adds the some design elements. The design of the template is
-based on a presentation by S. Wolf \cite{Wolf:npentrel15}. To bring the presentation to
-life the library impress.js is used because it makes it simple to reuse the XHTML code
-that was automatically generated by lmh. An important additional reason for the choice of
-impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.
-
-\subsection{Status of Information within the (Dis)Course}
-\label{sec:infostatus}
-In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed.
-Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information.
-\textit{Familiar/ old} information is shared by speaker and addressee, i.e.
-it is in the intersection of knowledge of student and teacher.
-\textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}.
-In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.
-
-\begin{quote}\em
-  My sister went to the circus the other day; \underline{she} said \underline{it} was
-  brilliant.
-\end{quote}
-
-In this example in the first part of the sentence, \textit{discourse-new} information pertaining to my sister and to a circus is introduced.
-In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.
-These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}.
-The accessibility depends on the relative \textit{newness}, i.e.
-recency of mention, of this information.
-
-These concepts can be adapted to the situation of teaching mathematics or computer science to students in a class.
-In general we will call the information that the speaker is passing on to the addressees/students \textit{course-new}.
-Since we are in a classroom setting, the \textit{course-new} information will generally depend on information that is \textit{course-old}.
-We will additionally introduce a third modus for information called \textit{course-ancient}.
-This covers the situation where the addressee has difficulties following the speaker since the \textit{course-new} information depends on \textit{course-old} information that might be 'too old' to be easily remembered, i.e.
-\textit{course-ancient}.
-
-Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}.
-The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}.
-The information about squares which Annie still remembers is \textit{course-old}.
-Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course.
-
-\subsection{Narrative Paths}
-\label{sec:narrativePaths}
-
-The information that OMDoc provides us with could also be simply visualized as a tree of information.
-However, this would not be very engaging and it would be hard for a person to process.
-Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information.
-Therefore we will focus on using spatial narrative to make presentations more engaging and enhance knowledge transfer.
-
-One opportunity to employ spatial narrative is to place content which is inherently related visually close together since this conveys the meaning that these objects belong together.
-In \textit{A mathematical approach to ontology authoring and documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers".
-In our case, the content layers are the mathematical objects, i.e.
-the statements or theories.
-Narrative layers refer to the order in which the mathematical objects from content layers are presented.
-
-\begin{figure}[ht]\vspace{-1.5em}
-  \fbox{\includegraphics[width=1\textwidth]{assets/final/inclusionGraphPythagorean}} 
-  \vspace{-1.5em}
-  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
-\vspace{-2em}
-\end{figure}
-
-In our system, the \stex files are parsed using a Depth First Search algorithm to retrieve the narrative the writer intended to use.
-For the explanation of the Pytha\-go\-rean theorem this can be seen in \autoref{fig:inclusionGraph}.
-We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation.
-To create this primary narrative path we add several slides with increasing x-coordinates.
-
-The primary narrative path, formed by a horizontal stream of slides, is the traditional
-path a presenter normally uses when preparing a PowerPoint presentation. Thus it contains
-also temporal information which is illustrated by the arrow in
-\autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from
-the \stex files as the order in which the slides (or the information on the slides) should
-appear.
-
-Temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic.
-These narrative paths are similar to short guided tours in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred.
-Going back to our example of Annie, an example of a subsection would be the information concerning angles.
-In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own which occur on different levels as explained in \autoref{sec:levels}.
-
-\subsection{Ordered Information Graphs}
-\label{sec:orderedInfoGraphs}
-
-\begin{wrapfigure}l{.42\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.40\textwidth]{assets/final/pythdep2}} 
-  \vspace{-1.9em}
-  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
-  \vspace{-2em}
-\end{wrapfigure}
-As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics.
-\sys parses this relational data and retrieves the dependencies of the topics which are visualized for Annie's example in \autoref{fig:depGraphPythagoreanFull}.
-Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information obtained longer ago.
-
-With the data about the order and the dependencies of information within the paper, we now
-have an ordered information graph out of which we can build a first presentation that
-Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
-presentation incrementally. As outlined in \autoref{sec:narrativePaths}, \sys creates the primary narrative path from the order
-of the slides. After adding each slide it checks whether there is \textit{course-ancient}
-information, i.e. whether there are dependencies, for that slide. If there are
-dependencies those are added below the slide itself (see
-\autoref{fig:visualDependency}).\footnote{The library impress.js was adapted to support the
-  choosing of different paths by pressing the right or down key
-  \cite{npentrel:npentrel15}.}
-
-\begin{figure}[ht]\vspace{-1.5em}
-  \fbox{\includegraphics[width=1\textwidth]{assets/final/fullPresentation2}} 
-  \vspace{-1.5em}
-  \caption{Visualization of Dependencies}\label{fig:visualDependency}
-\vspace{-2em}
-\end{figure}
-
-\subsection{Levels}
-\label{sec:levels}
-
-When writing a document or course notes in \stex, the creator general writes a top-level
-file such as \textit{notes.tex} from where other \TeX\ files are included. These included
-files again include further \TeX\ files etc.. Thus we are automatically provided with
-levels that we can use for splicing our primary narrative path into smaller narrative
-paths. In essence, on any level the order of information in that topic is a narrative path
-itself. Expressed in mathematical notation a level within a directed graph
-$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
-set of directed edges, is the set
-$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
-the status of the information. We already know that a dependent piece of information
-infers that it is \textit{course-ancient} information. Anything that is on the same level
-or in the sublevels thereof is considered to be \textit{course-old} information.
-
-\begin{figure}[ht]\vspace{-1.5em}
-  \fbox{\includegraphics[width=1\textwidth]{assets/final/levels}} 
-  \vspace{-1.5em}
-  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
-\vspace{-2em}
-\end{figure}
-
-\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
-  \fbox{\includegraphics[width=0.41\textwidth]{assets/final/60degree}} 
-  \vspace{-1.8em}
-  \caption{Visualization of Dependencies and Levels at 60\degree}
-  \label{fig:visualDependencyDegree}
-\vspace{-1.8em}
-\end{wrapfigure}
-If Annie, while browsing through the different dependencies, realizes that she needs to
-refresh her memory or learn more about any of the dependent information she can enter the
-respective level. The presentation will then continue on that level and show all the
-slides from that topic in the correct order. Once Annie has gone through this short
-excursion, she can return to the initial slide and resume the primary narrative path. By
-adding a way to explore these other levels, the presentation adds more context and allows
-Annie to understand the subject on a deeper level. These modular excursions are included
-in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
-excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
-story line -- see \autoref{fig:visualDependencyDegree}. The overlapping slides do not
-interfere as they are at a 90\degree\ angle. Therefore when seeing one slide, the other
-slide will be visible only from the side. Since a slide is very thin this makes it
-invisible.
-
-\subsection{The Relational Presentation}
-\label{sec:RelationalPresentations}
-
-Combining the information about narrative paths, dependencies, and levels, we derived an ordered information graph out of which we have built a presentation that Annie can interact with to learn about the Pythagorean theorem.
-In this section we will examine the structure of the created presentation.
-
-To begin with, let us examine the choice of layout.
-The goal of this presentation is to have all the information the Pythagorean theorem depends on easily accessible so that Annie can access \textit{course-ancient} information easily.
-The added expressiveness that impress.js offers allowed us to have this in a very structured format while focusing on visualizing relations between content with movement and closeness.
-This also serves to keep the resulting presentation simple and easily usable.
-
-While focusing on closeness and movement, it creates meaningful visual relations and semantic movements.
-The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it.
-The following movements exist:
-\begin{inparaenum}[\em a\rm)]
-\item movement along the x-axis,
-\item movement along the y-axis, and
-\item rotations.
-\end{inparaenum}
-
-The movement along the x-axis has a mostly temporal semantics associated with it.
-Going to the left is connected with going backwards in the narrative, whereas going to the right is associated with going forwards in the narrative.
-Apart from going forwards and backwards, we can also move along the y-axis.
-Moving down intuitively means that we dig deeper into a topic and go to the roots of a problem, whereas moving back up means we will be on a higher level.
-
-The most interesting movement is the rotations which aim to give the viewer the feeling of
-entering a topic and a different storyline. Thus entering a different topic comes with a
-change of perspective which is underlined by the 3D transformation that the user
-sees. Overall, these movements add expressiveness to the relations and allow for intuitive
-interaction with the presentation. The presentation can be found at
-\url{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.
-
-One might think that this is similar to a PowerPoint presentation, since PowerPoint offers
-similar animations to switch slides. The important addition is more obvious when regarding
-the presentation from a bird's eye perspective by looking at the overview in
-\autoref{fig:visualDependency} or \autoref{fig:visualDependencyDegree}. The value in these
-presentations is that dependencies become identifiable. More importantly this means that
-for Annie, dependencies become accessible and allow her to go on small guided tours or
-small excursions into \textit{course-ancient} topics giving her the flexibility to choose
-her own path while going through the presentation.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-We set out to help Annie understand the Pythagorean theorem.
-Her problem was that she did not know about some of the dependent information, i.e.
-right angles, and since there was no easy way to access this information she could not understand the topic fully.
-To help her, we created a system \sys that parses the documents that the instructor wrote and created a relational presentation out of it.
-
-This relational presentation combines spatial narrative with information about the relations between different pieces of information into a visual information graph.
-In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation.
-This allows Annie to choose her own path while going through the presentation and seamlessly looking up related information.
-
-The benefits are not just for Annie when she is going through the presentation on her own though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way.
-Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience.
-These digressions are the added value that allow flexibility in these new presentation and transform the traditional presentations from linear presentations to relational presentations.
-Overall this facilitates knowledge transfer and allows for a more engaging and interactive education.
-
-Linking learning materials is useful for knowledge transfer and especially mathematics is a field that could profit from guided tours through topics as a way of learning topics according to users' individual knowledge bases.
-In future, we believe that this research could be adopted in more fields, transforming education into something that allows individuals to learn the way that is best for them.
-In the introduction, we introduced the metaphor of hiking up a mountain which can be done in different ways.
-The type of presentations this research built allows for a lot of different paths to reaching a learning goal.
-The flexibility that comes with these presentations is undoubtedly preferable to traditional presentations as it offers clear benefits in allowing to effortlessly change the path of the presentation at any point.
-
-To conclude, we leave the reader to ponder how much education would change if we could allow individuals to learn at their own pace following their own path and easily learning course-ancient information in guided tours.
-\sys definitely helped Annie and we strongly believe that the mentioned benefits would benefit all of us, whether in the role of the presenter or in the role of the viewer.
-
-\bibliography{kwarc}
-\bibliographystyle{alpha}
 \end{document}
